### 2016-02-10 Paper_ttbarH_Draft.tex
initial commit

\documentclass[aps,preprint,tightenlines,floatfix,superscriptaddress,nofootinbib,showpacs]{revtex4-1}
\pdfoutput=1
\usepackage{graphicx}
%\usepackage{dcolumn}
\usepackage{amsfonts}
\usepackage{hhline}
\usepackage{multirow}
\usepackage{array}
%\usepackage{longtable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{maybemath}
%\usepackage[italic]{hepparticles}
\usepackage{float}
\usepackage[lofdepth,lotdepth]{subfig}
\usepackage[countmax]{subfloat}
\usepackage{cancel}
%\usepackage[nodisplayskipstretch]{setspace}
%\setstretch{1.5}
%\usepackage{caption}
%\usepackage{subcaption}
\setlength{\oddsidemargin}{-1in}
\addtolength{\oddsidemargin}{24mm} \setlength{\textwidth}{170mm}
\setlength{\topmargin}{-0.55in} \setlength{\headheight}{10mm}
\setlength{\headsep}{0mm} \setlength{\textheight}{230mm}
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\bea{\begin{eqnarray}}
\def\eea{\end{eqnarray}}
\def\nn{\nonumber}
\def\sss{\scriptstyle}
\def\lft{{\scriptstyle L}}
\def\rht{{\scriptstyle R}}
\def\roughly#1{\mathrel{\raise.3ex\hbox
{$#1$\kern-.75em\lower1ex\hbox{$\sim$}}}}
\def\lsim{\roughly<}
\def\gsim{\roughly>}
\def\tbslash{\tbar\hspace{-10pt}\not{}\hspace{4pt}}
\def\tslash{t\hspace{-10pt}\not{}\hspace{4pt}}
\def\lpslash{l^+\hspace{-10pt}\not{}\hspace{4pt}}
\def\lmslash{l^-\hspace{-10pt}\not{}\hspace{4pt}}
\def\nslash{n\hspace{-10pt}\not{}\hspace{4pt}}
\def\ntbslash{n_{\tbar}\hspace{-10pt}\not{}\hspace{4pt}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\note}[1]{\marginpar{{\small\begin{center}{\it #1}\end{center}}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\tbar{\bar{t}}
%\def\tbar{{\overline{t}}}
\def\bbar{\bar{b}}
\def\qbar{\bar{q}}
\def\nubar{{\bar{\nu}}_{\ell}}
\def\tbbc{t \to b \bbar c}
\def\tauprocess{\tau\rightarrow K\pi\pi\nu_{\tau}}
\def\ppprocess{pp\to t\,\left(\rightarrow b {\ell}^+ \nu_{\ell}\right) \tbar\,\left(\rightarrow\bbar {\ell}^-\nubar\right)\,H}
\def\bppprocess{{\boldmath $pp\to t \tbar H\to \left(b {\ell}^+ \nu_{\ell}\right)\left(\bbar {\ell}^-\nubar\right)H$}}
\def\ggprocess{gg\to t \tbar H\to\left(b l^+ \nu_l\right)\left(\bbar l^-\nubar\right)H}
\def\qqprocess{q\qbar\to t \tbar H\to\left(b l^+ \nu_l\right)\left(\bbar l^-\nubar\right)H}
\def\kp{\kappa_t}
\def\kpt{\tilde{\kappa}_t}
\def\MG{\mbox{MadGraph 5}}
\def\tm#1{\texttt{TM-{#1}}}
\def\ex#1{\texttt{EX-{#1}}}
\def\Ahat{\hat A_i^{\sigma}}
\def\madg{MadGraph~5}
\def\TPa{\epsilon(t,\tbar,n_t,n_{\tbar})}
\def\TPb{\epsilon(Q,\tbar,n_t,n_{\tbar})}
\def\TPc{\epsilon(Q,t,n_t,n_{\tbar})}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%
%for editing purposes
\usepackage[normalem]{ulem}
\usepackage{color}
\definecolor{BrickRed}{cmyk}{0,0.89,0.94,0.28}
\definecolor{DarkGreen}{cmyk}{1,0,1,0.5}
\definecolor{Blue}{cmyk}{1,1,0,0}
\definecolor{BurntOrange}{cmyk}{0,0.51,1,0}

\def\hldl#1{\textcolor{BrickRed}{\textsf{#1}}}
\def\hlps#1{\textcolor{DarkGreen}{\textsf{#1}}}
\def\hlkk#1{\textcolor{Blue}{\textsf{#1}}}
\def\hlas#1{\textcolor{BurntOrange}{\textsf{#1}}}
\def\soutdl{\bgroup\markoverwith{\textcolor{BrickRed}{\rule[0.5ex]{2pt}{0.4pt}}}\ULon}
\def\soutps{\bgroup\markoverwith{\textcolor{DarkGreen}{\rule[0.5ex]{2pt}{0.4pt}}}\ULon}
\def\soutkk{\bgroup\markoverwith{\textcolor{Blue}{\rule[0.5ex]{2pt}{0.4pt}}}\ULon}
\def\soutas{\bgroup\markoverwith{\textcolor{BurntOrange}{\rule[0.5ex]{2pt}{0.4pt}}}\ULon}

\def\mhldl#1{\textcolor{BrickRed}{\ensuremath{#1}}}
\def\mhlps#1{\textcolor{DarkGreen}{\ensuremath{#1}}}
\def\mhlkk#1{\textcolor{Blue}{\ensuremath{#1}}}
\def\mhlas#1{\textcolor{BurntOrange}{\ensuremath{#1}}}
\def\msoutdl#1{\text{\soutps{\ensuremath{#1}}}}
\def\msoutps#1{\text{\soutps{\ensuremath{#1}}}}
\def\msoutkk#1{\text{\soutps{\ensuremath{#1}}}}
\def\msoutas#1{\text{\soutps{\ensuremath{#1}}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{2cm}

\title{{\boldmath Pseudoscalar top-Higgs coupling:  Exploration of $\mathrm{CP}$-odd observables to 
resolve the sign ambiguity
}}

\def\tayloru{\affiliation{\it Physics and Engineering Department,
    Taylor University, \\ 236 West Reade Ave., Upland, IN 46989, USA \vspace*{1mm}}}

%\def\tayloru{\affiliation{\it Physics and Engineering Department,
%    Taylor University, \\ 236 West Reade Ave., Upland, IN 46989, USA \vspace*{8mm}}}

\def\laplata{\affiliation{\it IFLP, CONICET -- Dpto. de F\'{\i}sica,
    Universidad Nacional de La Plata, C.C. 67, 1900 La Plata,
    Argentina \vspace*{8mm}}}

\author{Nicolas Mileo}
\email{mileo@fisica.unlp.edu.ar}
\laplata

\author{Ken Kiers}
\email{knkiers@taylor.edu}
\tayloru

\author{Alejandro Szynkman}
\email{szynkman@fisica.unlp.edu.ar}
\laplata

\author{Daniel Crane \vspace*{4mm}}
\email{\hlkk{dkcrane@mtu.edu}}
\tayloru

\author{Ethan Gegner}
\email{ethan_gegner@taylor.edu}
\tayloru

\date{\vspace*{2mm}\today \\\bigskip\bigskip}

\begin{abstract}
\vspace*{4mm} We present a collection of $\mathrm{CP}$-odd observables
for the process $\ppprocess$ that are linearly dependent on the scalar
($\kp$) and pseudoscalar ($\kpt$) top-Higgs coupling and hence
sensitive to the corresponding relative sign. The proposed observables
are based on triple products (TP) structures that we extract from the
expression of the differential cross section in terms of the spin
vectors of the top and antitop quarks. In order to explore other
possibilities, we progressively modify these TPs, firstly, by
combining them and then by replacing the spin vectors by the lepton
momenta or the $t$ and $\tbar$ momenta by their visible parts. We
obtain that the most promising observable can disentangle the
hypotheses $\kp=1,\kpt=\pm 1$ by more than $\sim 20\sigma$ for $10^5$
events that is within the expected order of magnitude of events at the
HL-LHC. In the case of observables that do not need the reconstruction
of the $t$ and $\tbar$ momenta, the power of discrimination is up to
$\sim 16\sigma$ for the same ammount of events. We also show that the
capability of the most promising observables for separating the
$\mathrm{CP}$-mixed hypotheses preveals even when a number of events
plausible within the short term LHC is considered.

%We also show that the sensitivity of the most promising observables is not spoiled when a number of events affordable by the short term LHC is considered.

%We also show that even when the number of events is reduced by an order of magnitude the most promising observables are still useful for testing the couplings
\end{abstract}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec1}
After the discovery of a new boson $H$ by the ATLAS \cite{atlasH} and
CMS \cite{cmsH} collaborations, it has become of crucial importance
its characterization, namely the determination of its physical
properties with the highest possible precision. Among the features of
the new boson that are under investigation, the study of its couplings
to the fermions is of great relevance, allowing us to study the nature
of $H$ under the discrete symmetry $\mathrm{CP}$ and to clarify the
extent to which this new particle is consistent to the Higgs boson
predicted by the Standard Model (SM) of particle physics. In
particular, the test of the Higgs coupling to the heaviest fermion,
the top quark, is a priority since on the one hand, it rules the main
production mechanism through gluon fusion and contributes to the
important decay mode to two photons, and on the other hand, it is
involved in the scalar-field naturalness problem giving rise to the
leading dependence on the cut-off energy scale in the corrections to
the Higgs mass and it may play an important role in the EWSB
mechanism.\par

Given the fact that the main Higgs boson production
process, the gluon fusion, is dominated by a top quark loop and that
the diphoton and digluon decay channels are also mediated by a top
loop, these processes provide constraints on the scalar and
pseudoscalar $tH$ couplings, $\kp$ and $\kpt$
\cite{constraints1,constraints2, constraints3,constraints4}. However,
these constraints assume that there are no other sources contributing
to the corresponding effective couplings and, in the case of the
diphoton decay channel which also involves a $W$ boson loop, that the
coupling of the Higgs boson to the $W$ is standard. In this sense, the
constraints derived from measurements of Higgs rates are indirect
constraints. In this direction, electric dipole moments (EDM) can also
impose stringent indirect constraints on $\kpt$ by assuming that there
are no new physics (NP) particles contributing to the loops of the
relevant diagrams and that the electron-Higgs coupling is that
predicted by the SM \cite{constraints1,edm}. In order to probe
directly the $tH$ coupling, processes with smaller cross sections need
to be taken into account.  \par

In contrast to the $\tau H$ coupling which can be studied trough the
decay $H\rightarrow \tau^+\tau^-$ \cite{tau}, the $tH$ coupling is
tested directly by making use of the production processes since the
phase space forbids the Higgs to decay to the pair $t\tbar$. The
production of the Higgs boson in association with the pair $t\tbar$
and the production in association with a single top or antitop are the
only two direct ways of probing the $tH$ coupling. The cross section
of the single top (antitop) production is smaller and it is given by
the interference between a diagram in which the Higgs is radiated from
the top (antitop) leg and one with the Higgs emmited from the
intermediate virtual $W$ boson. This then implies that the contraints
over $\kp$ and $\kpt$ derived from $tH$ and $\tbar H$ production are
dependent on the asummption made on the coupling of the Higgs to the
gauge boson $W$, $\kappa_W$. However, it is important to note that the
interference between the above mentioned diagrams present in $tH$
($\tbar H$) production can be exploited in order to determine the
relative sign between $\kp$ and $\kappa_W$ (see for example
\cite{tHmaltoni}). From the point of view of $t\tbar H$ production,
several observables sensitive to the couplings $\kp$ and $\kpt$ has
been proposed. Examples of such observables are the cross section, the
invariant mass distributions, the transverse Higgs momentum
distribution or the azymuthal-angle separation between $t$ and $\tbar$
just to name a few \citep{Guadagnoli}. An approach based on weighted
moments and optimal observables has been developed in \cite
{Gunion1,*Gunion2,*Gunion3,*Gunion} to discriminate the hypothesis of
a $\mathrm{CP}$-even Higgs from that of a $\mathrm{CP}$-mixed state
within the context of a $e^+ e^-$ as well as a $pp$ collider. All the
mentioned observables are $\mathrm{CP}$-even and hence are not
sensitive to relative sign between the scalar and pseudoscalar
couplings $\kp$ and $\kpt$. Such observables are quadratically
dependent on these couplings and then only provide an indirect measure
of $\mathrm{CP}$ violation. In order to be sensitive to the relative
sign between $\kp$ and $\kpt$, $\mathrm{CP}$-odd observables must be
considered.  \par

Since the quark top decays before it can hadronize, its spin
information is passed on to the angular distributions of the decay
products in such a way that these particles work as spin analyzers
being the lepton the most powerful. On the other hand, it has been
shown that in $t\tbar$ production the top quark and antiquark spins
are strongly correlated \cite{Mahlon1,*Mahlon2,*Mahlon3,*atwood} and
this manifests in the double angular distributions of the decay
products of the $t$ and $\tbar$ systems. These correlations are
dependent in turn on the production mechanism and in the case of
$t\tbar H$ associated production are sensitive to the manner in which
the top couples to the Higgs boson. In fact, observables that exploit
the differences on the $t\tbar$ spin configurations are used in
\cite{Biswas} to improve the discrimination of the $t\tbar H$ signal
from the dominant irreducible background $t\tbar b\bbar$, in which the
Higgs boson is not involved.  \par

In this paper, we define a set of observables linearly dependent on
$\kp$ and $\kpt$ and hence sensitive to the relative sign of these
couplings. The proposed observables are based on a particular set of
triple product structures (TP) that we extract naturally from the
expression of the differential cross section, which makes use in turn
of the fact that the kinematics of the decay products contain the
information on the $t$ and $\tbar$ spins and thus is sensitive to the
nature of the $tH$ coupling, just as was discussed in the previous
paragraph. By using spinor thechniques we simply relate the top quark
and antiquark spin vectors and the corresponding final state particle
momenta and separate the production process from the decay which
allows to identify straightforwardly the contributions linearly
sensitive to the couplings. Further, the TPs correlations in these
contributions incorporate the $t$ and $\tbar$ spin vectors. Starting
with these TPs, we not only recover the observables given in
\cite{Ellis,Guadagnoli} but also propose additional possibilities that
increase the sensitivity. In order to establish a hierarchy in the
sensitivity of the TPs under analysis we investigate three different
types of observables by using simulated events: asymmetries, mean
values and angular distributions. We note that TP correlations has
been used in \cite{Valencia1,*Valencia2} in the context of top-quark
production and decay and in \cite{Valencia3} in the framework of
anomalous color dipole operators.  \par

The remainder of this paper is organized as follows. In
Sec.~\ref{sec2} we study the theoretical framework for the process
$\ppprocess$ and derive a general expression for the differential
cross section from which a first set of TP correlations is
extracted. In Sec.~\ref{sec3} we probe the sensitivity of these TPs to
the $tH$ coupling by using various $\mathrm{CP}$-odd
observables. Subsequent sections are dedicated to explore another
possibilities of $\mathrm{CP}$-odd observables. In particular,
observables based on TPs that incorporate the Higgs momentum are
discussed in Sec.~\ref{sec4}, whereas observables obtained without
using the $t$ and $\tbar$ momenta are studied in
Sec.~\ref{sec5}. Finally, Sec.~\ref{sec6} is devoted to the discussion
on the experimental feasibility of the most promising observables
encountered here. The main conclusions are summarized in
Sec.~\ref{sec7}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%%%%%%%%%%%%%%%% Quitarlo %%%%%%%%%%%%%%%%%%%%%%%
\setlength{\abovedisplayskip}{10.6pt}
\setlength{\belowdisplayskip}{10.6pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Process \MakeLowercase{{\boldmath $pp\to t \bar{t}$}}$H\to$\MakeLowercase{{\boldmath $\left(b l^+ \nu_l \right) \left(\bar{b} l^-\bar{\nu}_l\right)$}}$H$. Theoretical framework}
\section{Process \MakeLowercase{{\boldmath $pp\to t(\to b {\ell}^+ \nu_{\ell})\,\bar{t}(\to\bar{b} {\ell}^-\bar{\nu}_{\ell})$}}$\,H$. Theoretical framework}
\label{sec2}

%
At the LHC the $t\bar{t}H$ production proceeds via $q\bar{q}$
annihilation and $gg$ fusion processes. The relevant Feynman diagrams
at leading order are displayed in Fig.~\ref{fig1}, where the two first
rows correspond respectively to $q\bar{q}$ and $gg$ s-channels whereas
the last one depicts the $gg$ t-channels. By exchanging the gluon
lines in this row, three more $gg$-initiated diagrams can be
obtained. We describe the $tH$ cupling with the effective lagrangian
%
\beq
\label{eq1}
\mathcal{L}_{t\bar{t}H}=-\frac{m_t}{v}(\kp \tbar t+i\kpt \tbar
\gamma_5 t)H,
\eeq
%
where $v=246~\mathrm{GeV}$ is the SM Higgs vacuum
expectation value, and the coefficients $\kp$ and $\kpt$ determine the
weigth of the scalar and pseudoscalar interaction, respectively. The
SM case is obtained for $\kp=1$ and $\kpt=0$, while the values $\kp=0$
and $\kpt\neq 0$ parameterizes a $\mathrm{CP}$-odd Higgs. \par
%%%%%%%%%%%%%%%%%%%% Figura 1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%/home/nico/jaxodraw-2.1-0/
\begin{center}
\begin{figure}[H]
\centering
%\hspace*{-0.4cm}
\subfloat{\includegraphics[scale=0.45]{qqs1_II.pdf}}
\hspace*{0.05\textwidth}
%\label{fig1a}}
\subfloat{\includegraphics[scale=0.45]{qqs2_II.pdf}}
%\label{fig1b}}
\\[0.032\textwidth]
\subfloat{\includegraphics[scale=0.45]{ggs1_II.pdf}}
\hspace*{0.05\textwidth}
%\label{fig1b}}
\subfloat{\includegraphics[scale=0.45]{ggs2_II.pdf}}
%\label{fig1c}}
\\[0.032\textwidth]
\subfloat{\includegraphics[scale=0.45]{ggt1_II.pdf}}
%\label{fig1b}}
\hspace*{0.025\textwidth}
\subfloat{\includegraphics[scale=0.45]{ggt2_II.pdf}}
%\label{fig1c}}
\hspace*{0.025\textwidth}
\subfloat{\includegraphics[scale=0.45]{ggt3_II.pdf}}
%\label{fig1b}}
\vspace*{0.02\textwidth}
\caption{Tree level Feynman diagrams contributing to $t\tbar H$ production at the LHC. Three more diagrams are obtained by exchanging the gluon lines in the t-channel diagrams.}
\label{fig1}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Since the total cross-section is dominated by the $gg$ contribution,
let us focus on the $gg$-initiated production followed by the leptonic
SM decay of both $t$ and $\tbar$. By using the narrow-width
approximation for the top quark, it can be shown that the unpolarized
differential cross section for the full process $gg\to t(\to
b{\ell}^+\nu_{\ell})\,\tbar(\to \bbar {\ell}^- \nubar)\,H$ takes the
following form (we sketch the proof below)
%
\beq
\label{eq2}
%dd\sigma(gg\to (bl^+\nu_l)(\bbar l^- \nubar) H)=\sum_{\substack{bl^+\nu_l \\ \tiny{\mathrm{spins}}}}\,\sum_{\substack{\bbar l^-\nubar \\ \mathrm{\tiny{spins}}}}\left(\frac{2}{\Gamma_t}\right)^2\,d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)\,d\Gamma(t(n_t)\to bl^+\nu_l)\,d\Gamma(\tbar (n_{\tbar})\to \bbar l^-\nubar)
d\sigma =\sum_{\substack{b{\ell}^+\nu_l \\ \tiny{\mathrm{spins}}}}\,\sum_{\substack{\bbar {\ell}^-\nubar \\ \mathrm{\tiny{spins}}}}\left(\frac{2}{\Gamma_t}\right)^2\,d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)\,d\Gamma(t(n_t)\to b{\ell}^+\nu_{\ell})\,d\Gamma(\tbar (n_{\tbar})\to \bbar {\ell}^-\nubar),
\eeq  
%
where $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$ is the differential
cross section of the production of a top quark with spin vector $n_t$
plus an anti-top quark with spin vector $n_{\bar{t}}$ and a Higgs
boson, whereas $d\Gamma(t(n_t)\to b{\ell}^+\nu_{\ell})$ and
$d\Gamma(\tbar (n_{\tbar})\to \bbar {\ell}^-\nubar)$ are the
differential decay widths of a top with spin vector $n_t$ and an
anti-top with spin vector $n_{\tbar}$, respectively. Also, the vectors
$n_t$ and $n_{\tbar}$ are given by particular combinations of the
momenta $t,\ell^+$ and $\tbar,\ell^-$ respectively \cite{Arens},
%
\bea
\label{eq3}
n_t&=&-\frac{p_t}{m_t}+\frac{m_t}{(p_t\cdot p_{{\ell}^+})}p_{{\ell}^+}\\
\label{eq4}
n_{\tbar}&=&\,\frac{p_{\tbar}}{m_t}-\frac{m_t}{(p_{\tbar}\cdot p_{{\ell}^-})}p_{{\ell}^-}.
\eea
%
Expressions similar to Eq.~(\ref{eq2}) have been derived for the
production of short-lived particles in $e^-e^+$ colliders
\cite{kawasaki} and in particular for $t\tbar$ production both in
$e^-e^+$ colliders \cite{Arens} and $pp$ colliders
\cite{ale1,*ale2,*ale3,*ale4}. \par We will outline now how to derive
Eq.~(\ref{eq2}) and to obtain the above definitions for the spin
vectors. The process $g_ag_b\to t(\to
b_i{\ell}^+\nu_{\ell})\,\tbar(\to \bbar_j {\ell}^- \nubar)\,H$ can be
drawn as in Fig.~\ref{fig2}, where $a$ and $b$ denote the gluons and
$i$ and $j$ are the top and anti-top colours.
%%%%%%%%%%%%%%%%% FIGURA 2 %%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{esquematico_II.pdf}
\vspace*{0.02\textwidth}
\caption{Schematic representation of the process $g_ag_b\to t(\to
  b_i{\ell}^+\nu_{\ell})\tbar(\to \bbar_j {\ell}^- \nubar) H$. The
  indices $i,j$ denote the colour of the quarks while $a,b$ are gluon
  indices.}
\label{fig2}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\par
%
The diagrams displayed in Fig.~\ref{fig1} (second and third rows)
contribute to the quantity $A^{ab,ij}$, so that
%
\beq
\label{eq5}
\mathcal{A}^{ab,ij}\equiv A^{ab,ij}_{\mu\nu}(\epsilon_{\lambda_a})^{\mu}(\epsilon_{\lambda_b})^{\nu}=\sum_{k=1}^8 \mathcal{A}^{ab,ij}_k =\kp \sum_{k=1}^8 \mathcal{S}^{ab,ij}_k + i\kpt \sum_{k=1}^8 \mathcal{P}^{ab,ij}_k, 
\eeq 
%
where $\epsilon_{\lambda_a}$ and $\epsilon_{\lambda_b}$ are the
polarization vectors of $g_a$ and $g_b$ respectively and in the last
equality the scalar piece of each diagram has been separated from the
pseudoscalar one. The quantity $\mathcal{A}^{ab,ij}$ can be linked to
the final states particles by using two spinors, $\psi_{t}$ and
$\psi_{\tbar}$, that will contain the information on the decay of the
virtual top and anti-top, respectively. Hence, the amplitude for the
complete process depicted in Fig.~\ref{fig2} can be witten as
%
\beq
\label{eq6}
\mathcal{M}^{ab,ij}=\bar{\psi}_t\,\mathcal{A}^{ab,ij}\,\psi_{\tbar}\,.
\eeq
%
If we assume $b,l$ and $\nu_l$ to be massless, we can make use of the
spinor techniques\footnote{These spinors techniques can also be used
  for massive particles. However, the derivation of Eq.~(\ref{eq2}) is
  much simpler by assuming the final state particles to be massless
  which is a sensible approximation in view of the energy involved in
  the process.} developed in \cite{Kleiss} to write $\bar{\psi}_t$ and
$\psi_{\tbar}$ as follows
%
\bea
\label{eq7}
\bar{\psi}_t &=& -g^2\,\frac{1}{(t^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{((t-b)^2-M^2_W+im_W\Gamma_W)}\,\langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\
\label{eq8}
\psi_{\tbar} &=& -g^2\,\frac{1}{(\tbar^2-m^2_t+im_t\Gamma_t)}\frac{1}{((\tbar-\bbar)^2-M^2_W+im_W\Gamma_W)}\,\langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
\eea
%
where $|i+(-)\rangle \equiv P_{R(L)}\,\psi_i$ ($P_{R,L}=(1\pm
\gamma^5)/2$) represents a right-handed(left-handed) chiral spinor for
particle $i$, $\langle i+(-)|$ is the corresponding adjoint spinor and
we have denoted the momenta through the symbols that represents the
name of the particles \cite{Mangano}. The relevant quantity is
$|\mathcal{M}^{ab,ij}|^2$, which from Eqs.~(\ref{eq6})-(\ref{eq8}) is
proportional to $((t^2-m^2_t)^2+m^2_t\Gamma^2_t)^{-1}$ and
$((\tbar^2-m^2_t)^2+m^2_t\Gamma^2_t)^{-1}$. Under the narrow-width
approximation we can replace these factors by
$(\pi/m_t\Gamma_t)\delta(t^2-m^2_t)$ and
$(\pi/m_t\Gamma_t)\delta(\tbar^2-m^2_t)$ respectively. Hence, we can
take directly $t^2=\tbar^2=m^2_t$ in the amplitude and write
%
\beq
\label{eq9}
\mathcal{M}^{ab,ij}=\!-g^4\,\mathbb{P}_t(t)\,\mathbb{P}_{\tbar}(\tbar)\,\mathbb{P}_W(t-b)\,\mathbb{P}_W(\tbar-\bbar)\,\langle b-|\nu_{\ell}+\rangle \langle\nubar+|\bbar-\rangle \sqrt{\strut2(t\cdot {\ell}^+)}\sqrt{\strut2(\tbar\cdot {\ell}^-)}\,[\bar{\phi}_t \mathcal{A}^{ab,ij}\phi_{\tbar}],
%\frac{1}{(t^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{(\tbar^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{((t-b)^2-M^2_W)}\frac{1}{((\tbar-\bbar)^2-M^2_W)}\,\langle b-|\nu+\rangle\,\langle\nubar+|\bbar-\rangle
\eeq
%
where we have used the notation
$\mathbb{P}_t(t)=(t^2-m^2_t+im_t\Gamma_t)^{-1}$,
$\mathbb{P}_{\tbar}(\tbar)=(\tbar^2-m^2_t+im_t\Gamma_t)^{-1}$,
$\mathbb{P}_W(t-b)=((t-b)^2-M^2_W+im_W\Gamma_W)^{-1}$ and
$\mathbb{P}_W(\tbar-\bbar)=((\tbar-\bbar)^2-M^2_W+im_W\Gamma_W)^{-1}$. The
spinors $\phi_{t}$ and $\phi_{\tbar}$ are defined as follows
%
\beq
\label{eq10}
\phi_t=\frac{(\tslash +m_t)}{\sqrt{\strut2(t\cdot {\ell}^+)}}|{\ell}^++\rangle
\eeq
%
\beq
\label{eq11}
\phi_{\tbar}=\frac{(\tbslash -m_t)}{\sqrt{\strut2(\tbar\cdot {\ell}^-)}}|{\ell}^-+\rangle
\eeq
%
and describe a top quark with spin vector $n_t$ and an anti-top quark
with spin vector $n_{\tbar}$, since the corresponding projection
operators are given by
%
\beq
\label{eq12}
\phi_t\,\bar{\phi}_t=\frac{1}{2}(1+\nslash_{\!t}\gamma^5)(\tslash +m_t)
\eeq
%
\beq
\label{eq13}
\phi_{\tbar}\,\bar{\phi}_{\tbar}=\frac{1}{2}(1+\nslash_{\!\tbar}\gamma^5)(\tbslash -m_t),
\eeq
%
with $n_t$ and $n_{\tbar}$ being the vectors defined in
Eq.~(\ref{eq3})-(\ref{eq4}). Moreover, if we use these spinors to
compute the amplitude for a top(anti-) with spin vector
$n_t$($n_{\tbar}$) to decay into
$b{\ell}^+\nu_{\ell}$($\bar{b}{\ell}^-\bar{\nu}_{\ell}$) we obtain
%
\beq
\label{eq14}
\mathcal{M}(t(n_t)\to b{\ell}^+\nu_{\ell})=ig^2\mathbb{P}_W(t-b)\langle b-|\nu_{\ell}+\rangle\sqrt{\strut2(t\cdot {\ell}^+)}
\eeq
%
\beq
\label{eq15}
\mathcal{M}(\tbar(n_{\tbar})\to \bar{b}{\ell}^-\bar{\nu}_{\ell})=ig^2\mathbb{P}_W(\tbar-\bar{b})\langle \bar{\nu}_{\ell}+|\bar{b}-\rangle\sqrt{\strut2(\tbar\cdot {\ell}^-)}.
\eeq
%
On the other hand, the term inside the square brackets in
Eq.~(\ref{eq9}) is nothing but the amplitude for producing a top quark
with spin vector $n_t$, along with an anti-top with spin vector
$n_{\tbar}$ and a Higgs boson, i.e.
%
\beq
\label{eq16}
\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H)=\bar{\phi}_t \mathcal{A}^{ab,ij}\phi_{\tbar}.
\eeq
%
By combining Eqs.~(\ref{eq14})-(\ref{eq16}), we can write Eq.~(\ref{eq9}) as follows
%
\beq
\label{eq17}
\mathcal{M}^{ab,ij}=\mathbb{P}_t(t)\mathbb{P}_{\tbar}(\tbar)\,\mathcal{M}(t(n_t)\to b{\ell}^+\nu_{\ell})\,\mathcal{M}(\tbar(n_{\tbar})\to \bar{b}{\ell}^-\bar{\nu}_{\ell})\,\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H).
\eeq
%
From Eq.~(\ref{eq17}), Eq.~(\ref{eq2}) can be derived. It's important
to note that, even though Eqs.~(\ref{eq2}) and (\ref{eq9}) appear to
be factorized into production and decay parts, these are not
independent, since both parts share kinematical variables due to the
presence of the spin vectors $n_t$ and $n_{\tbar}$ (see
Eqs.~(\ref{eq14})-(\ref{eq16}) along with the definitions given in
Eqs.~(\ref{eq3}) and (\ref{eq4})).\par
%%%%%%%%%%%%%%%%%%% Quitarlo %%%%%%%%%%%%%%%%%%%%
\setlength{\abovedisplayskip}{10.2pt}
\setlength{\belowdisplayskip}{10.2pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Let us focus now in the production amplitude in Eq.~(\ref{eq17})
needed for computing the production part of the unpolarized
differential cross-section. By summing over colour and gluon indices
we have
%
\beq
\label{eq18}
\sum_{\substack{a,b \\ i,j}}|\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H)|^2=\sum_{\substack{a,b \\ i,j}}\left|\sum^{8}_{k=1}C^{ab,ij}_k\,\bar{\phi}_t (\kp\mathcal{S}_k+i\kpt\mathcal{P}_k)\phi_{\tbar}\right|^2,
\eeq
%
where we have separated the colour structure of each diagram by using
the definitions $\mathcal{S}^{ab,ij}= C^{ab,ij}_k \mathcal{S}$ and
$\mathcal{P}^{ab,ij}= C^{ab,ij}_k \mathcal{P}$. Also, the factors
$g^2_s m_t/v$ and $-ig^2_s m_t/v$ arising from the vertices of the t-
and s-channel diagrams respectively have been included in the
definition of $C^{ab,ij}_k$ for convenience. The terms linear in $\kp$
and $\kpt$ can be written as
%
\beq
\label{eq19}
\mathcal{O}(\kp\kpt)\to \frac{1}{2}\kp\kpt \sum_{k,r}\mathbb{C}_{kr}\mathrm{Im}
\left\lbrace \mathrm{Tr}\left[ (1+\nslash_t \gamma^5)(\tslash+m_t)\mathcal{S}_k(1+\nslash_{\tbar}\gamma^5
 )(\tbslash -m_t)\tilde{\mathcal{P}}_r \right] \right\rbrace ,
\eeq
%
where the factor $\mathbb{C}_{kr}=\sum_{ab,ij}C^{ab,ij}_k
C^{ab,ij*}_r$ is real and $\tilde{\mathcal{P}}_r = \gamma^0
\mathcal{P}_r \gamma^0$. The only contributing terms are those with an
odd number of $\gamma^5$ matrices and will lead to triple-products
(TP) structures, i.e. contractions between the levi-civita tensor
$\epsilon_{\alpha\beta\gamma\delta}$ with four momenta. In contrast,
it can be seen from Eq.~(\ref{eq18}) that the terms proportional to
$\kp^2$ and $\tilde{\kappa}^2_t$ contain an even number of $\gamma^5$
matrices and can be written in terms of scalar products of the
available momenta.\par
%\vspace*{-2mm}

In order to state this more clearly, we will consider the form of the
differential cross-section in terms of the momenta $q=(q_1-q_2)/2$,
$Q=(q_1+q_2)/2$, $t$, $\bar{t}$, $n_t$ and $n_{\tbar}$, where
$q_{1,2}$ denote the momenta of the gluons. Note that with this
choice, $q\cdot Q=0$ and $Q^2=-q^2=M^2_{t\tbar H}/4$, where $M_{t\tbar
  H}$ is the invariant mass of the system $t\tbar H$. From these six
vectors, fifteen TPs can be built\footnote{ We note that these fifteen
  TPs are not linearly independent (see the epsilon relations
  discussed in \cite{identities}).}, and the general form of the
production differential cross-section will be given by
%
\beq
\label{eq20}
d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)= \kp^2\,f_1(p_i\cdot p_j)+\tilde{\kappa}^2_t\,f_2(p_i\cdot p_j)+\kp\kpt\,\sum^{15}_{l=1}g_l(p_i\cdot p_j)\,\epsilon_l,
\eeq   
%
where
$\epsilon_l=\epsilon_{\alpha\beta\gamma\delta}\,p^{\alpha}_ap^{\beta}_bp^{\gamma}_cp^{\delta}_d$
denotes the $l$th TP, the Roman indices refer to any of the involved
momenta and we adopt the convention $\epsilon_{0123}=+1$. The
functions $f_{1,2}$ and $g_k$ depend only on the possible scalar
products and are therefore even under a parity transformation
($\mathrm{P}$). However, the terms linear in $\kp\kpt$ are
$\mathrm{P}$-odd due to the presence of the $\mathrm{P}$-odd
TPs. Hence, only the functions $f_{1,2}$ will contribute to the total
cross-section, whereas the TPs terms will be sensitive to the sign of
the anomalous coupling $\kpt$. From the fifteen TPs mentioned above,
we will focus on those that do not include $q$ and contain both spin
vectors $n_t$ and $n_{\tbar}$. The former is motivated in the fact
that $q$ cannot be eliminated in terms of the momenta of final state
particles (like $Q$ in virtue of momentum-energy conservation). The
latter takes into account that for $t\tbar$ production at hadron
colliders the top and antitop are not polarized but their spins are
strongly correlated and observables combining the decay products of
$t$ and $\tbar$ will be sensitive to this spin correlation
\cite{Bernreuther}.  A similar behaviour is expected in $t\tbar H$
production where it can be shown that the single-spin asymmetries
vanish \cite{Ellis,Biswas}. Hence, in order to construct observables
sensitive to the structure of the $tH$ coupling, we will prefer those
TPs that include information on the decay products of both top and
anti-top quarks. Only five of the fifteen TPs in Eq.~(\ref{eq20}) do
not involve the vector $q$ and, among these, we will focus on the
three that include both $n_t$ and $n_{\tbar}\,$:
%
\beq
\label{eqa1}
\epsilon_1\equiv\epsilon(t,\tbar,n_t,n_{\tbar}),\,\,
\vspace*{1mm}
\eeq
%
\beq
\label{eqa2}
\epsilon_2\equiv\epsilon(Q,\tbar,n_t,n_{\tbar}),
\vspace*{1mm}
\eeq
%
\beq
\label{eqa3}
\epsilon_3\equiv\epsilon(Q,t,n_t,n_{\tbar}).
\vspace*{1mm}
\eeq
%
\par

Finally, we remark that even though all the above discussion was given
within the context of $gg$-initiated production, similar conclusions
are obtained for $q\qbar$-initiated production. In particular, the
definitions of the spin vectors in Eqs.~(\ref{eq3})-(\ref{eq4}) and
the general form of $d\sigma$ introduced in Eq.~(\ref{eq20}) are valid
in both cases.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setlength{\belowdisplayskip}{10pt} \setlength{\belowdisplayshortskip}{10pt}
%\setlength{\abovedisplayskip}{10pt} \setlength{\abovedisplayshortskip}{10pt}
\bigskip
\section{$\mathrm{\mathbf{CP}}$-odd observables}
\label{sec3}
We present below three types of observables based on the TPs discussed
in Sec.~\ref{sec2}, mean values, asymmetries and angular
distributions. These observables are sensitive not only to the
magnitude of the pseudoscalar coupling $\kpt$ but also to its
sign. With the aim of testing them, we have used in all the cases a
set of $10^5$ events $\ppprocess$ simulated at parton level with
$\mathtt{MadGraph5\_aMC@NLO}$ \cite{Madgraph} at a center-of-mass
energy of $14\,\mathrm{TeV}$ for different values of the couplings
$\kp$ and $\kpt$\footnote{Although we use the same number of events in
  all the cases, the required luminosities are different since the
  cross section depends on the value of $\kpt$.}. We have used this
somewhat large number of events with the aim of determining clearly
the extent to which the proposed observables are sensitive to the NP
coupling. However, we will discuss the corresponding experimental
viability in Sec.~\ref{sec6}. Finally, we have also imposed the
following set of cuts: $p_T$ of leptons $> 10\,\mathrm{GeV}$, $|\eta|$
of leptons $< 2.5$, $|\eta|$ of b jets $< 2.5$ and $\Delta
R_{\ell\ell}>0.4$.\par Under the assumption of no other new physics
sources but the inclusion of the pseudoscalar coupling $\kpt$,
indirect contraints based on the Higgs production from gluon fusion
followed by its decay to two photons disfavour $\kp < 0$ without
resolving the degeneracy in the sign of $\kpt$ \cite{Guadagnoli}. On
the other hand, by assuming the tensor structure of the Lagrangian to
be the same as in the SM and considering a parameterization with one
universal Higgs coupling to vector bosons, $\kappa_V$, and one
universal Higgs coupling to fermions, $\kappa_f$, the measured signal
strengths provided by ATLAS and CMS collaborations are compatible with
the values predicted by the SM, ($\kappa_f=1,\kappa_V=1$). Based on
these facts, we will set the value of the scalar coupling to its SM
value, $\kp=1$, and concentrate in modifications of the value as well
as the sign of the pseudoscalar coupling. In particular, we have
analized the cases $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm
1$. However, we will give some results and comments regarding the pure
$\mathrm{CP}$-odd hypothesis ($\kp=0,\kpt=1$).
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetry}
%\bigskip
\label{sec3.1}
The first type of $\mathrm{CP}$-odd observable we will consider is the
asymmetry. For a certain TP, we define an asymmetry which gives the
balance between the number of events with $\epsilon > 0$ and those for
which $\epsilon < 0$:
%
\beq
\label{eq21}
\mathcal{A}(\epsilon)=\frac{N(\epsilon > 0)-N(\epsilon < 0)}{N(\epsilon > 0)+N(\epsilon < 0)}.
\eeq 
%
Based on the general expression given in Eq.~(\ref{eq20}), we expect
the following shape for the asymmetry,
%
\beq
\label{eq22}
\mathcal{A}(\epsilon)=\frac{A\kp\kpt}{B\kappa^2_t+C\tilde{\kappa}^2_t},
\eeq 
%
which for $\kp=1$ can be parameterized as
%
\beq
\label{eq23}
\mathcal{A}(\epsilon)=\frac{a\kpt}{1+b\tilde{\kappa}^2_t},
\eeq 
%
where the parameter $a\equiv A/B$ determines the sensitivity to the
pseudoscalar coupling, whereas $b\equiv C/B$ quantifies the deviation
from the linear behaviour.  The results for $\kp=1$ and $\kpt=0,\pm 1$
are shown in Table \ref{table1}, where the values in terms of the
corresponding statistical uncertainty are also included. It can be
seen that the considered asymmetries are useful to separate the
$\mathrm{CP}$-mixed cases from the SM case and also to discriminate
the different sign of $\kpt$, giving deviations of order $10\sigma$ in
the former case and $20\sigma$ in the latter.\par The sensitivity of
the asymmetry is quite similar for the three TPs, as can be seen by
including other values of $\kpt$ and using the expression in
Eq.~(\ref{eq23}) as fitting function (see Fig.~\ref{fig3}). In fact,
we obtain the fit parameters $(a=-0.057\pm 0.006, b=0.5\pm 0.2),
(a=-0.056\pm 0.006, b=0.5 \pm 0.2)$ and $(a=0.058\pm 0.006, b=0.6 \pm
0.2)$ for $\epsilon_1$, $\epsilon_2$ and $\epsilon_3$,
respectively. In addition, we include in Fig.~\ref{fig4} the asymmetry
for $\epsilon_1$ isolating the $gg$-initiated, $q\qbar$-initiated and
$pp$ production. We see that the asymmetry is enhanced for
$gg$-initiated production, while it is reduced and of opposite sign
for the $q\qbar$-initiated case. The asymmetry for the $pp$ case is
then dominated by the $gg$ contribution, albeit smaller due to the
$q\qbar$ contribution.
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
\renewcommand{\arraystretch}{1.4}
\begin{table}[H]
\caption{Asymmetries obtained by using $10^5$ simulated events for the
  TPs $\epsilon_1=\TPa, \epsilon_2=\TPb$ and $\epsilon_3=\TPc$ in the
  SM case and the two $\mathrm{CP}$-mixed cases defined by
  $\kp=1,\kpt=\pm 1$.}
\label{table1}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|========|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_1)$~~&$\mathcal{A}(\epsilon_1)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_2)$~~&$\mathcal{A}(\epsilon_2)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_3)$~~&$\mathcal{A}(\epsilon_3)/\sigma_{\mathcal{A}}$  \\ 
\hhline{|========|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.0315$~ & $10.0$ & $0.0332$~ & $10.5$~ & $-0.0307$~~~ & $-9.7$~~~\\[0.6mm]
\hline
$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $0.0009$~ & $0.3$~ & $-0.0011$~~~ & $-0.3$~~~\\[0.6mm]
\hline
$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $-0.0411$~~~& $-13.0$~~~ & $\,0.0378$~ & $12.0$ \\[0.6mm]
\hhline{|========|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% FIGURA 3 %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\vspace*{2.5mm}
\begin{figure}[H]
%\centering
\hspace*{-0.45cm}
\subfloat{\includegraphics[scale=0.45]{ATP1_nuevo.pdf}}
\hspace*{0.002\textwidth}
\subfloat{\includegraphics[scale=0.45]{ATP2_nuevo.pdf}} \\
%\hspace*{0.03\textwidth}
\centering
\subfloat{\includegraphics[scale=0.45]{ATP3_nuevo.pdf}}
\caption{Asymmetries for the TPs
  $\epsilon_1=\epsilon(t,\tbar,n_t,n_{\tbar})$ (top-left),
  $\epsilon_2=\epsilon(Q,\tbar,n_t,n_{\tbar})$ (top-right) and
  $\epsilon_3=\epsilon(Q,t,n_t,n_{\tbar})$ (bottom). The points
  represent the values for $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm 1$
  and the red solid line is the fitting curve.}
\label{fig3}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%%%%%%% FIGURA 4  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\vspace*{-4mm}
\begin{figure}[H]
\centering
\includegraphics[scale=0.45]{ATP1juntos_nuevo.pdf}
\caption{Asymmetry for the TP
  $\epsilon_1=\epsilon(t,\tbar,n_t,n_{\tbar})$. The dashed line (red)
  corresponds to $gg$-initiated production, the dot-dashed line (grey)
  to $q\qbar$-initiated production and the solid line (blue) to $pp$
  production.}
\label{fig4}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace*{-6mm} \par On the other hand, we have also tested various
linear combinations of the TPs $\epsilon_{1,2,3}$, with the result
that the asymmetry is enhanced in the following case:
%
\beq
\setlength{\abovedisplayskip}{9.5pt}
\setlength{\belowdisplayskip}{9.5pt}
\label{eq24}
\epsilon_4=\epsilon_3-\epsilon_2=\epsilon(Q,t-\tbar,n_t,n_{\tbar}).
\eeq
%
Note that in the $Q$ rest frame $\epsilon_4=Q^0
(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$ and the
sign of this TP is determined by the quantity
$(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$. The
values obtained for the asymmetry of this TP are shown in
\ref{table2}. We see by comparing the results in Tables \ref{table1}
and \ref{table2} that the capability of the asymmetry to separate the
two $\mathrm{CP}$-mixed hypotheses is increased by at least $3\sigma$.
\vspace{4mm}
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{4}$ for the SM case and the
  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
  values are obtained by using $10^5$ simulated events.}
\label{table2}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ \\ 
\hhline{|====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0371$~~~ & $-12$~~~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0004$~ & $0.1$ \\[0.6mm]
\hline
$1$ & $1$ & $0.0461$~ & $14\,$ \\[0.6mm]
\hhline{|====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\par Finally, it is worth noting that the asymmetry is not useful for
discriminating between the SM hypothesis ($\kp=1,\kpt=0$) and the pure
pseudoscalar hypothesis ($\kp=0,\kpt=1$) because, being linear in both
$\kp$ and $\kpt$, it is expected to vanish in these cases. However, we
will show in the next section that there exist angular distributions
derived from the TPs that are actually suitable to distinguish these
two hyphothesis.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Angular Distributions}
\label{sec3.2}
Given a certain TP, it is possible to define asocciated angular
distributions that are also sensitive to the pseudoscalar coupling
$\kpt$. In order to clarify this, let us first consider the TP
$\epsilon(t,\tbar,n_t,n_{\tbar})$. This TP can be written as
$\epsilon(t+\tbar,\tbar,n_t,n_{\tbar})$ so that in the reference frame
defined by $\vec{t}+\vec{\tbar} =0$ and $\vec{\tbar}\parallel \hat{z}$
we have
%
\beq
\label{eq25}
\epsilon(t+\tbar,\tbar,n_t,n_{\tbar})=M_{t\tbar}\,|\vec{\tbar}|\,(\vec{n}_t\times \vec{n}_{\tbar})_z=M_{t\tbar}\,|\vec{\tbar}||\vec{n}_t||\vec{n}_{\tbar}|\sin\theta_{n_t}\sin\theta_{n_{\tbar}}\sin \Delta \phi(n_t,n_{\tbar}),
\eeq
%
where $M_{t\tbar}$ is the invariant mass of the $t\tbar$ pair, the
angles $\theta_{n_t}$ and $\theta_{n_{\tbar}}$ denote the polar angles
of $\vec{n}_t$ and $\vec{n}_{\tbar}$ respectively and finally
$\Delta\phi(n_t,n_{\tbar})$ is the angular difference between the
projections of $\vec{n}_t$ and $\vec{n}_{\tbar}$ onto the plane
perpendicular to $\vec{\bar{t}}$. If we define this angle within the
range $[-\pi,\pi]$, we see from Eq.~(\ref{eq25}) that its sign will
determine the sign of the TP. In this sense, the distribution of the
number of the events with respect to the angle
$\Delta\phi(n_t,n_{\tbar})$ is related to the asymmetry of the TP,
%
\beq
\label{eq26}
\mathcal{A}(\epsilon)=1-2\frac{N(\epsilon < 0)}{N_T}\,\,\mbox{ and }\,\,\frac{N(\epsilon < 0)}{N_T}=\int^0_{-\pi}\frac{1}{N_T}\frac{dN}{d\Delta\phi(n_t,n_{\tbar})}\,d\Delta\phi(n_t,n_{\tbar}),
\eeq  
%
where $N_T$ is the total number of events. Moreover, from a certain TP
one can derive different angular distributions by considering
different reference frames, but all of these will satisfy
Eq.~(\ref{eq26}). In particular, we will analyze the following angular
distributions based on the TPs defined in Sec.~\ref{sec2}:
\begin{itemize}
\item Related to $\epsilon_1 = \TPa$ we consider
  $d\sigma/d\Delta\phi_1(n_t,n_{\tbar})$ in the rest frame of $t\tbar$
  with $\vec{\tbar}$ in the $z$-axis. The angle
  $\Delta\phi_1(n_t,n_{\tbar})$ is the angular difference between the
  projection of the spin vectors in the plane perpendicular to
  $\vec{\tbar}$.
\item Related to $\epsilon_2 = \TPb$ we consider
  $d\sigma/d\Delta\phi_2(n_t,n_{\tbar})$ in the rest frame of $Q$ with
  $\vec{\tbar}$ in the $z$-axis. The angle
  $\Delta\phi_2(n_t,n_{\tbar})$ is the angular difference between the
  projection of the spin vectors in the plane perpendicular to
  $\vec{\tbar}$.
\item Related to $\epsilon_3 = \TPc$ we consider
  $d\sigma/d\Delta\phi_3(n_t,n_{\tbar})$ in the rest frame of $Q$ with
  $\vec{t}$ in the $z$-axis. The angle $\Delta\phi_3(n_t,n_{\tbar})$
  is the angular difference between the projection of the spin vectors
  in the plane perpendicular to $\vec{t}$.
\end{itemize}
\par
%
In Fig.~\ref{fig5} we present the normalized distributions obtained
for the first case listed above with $\kp= 1,\kpt=0$
($\mathrm{CP}$-even Higgs boson), $\kp= 1,\kpt=\pm 1$
($\mathrm{CP}$-mixed Higgs boson) and $\kp= 0,\kpt=1$
($\mathrm{CP}$-odd Higgs boson). In Fig.~\ref{fig6} we display in turn
the analogous distributions for $\epsilon_2$. The distributions
correponding to $\epsilon_3$ are similar to those of $\epsilon_2$ but
with the opposite shift for $\kp=\kpt=1$ and $\kp=-\kpt=1$ and then we
do not include them here.
%%%%%%%%%%%%%%%%%%%%%%%%% FIGURA 5 %%%%%%%%%%%%%%%%%%%%%%%%%
%%%% ruta turin facultad: /home/nico/Documentos/ttbarH/Material_final/ todas las figs para abajo
\begin{center}
\vspace*{1.4mm}
\begin{figure}[H]
%\centering
\hspace*{-0.52cm}
\subfloat{\includegraphics[scale=0.45]{TP1_10_nuevo.pdf}}
\hspace*{-0.006\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP1_01_nuevo.pdf}} \\
\hspace*{-0.45cm}
%\hspace*{0.03\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP1_11_nuevo.pdf}}
\hspace*{-0.006\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP1_1-1_nuevo.pdf}}
\caption{Angular distributions associated with the TP
  $\epsilon(t,\tbar,n_t,n_{\tbar})$ for various values of
  $(\kp,\kpt)$. The error bars correspond to the statistical
  uncertainties.}
\label{fig5}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%% FIGURA 6 %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
%\vspace*{-4mm}
\begin{figure}[H]
%\centering
\hspace*{-0.52cm}
\subfloat{\includegraphics[scale=0.45]{TP2_10_nuevo.pdf}}
\hspace*{-0.006\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP2_01_nuevo.pdf}} \\
\hspace*{-0.45cm}
%\hspace*{0.03\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP2_11_nuevo.pdf}}
\hspace*{-0.006\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP2_1-1_nuevo.pdf}}
\caption{Angular distributions associated with the TP $\TPb$ for
  various values of $(\kp,\kpt)$. The error bars correspond to the
  statistical uncertainties.}
\label{fig6}
\end{figure}
\end{center}
\par As can be seen from Figs.~\ref{fig5} and \ref{fig6}, the peak of
the distributions is shifted according to the values of the couplings
$\kp, \kpt$. This shift appears to be approximately the same but with
opposite sign for $\kp=\kpt=1$ and $\kp=-\kpt=1$, distinguishing then
the sign of the pseudoscalar coupling. The last is the expected
behaviour since the asymmetry is linear in $\kpt$ (see
Sec.~\ref{sec3.1}) and the quantity $N(\epsilon < 0)/N_T$ is related
to the angular distribution according to Eq.~(\ref{eq26}). The
distributions for the SM and the pure pseudoscalar hypotheses are
clearly different. While in the former case the distributions exhibit
a minimum at $\Delta\phi_{1,2}(n_t,n_{\tbar})=0$, in the latter the
similar distributions display a peak, so that the two hypotheses can
be discriminated, in contrast to the asymmetry that vanishes for both
hypotheses. In order to quantify the mentioned shifts, we have fitted
the simulated distributions with the following function proposed in
\cite{Ellis},
%
\beq
\label{eq27}
\frac{1}{\sigma}\frac{d\sigma}{d\Delta\phi_i(n_t,n_{\tbar})}=a_0 + a_1\cos(\Delta\phi_i(n_t,n_{\tbar})+\delta),\qquad\, i=1,2,3.
\eeq
%
To the extent that this equation is exact we note that
Eq.~(\ref{eq29}) gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
this fitting function, we obtain phase shifts approximately between
$0.9$ and $1$ ($-1$ and $-0.9$) for $\kp=\kpt=1$ ($\kp=-\kpt=1$) both
for $\epsilon_1$ and $\epsilon_2$. However, the quality of the fits is
not good enough, being worse in the case of the $\epsilon_1$
distributions for which $\chi^2/\mathrm{d.o.f}$ is in the range
$1.69$-$3.86$, in contrast to the range $0.53$-$1.16$ obtained for
$\epsilon_2$. The main impact on the deviation from the functional
form proposed in Eq.~(\ref{eq27}) appears to be caused by the $\Delta
R_{ll}$ cut we have imposed. In fact, when this cut is turned off the
above ranges for $\chi^2/\mathrm{d.o.f}$ modify to $0.75$-$1.14$ and
$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions
respectively. In Tables \ref{table3} and \ref{table4} we list the
results of the fits obtained when the $\Delta R_{\ell\ell}$ cut is
relaxed. The results for the TP $\epsilon_3$ are pretty similar to
those for $\epsilon_2$ but with opposite sign in the phase shifts of
the $\mathrm{CP}$-mixed hypotheses and hence we do not include them
here. In addition, we show in Fig.~\ref{fig7} the angular
distributions along with the fit curves for both $\mathrm{CP}$-mixed
cases when no cut is imposed in $\Delta R_{\ell\ell}$.
\renewcommand{\arraystretch}{1.2}
\begin{table}[H]
\caption{Fit results for the angular distribution $d\sigma/(\sigma
  d\Delta\phi_1(n_t,n_{\tbar}))$ related to the TP
  $\epsilon_1=\epsilon(t,\tbar,n_t,n_{\tbar})$ when the $\Delta
  R_{\ell\ell}$ is turned off. Note that the parameter $a_1$ change
  its sign for $\kp=0,\kp=1$.}
\label{table3}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{3cm}|C{3cm}|C{3cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|=====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$a_0$~~&$a_1$& $\delta$~~ \\ 
\hhline{|=====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.1592 \pm 0.0006$ & $-0.0139 \pm 0.0008$ & $0.81 \pm 0.07$ \\[0.6mm]
\hline
$1$ & $0$ & $0.1595 \pm 0.0006$ & $-0.0181 \pm 0.0008$ & $0.002 \pm 0.06\,\,$ \\[0.6mm]
\hline
$1$ & $1$ & $0.1591 \pm 0.0006$ & $-0.0131 \pm 0.0008 $ & $\,-0.82 \pm 0.07\quad$  \\[0.6mm]
\hline
$0$ & $1$ & $0.1591 \pm 0.0006$ & ~~$\,0.0102 \pm 0.0008$ & $0.11 \pm 0.08$ \\
\hhline{|=====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[H]
\caption{Fit results for the angular distribution $d\sigma/(\sigma
  d\Delta\phi_2(n_t,n_{\tbar}))$ related to the TP
  $\epsilon_2=\epsilon(Q,\tbar,n_t,n_{\tbar})$ when the $\Delta
  R_{\ell\ell}$ is turned off. Note that the parameter $a_1$ change
  its sign for $\kp=0,\kp=1$.}
\label{table4}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{3cm}|C{3cm}|C{3cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|=====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$a_0$~~&$a_1$& $\delta$~~ \\ 
\hhline{|=====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.1591 \pm 0.0006$ & $-0.0146 \pm 0.0008$ & $0.73 \pm 0.06$ \\[0.6mm]
\hline
$1$ & $0$ & $0.1594 \pm 0.0007$ & $-0.0190 \pm 0.0008$ & $0.005 \pm 0.06\,\,$ \\[0.6mm]
\hline
$1$ & $1$ & $0.1592 \pm 0.0006$ & $-0.0136 \pm 0.0008 $ & $\,-0.77 \pm 0.07\quad$  \\[0.6mm]
\hline
$0$ & $1$ & $0.1591 \pm 0.0006$ & ~~$\,0.0113 \pm 0.0008$ & $0.09 \pm 0.08$ \\
\hhline{|=====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\par From Tables \ref{table3} and \ref{table4} we see that the
parameter $\delta$ is sensitive not only to the modulus of $\kpt$ but
also to its sign, as expected if Eq.~(\ref{eq26}) is taken into
account. The phase shift $\delta$ for the distribution of the angle
$\Delta\phi_1$ appears to exhibit a slightly higher sensitivity than
that obtained from the $\Delta\phi_2$-distribution, albeit both are
still compatible within the statistical uncertainties. However, it is
important to stress that the fits of the $\Delta\phi_2$-distributions
give allways smaller values for $\chi^2/\mathrm{d.o.f}$.
%%%%%%%%%%%%%%%%%%%%%%%%% FIGURA 7 %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
%\vspace*{-4mm}
\begin{figure}[H]
%\centering
\hspace*{-0.52cm}
\subfloat{\includegraphics[scale=0.45]{TP1_11_nocuts_nuevo.pdf}}
\hspace*{-0.006\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP1_1-1_nocuts_nuevo.pdf}} \\
\hspace*{-0.52cm}
%\hspace*{0.03\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP2_11_nocuts_nuevo.pdf}}
\hspace*{-0.006\textwidth}
\subfloat{\includegraphics[scale=0.45]{TP2_1-1_nocuts_nuevo.pdf}}
\caption{Angular distributions $d\sigma/(\sigma
  d\Delta\phi_1(n_t,n_{\tbar}))$ (top) and $d\sigma/(\sigma
  d\Delta\phi_2(n_t,n_{\tbar}))$ (bottom) associated with the TPs
  $\epsilon_1=\TPa$ and $\epsilon_2=\TPb$ respectively for the
  $\mathrm{CP}$-mixed cases $\kp=\kpt=1$ (left) and $\kp=-\kpt=1$
  (right) when the $\Delta R_{\ell\ell}$ cut is turned off. Also, the
  corresponding fit curves are displayed in red.}
\label{fig7}
\end{figure}
\end{center}
\par Concerning the angular distributions that can be related to the
combination $\epsilon_4$, we have analized the
$\Delta\phi(n_t,n_{\tbar})$ distribution in the $Q$ rest frame with
$H$ in the $z$-axis for various values of $\kp$ and $\kpt$. We have
found that these distributions are not described by Eq.~(\ref{eq27})
and their range of variation is larger than that of the distributions
displayed in Figs.~\ref{fig5} and \ref{fig6}. Unlike the distributions
related to $\epsilon_1$-$\epsilon_3$, those arising from $\epsilon_4$
exhibit small changes in their shapes for all the considered
hypotheses and for this reason we have not included the corresponding
plots here. However, the larger range of variation of the $\epsilon_4$
distributions leads to higher values for the asymmetry (as can be sees
from Tables \ref{table1} and \ref{table2}) even when the changes in
the respective shapes are smaller than in the case of the
distributions described by Eq.~(\ref{eq27}).  \par
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mean value}
\label{sec3.3}
We turn now to consider the last type of observables constructed from
the TPs that are sensitive to $\kpt$, the mean value. Given a certain
TP, we define its mean value in the following manner,
%
\beq
\label{eq28}
\langle \epsilon \rangle = \frac{\int\epsilon\, \{d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi\}\,d\Phi}{\int \{d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi\}\,d\Phi},
\eeq
%
where $\Phi$ is the Lorentz invariant phase space corresponding to the
final state
$b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H$. From
Eq.~(\ref{eq20}) we see that only the terms linear in $\kp$ and $\kpt$
will contribute to the mean value, so that we expect this observable
to be sensitive not only to the value but also to the relative sign of
the couplings.\par The results obtained for the TPs $\epsilon_1=
\epsilon(t,\tbar,n_t,n_{\tbar})$, $\epsilon_2=
\epsilon(Q,\tbar,n_t,n_{\tbar})$ and $\epsilon_3
=\epsilon(Q,t,n_t,n_{\tbar})$ introduced in Sec.~\ref{sec2} are
displayed in Table \ref{table5}, where we list the deviation of the
mean values from the SM case ($\kpt = 0$) in terms of the
corresponding statistical uncertainty of the estimator of $\langle
\epsilon \rangle$, $\bar{\epsilon}$.
\renewcommand{\arraystretch}{1.6}
\begin{table}[H]
\caption{Mean values obtained for the TPs $\epsilon_{1,2,3}$ for the
  SM case and two $\mathrm{CP}$-mixed cases with opposite sign in the
  pseudoscalar coupling. The values are obtained by using $10^5$
  simulated events.}
\label{table5}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}||C{2cm}||C{2cm}|}
%\hhline{|=====|}
\hhline{|-----|}
$\kappa_t$ & $\tilde{\kappa}_t$ & $\langle \epsilon_1 \rangle /\sigma_{\bar{\epsilon}_1}$ & $\langle \epsilon_2 \rangle /\sigma_{\bar{\epsilon}_2}$ & $\langle \epsilon_3 \rangle /\sigma_{\bar{\epsilon}_3}$ \\ 
\hhline{|=====|} 
%\hhline{|-----|}
%\vspace*{.5mm}
\renewcommand{\arraystretch}{1.0}
$1$~ & $-1$~~~ & $4.26$~ & $4.94$~ & $-5.81$~~~\\[0.6mm]
\hline
$1$ & $0$~ & $-0.91$~~~ & $-0.22$~~~ & $1.25$~\\[0.6mm]
\hline
$1$ & $1$~ & $-7.98$~~~ & $-8.83$~~~& $8.75$~\\[0.6mm]
\hhline{|=====|}
%\hhline{|-----|}
\end{tabular}
\end{center} 
\end{table}
We see that the three observables are capable of disinguishing the SM
case from both $\mathrm{CP}$-mixed cases. Further, the observables are
sensitive to the sign of $\kpt$ and the two $\mathrm{CP}$-mixed cases
are also clearly disentangled. The observables $\langle \epsilon_2
\rangle$ and $\langle \epsilon_3 \rangle$ appear to be slightly more
sensitive than $\langle \epsilon_1 \rangle$. On the other hand, the
mean value for the combination $\epsilon_4$ introduced in
Sec.~\ref{sec3.1} gives slightly smaller values than those listed in
Table \ref{table5}, with $-4.32, 1.11$ and $7.23$ for the cases
$(\kp=1,\kpt=-1,0,1)$ respectively. As with the asymmetry, the
hypotheses $\mathrm{CP}$-even and $\mathrm{CP}$-odd cannot be
distinguished by the mean value that is also linear in both $\kp$ and
$\kpt$ (see Eqs.~(\ref{eq20}) and (\ref{eq28})). By taking into
account the results given in Sec.~\ref{sec3.1}, we can conclude that
the sensitivity to the NP contribution is smaller for the mean values
than for the asymmetries of the TPs under consideration.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{{\boldmath $\mathrm{CP}$}-odd observables not depending on \MakeLowercase{{\boldmath $t$}} and \MakeLowercase{{\boldmath $\tbar$}} spin vectors}
\label{sec4}
So far we have considered three TPs involving the momenta $t,\tbar$
and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ given in
Eqs.~(\ref{eq3})-(\ref{eq4}). In fact, we have described the general
form of the differential cross-section in terms of these vectors in
Eq.~(\ref{eq20}). Here, we will take into account another
possibilities for the choice of the vectors from which the
$\mathrm{CP}$-odd observables can be constructed. From the definitions
in Eqs.~(\ref{eq3})-(\ref{eq4}), we see that the TPs
$\epsilon_{1,2,3}$ can be written as follows,
%
\beq
\label{eq29}
\TPa = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\,\epsilon(t,\tbar,\ell^-\!,\ell^+),
\eeq
%
\vspace*{1mm}
\beq
\label{eq30}
\TPb = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,\tbar,\ell^-\!,\ell^+)+\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(H,\tbar,t,\ell^-\!)\right)
\eeq
%
\vspace*{1mm}
\beq
\label{eq31}
\TPc = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(-\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,t,\ell^-\!,\ell^+)+\frac{(\tbar\cdot\ell^-)}{m^2_t}\epsilon(H,\tbar,t,\ell^+\!)\right).
\vspace*{2mm}
\eeq
%
The above equations express the TPs studied in the last sections as
linear combination of TPs involving the momenta $t,\tbar,H,\ell^+$ and
$\ell^-$, with coefficients that are functions of phase space
variables. These five momenta give rise to five TPs whose sensitivity
can also be tested by means of the observables introduced in
Secs.~\ref{sec3.1}-\ref{sec3.3}. In the first place, we have found
that TPs not including both lepton and anti-lepton momenta present a
negligible sensitivity, and then we will concentrate here on the
results obtained for the remaining TPs,
$\epsilon_5\equiv\epsilon(t,\tbar,\ell^-\!,\ell^+),
\epsilon_6\equiv\epsilon(H,t,\ell^-\!,\ell^+)$ and $\epsilon_7\equiv
\epsilon(H,\tbar,\ell^-\!,\ell^+)$. The Tables \ref{table6} and
\ref{table7} summarize the results for these TPs.
\renewcommand{\arraystretch}{1.6}
\begin{table}[H]
\caption{Mean values obtained for the TPs $\epsilon_{5,6,7}$ for the
  SM case and two $\mathrm{CP}$-mixed cases with opposite sign in the
  pseudoscalar coupling. The values correspond to $10^5$ simulated
  events.}
\label{table6}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}||C{2cm}||C{2cm}|}
%\hhline{|=====|}
\hhline{|-----|}
$\kappa_t$ & $\tilde{\kappa}_t$ & $\langle \epsilon_5 \rangle /\sigma_{\bar{\epsilon}_5}$ & $\langle \epsilon_6 \rangle /\sigma_{\bar{\epsilon}_6}$ & $\langle \epsilon_7 \rangle /\sigma_{\bar{\epsilon}_7}$ \\ 
\hhline{|=====|} 
%\hhline{|-----|}
%\vspace*{.5mm}
\renewcommand{\arraystretch}{1.0}
$1$~ & $-1$~~~ & $3.98$~ & $-1.96$~~~ & $1.69$~ \\[0.6mm]
\hline
$1$ & $0$~ & $-0.43$~~~ & $1.25$~ & $0.74$~ \\[0.6mm]
\hline
$1$ & $1$~ & $-6.76$~~~ & $3.46$~ & $-3.29$~~~~\\[0.6mm]
\hhline{|=====|}
%\hhline{|-----|}
\end{tabular}
\end{center} 
\end{table}
\renewcommand{\arraystretch}{1.4}
\begin{table}[H]
\caption{Asymmetries for the TPs $\epsilon_{5,6,7}$ for the SM case
  and the two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm
  1$. The values correspond to $10^5$ simulated events.}
\label{table7}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|========|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_5)$~~&$\mathcal{A}(\epsilon_5)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_6)$~~&$\mathcal{A}(\epsilon_6)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_7)$~~&$\mathcal{A}(\epsilon_7)/\sigma_{\mathcal{A}}$  \\ 
\hhline{|========|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.0315$~ & $10.0$~ & $-0.0134$~~~ & $-4.2$~~~ & $0.0111$~ & $3.5$~\\[0.6mm]
\hline
$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $-0.0011$~~~ & $-0.3$~~~ & $0.0009$~& $0.3$~\\[0.6mm]
\hline
$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $0.0143$~ & $4.5$~ & $-0.0137$~~~ & $\,-4.3$~~~  \\[0.6mm]
\hhline{|========|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\par
%
We see that the TP $\epsilon_5$ gives rise to asymmetries and mean
values that are clearly higher than those obtained from $\epsilon_6$
and $\epsilon_7$. This is in contrast to the TPs $\epsilon_{1,2,3}$,
for which the asymmetries and mean values are comparable (see Tables
\ref{table1} and \ref{table5}). We also note that the asymmetry for
$\epsilon_5$ is exactly the same as for $\epsilon_1$ as was expected
from Eq.~(\ref{eq29}) since the proportionality factor relating them
is positive definite. Regarding the mean values, we see by comparing
Tables \ref{table5} and \ref{table6} that the TPs $\epsilon_{1,2,3}$
appear to have a higher sensitivity to the pseudoscalar coupling than
$\epsilon_{5,6,7}$.  \par It is important to mention that in the
$t\tbar$ rest frame the sign of the TP $\epsilon_5$ is defined through
the angle $\Delta\phi_{\ell^-\ell^+}$ (recall the discussion on
Eq.~(\ref{eq28})), which is the angular difference between the
projections of the leptons momenta onto the plane perpendicular to
$\vec{\tbar}$. By a similar argument to that discussed at the
beginning of Sec.~\ref{sec3.2}, we can construct an associated angular
distribution that, being constrained by the $\mathcal{A}(\epsilon_5)$,
will be also sensitive to the sign of the pseudoscalar coupling. This
angular variable is nothing but that proposed in \cite{Ellis} as a
useful $\mathrm{CP}$-odd observable. Moreover, it is shown in
\cite{Ellis} that this angular distribution follows the functional
form given in Eq.~(\ref{eq27}). Due to the fact that this distribution
is constrained by $\mathcal{A}(\epsilon_5)$ which is equal to
$\mathcal{A}(\epsilon_1)$ and smaller than
$\mathcal{A}(\epsilon_{2,3})$, the corresponding shifts ($\delta$)
obtained for different values of $\kpt$ are expected to be of the same
order than those exhibited by the $\Delta\phi_1(n_t,n_{\tbar})$
distribution and somewhat smaller than those observed in the
$\Delta\phi_2(n_t,n_{\tbar})$ distribution.  \par In analogy to the
combination of TPs considered in Sec.~\ref{sec3}, we have found a
combination of the TPs $\epsilon_{5,6,7}$ for which the asymmetry is
enhanced with respect to $\epsilon_5$-$\epsilon_7$,
%
\beq
\label{eq32}
\epsilon_8 = 2\epsilon_5 -\epsilon_6 +\epsilon_7 = \epsilon(t+\tbar+H,t-\tbar,\ell^+,\ell^-).
%2\epsilon(t,\tbar,\ell^-,\ell^+)+\epsilon(H,\tbar,\ell^-,\ell^+)-\epsilon(H,t,\ell^-,\ell^+)
\eeq
%
We see from Eq.~(\ref{eq32}) that in the $t\tbar H$ rest frame
$\epsilon_8=M_{t\tbar H}(\vec{t}-\vec{\tbar})\cdot (\vec{\ell}^+\!
\times \vec{\ell}^-)$, where $M_{t\tbar H}$ is the invariant mass of
the system $t\tbar H$. Hence, in this reference frame the sign of the
combination $\epsilon_8$ is set by the quantity
$(\vec{t}-\vec{\tbar})\cdot (\vec{\ell}^+\! \times
\vec{\ell}^-)$. Taking into account Eqs.~(\ref{eq24}) and (\ref{eq32})
along with the definition $Q=(t+\tbar+H)/2$, we see that the only
relevant difference between $\epsilon_4$ and $\epsilon_8$ is that in
the latter the spin vectors $n_t$ and $n_{\tbar}$ have been replaced
by the momenta of the leptons $\ell^+$ and $\ell^-$ respectively. The
values obtained for $\mathcal{A}(\epsilon_8)$ are shown in Table
\ref{table8}. Compared to the TPs $\epsilon_5$-$\epsilon_7$ and
$\epsilon_1, \epsilon_3$ (see Tables \ref{table1} and \ref{table7}),
the chosen combination exhibits a slightly higher sensitivity in the
asymmetry for resolving the $\mathrm{CP}$-mixed cases. This is not
true in the case of the TPs $\epsilon_2$ and $\epsilon_4$, for which
the asymmetry is larger (see Tables \ref{table1}, \ref{table2} and
\ref{table8}). In particular, the comparison between $\epsilon_4$ and
$\epsilon_8$ indicates that the use of the momenta of the leptons
instead of the spin vectors produces a decrease in the sensitivity of
the asymmetry. \par From the TPs $\epsilon_5$-$\epsilon_7$ one can
derive various angular distributions in the same manner we have
discussed in Sec.~\ref{sec3.2} for $\epsilon_1$-$\epsilon_3$. Of
course, in this case the corresponding angle will be defined in terms
of the momenta of the leptons instead of using the spin vectors. These
distributions have the same behaviour than those derived from
$\epsilon_1$-$\epsilon_3$, but only the shift obtained in the case of
$\epsilon_5$ is compatible to the values given in Tables for
$\epsilon_1$-$\epsilon_3$. The shifts resulting from the fit of the
distributions related to $\epsilon_6$ and $\epsilon_7$ are
smaller. Taking into account these facts we do not give further
details of the angular distributions for the TPs discussed in this
section.\par The mean value of $\epsilon_8$ for the hypotheses under
consideration is comparable with the values listed in Table
\ref{table6} for $\epsilon_5$. Concerning the associated angular
distributions, their range of variation is larger than in the case of
the distributions related to $\epsilon_5$-$\epsilon_7$ but exhibit
smaller changes in their shapes for the different hypothesis and for
this reason we do not include here the corresponding plots.
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{8}$ for the SM case and the
  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
  values are obtained with $10^5$ simulated events.}
\label{table8}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_8)$~~&$\mathcal{A}(\epsilon_8)/\sigma_{\mathcal{A}}$ \\ 
\hhline{|====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.0331$~ & $10.5$~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0023$~ & $0.7$~ \\[0.6mm]
\hline
$1$ & $1$ & $-0.0403$~~~ & $\,-12.7$~~~~ \\[0.6mm]
\hhline{|====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\section{{\boldmath{$\mathrm{CP}$}}-odd observables not depending on \MakeLowercase{{\boldmath $t$}} and \MakeLowercase{{\boldmath $\tbar$}} momenta}
\label{sec5}
All the observables discussed in the above sections involve the
momenta of the top and anti-top quarks thus requiring the full
reconstruction of the kinematics of the individual $t$ and $\tbar$
systems in order to be measured. Although challenging due to the
presence of two neutrinos in the final state, this can be in principle
done by applying a kinematic reconstruction method such that the
neutrino weighting technique \cite{atlasconf,atlascharge}. Another
possibility is to define observables that are not dependent on the $t$
and $\tbar$ momenta but make use of the quarks $b$ and $\bbar$. In
order to construct such observables we will modify here the most
sensitive observables studied in Secs.~\ref{table3} and \ref{sec4},
namely the combinations $\epsilon_4$ and $\epsilon_8$
respectively. Let us first consider the combination $\epsilon_8$
defined in Eq.~(\ref{eq32}) and replace the top and antitop momenta by
the bottom and antibottom momenta respectively. Thus, we define
%
\beq
\label{eq33}
\epsilon_9 = \epsilon(b+\bbar+H,b-\bbar,\ell^+,\ell^-).
\eeq
%
Note that now the sign of the TP $\epsilon_9$ is set by the sign of
the quantity $(\vec{b}-\vec{\bbar})\cdot(\vec{\ell}^+\!\times
\vec{\ell}^-)$ in the $b\bbar H$ rest frame. This quantity is in fact
used in \cite{Guadagnoli} but in the lab frame in order to define a
$\mathrm{CP}$-odd observable that only depends on lab frame
variables. The values of the asymmetry for $\epsilon_9$ are listed in
Table \ref{table9}. By comparing Tables \ref{table8} and \ref{table9}
we see that the use of the $b,\bbar$ instead of $t,\tbar$ leads to a
decrese in the sensitivity of the asymmetry by $\sim 5\sigma$ for
$\kp=1,\kpt=\pm 1$. However, the observable is still capable of
discriminating not only between the two $\mathrm{CP}$-mixed hypotheses
but also between these and the SM case.
%\newpage
We proceed now in a similar way with the combination $\epsilon_4$. By
using Eq.~(\ref{eq24}) along with the definitions of the spin vectors
in Eqs.~(\ref{eq3})-(\ref{eq4}), we can write
%
\beq
\label{eq34}
\epsilon_4 = \frac{m^2_t}{(t\cdot\ell^+)\cdot(\tbar\cdot\ell^-)}\,\epsilon(Q,t-\tbar,\ell^-,\ell^+)+\frac{1}{(t\cdot\ell^+)}\,\epsilon(Q,t,\ell^+,\tbar)-\frac{1}{(\tbar\cdot \ell^-)}\,\epsilon(Q,\tbar,t,\ell^-).
\eeq
%
Since the asymmetry is not changed by an overall positive definite
factor, we will concentrate in the following combination arising from
the expression in Eq.~(\ref{eq34}),
%
\beq
\label{eq35}
\epsilon(Q,t-\tbar,\ell^-,\ell^+)+\frac{(\tbar\cdot \ell^-)}{m^2_t}\epsilon(Q,t,\ell^+,\tbar)-\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(Q,\tbar,t,\ell^-),
\eeq
%
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{9}$ for the SM case and the
  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
  values are obtained with $10^5$ simulated events.}
\label{table9}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_9)$~~&$\mathcal{A}(\epsilon_9)/\sigma_{\mathcal{A}}$ \\ 
\hhline{|====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.0171$~ & $5.4$~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0010$~ & $0.3$~ \\[0.6mm]
\hline
$1$ & $1$ & $-0.0247$~~~ & $\,-7.8$~~~~ \\[0.6mm]
\hhline{|====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\noindent
%
and instead of replacing $t$ and $\tbar$ directly by $b$ and $\bbar$,
we use their visible parts, namely $b+\ell^+$ and $\bbar +\ell^-$
respectively. This results in the following definition
%
\beq
\label{eq36}
\epsilon_{10}=\epsilon(\tilde{Q},c_{b\bbar}\,,\ell^-,\ell^+)-w_1\,\epsilon(\tilde{Q},b,\bbar,\ell^+)+w_2\,\epsilon(\tilde{Q},b,\bbar,\ell^-),
\eeq
%
where $\tilde{Q}\equiv (b+\ell^+\!+\bbar +\ell^-)/2$ stands for the
visible part of $Q$, $c_{b\bbar}=(1-w_1)\,b-(1-w_2)\,\bbar$ and the
weights $w_{1,2}$ are given by $(\bbar\cdot \ell^-)/m^2_t $ and
$(b\cdot \ell^+)/m^2_t$ respectively. Also, the contribution
$m^2_{\ell}/m^2_t$ has been neglected both in $w_1$ and in $w_2$. Note
that if we set $w_1=w_2=0$, the combination $\epsilon_{10}$ reduces to
$\epsilon_9 /2$ and $\mathcal{A}(\epsilon_{10})$ becomes equal to
$\mathcal{A}(\epsilon_9)$. The results obatined for the asymmetry of
$\epsilon_{10}$ are given in Table \ref{table10}. By comparing Tables
\ref{table2} and \ref{table10} we see again that the sensitivity of
the asymmetry decreases when $t$ and $\tbar$ are not included in the
TP. Nevertheless, the combination $\epsilon_{10}$ remains a useful
observable for discriminating the $\mathrm{CP}$ nature of the Higgs
boson, with the corresponding asymmetry having a sensitivity even
higher than that of $\epsilon_9$, as can be checked by taking into
account Tables \ref{table9} and \ref{table10}. More precisely, the
separation between the $\mathrm{CP}$-mixed hypotheses is enhanced by
about $3\sigma$. This improvement in the asymmetry of $\epsilon_{10}$
with respect to $\epsilon_9$ may be due to two facts. In the first
place, as was pointed out in Sec.~\ref{sec4} when comparing the TPs
$\epsilon_4$ and $\epsilon_8$, the asymmetry appears to be higher when
the spin vectors are used instead of the lepton momenta and we see
from Eqs.~(\ref{eq33}) and (\ref{eq36}) that $\epsilon_{10}$, being
obtained from $\epsilon_4$, contains the information on the spin
vectors, as opposed to $\epsilon_9$ that depends directly on the
lepton momenta because it is derived from $\epsilon_8$. In the second
place, in order to obtain $\epsilon_{10}$ we have replaced in the
expression for $\epsilon_4$ the top and antitop momenta by their
visible part, while in the case of $\epsilon_9$ the bottom and
antibottom momenta have been used.
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{10}$ for the SM case and the
  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
  values are obtained by using $10^5$ simulated events.}
\label{table10}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ \\ 
\hhline{|====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0213$~~~ & $-6.7$~~~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0031$~ & $1.0$~ \\[0.6mm]
\hline
$1$ & $1$ & $0.0300$~ & $9.5$~ \\[0.6mm]
\hhline{|====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\par
%
By using our set of simulated events we have also tested, for
comparison purposes, the asymmetry of the lab frame observable given
in \cite{Guadagnoli}. We have obtained that this observable appears to
be slightly less sensitive than the combination $\epsilon_{10}$,
giving rise to a separation between the $\mathrm{CP}$-mixed hypotheses
smaller by about $1.4\sigma$.
\section{Experimental Feasibility}
\label{sec6}
%
By considering the mild selection cuts introduced in Sec.~\ref{sec3},
the SM cross section for $\ppprocess$, $\ell=e,\mu$ at
$14\,\mathrm{TeV}$ is $\sim 15.3\,\mathrm{fb}$ and hence the number of
events expected within the context of the HL-LHC is $\sim
15.3\,\mathrm{fb} \times 3000\,\mathrm{fb}^{-1} = 4.59\times
10^4$. This number is expected to be even larger in the case of
$\kp=1,\kpt\neq 0$ since the corresponding cross section is then
higher than the SM one. By taking into account NLO corrections to the
production process and considering a $K$-factor around $1.2$
\cite{Dawson,Beenakker,Dittmaier}, the number of events can be raised
up to $\sim 5.49 \times 10^4$. On the other hand, additional cuts as
well as the efficiency related to the reconstruction of particles
momenta will contribute to decrease this number. For instance, in
order to obtain the asymmetry of $\epsilon_4$, the $t$ and $\tbar$
momenta need to be reconstructed. This is challenging not only due to
the presence of two neutrinos in the final state which escape the
detector undetected but also because final state objects need to be
asocciated with the respective parent quark \cite{atlasconf}. As was
already mentioned in Sec.~\ref{sec5}, a possibility is to use the
neutrino weighting technique along with the kinematic equations
arising from kinematic constraints related to the top and $W$ masses
as well as from the energy-momentum conservation at each of the decay
vertices involved in the process. Within the context of $t\tbar$ this
procedure has been used, for instance, in order to obtain measurements
of spin correlation \cite{atlasconf} and charge asymmetry
\cite{atlascharge}. Also, events reconstructed with this technique has
been used in \cite{dosSantos} for analyzing angular distributions that
are useful for discriminating the signal from the backgrounds in
$t\tbar H (H\rightarrow b\bbar)$. In all these cases the corresponding
efficiency in the reconstruction of the momenta is up to $\sim 80
\%$.\par Based on the discussion given in the previous paragraph, we
have simulated sets of $5\times 10^4, 1\times 10^4$ and $5\times 10^3$
events and recalculated the most sensitive observable, namely
$\mathcal{A}(\epsilon_4)$, for each case. The results are displayed in
Table \ref{table11}, where it can be seen that for a number of events
close to that roughly estimated above within the context of the
HL-LHC, the observable is still sensitive to $\kpt$ allowing to
separate the $\mathrm{CP}$-mixed cases by $19\sigma$. As expected, the
sensitivity worsen as the number of events is reduced, but even with
$5\times 10^3$ events the separation between the $\mathrm{CP}$-mixed
hypotheses under consideration is around $6.5\sigma$. \par Although
the combination $\epsilon_{10}$ discussed in Sec.~\ref{sec5} avoids
the problem of reconstructing the top and antitop momenta, we have
also considered the respective asymmetry obtained for more
conservative numbers of events. In Table \ref{table12} we show the
results for $\mathcal{A}(\epsilon_{10})$ when the number of events is
reduced from $5\times 10^4$ to $1\times 10^4$. We see in this case
that even with $1\times 10^4$ simulated events the observable is
capable to discriminate the $\mathrm{CP}$-mixed cases by
$5.6\sigma$.\par Finally, it is important to mention that a realistic
analysis of the sensistivity of the observables discussed in this
paper requires the study of the impact of the backgrounds as well as
the hadronization of the quarks in the final state and the effects of
the detector. If we consider the dominant decay mode of the higgs,
$H\rightarrow b\bbar$, in order to maximize the cross section of the
process, the signature is given by $4$ $b$-jets, two leptons and
missing energy, while the main background arise from the production of
$t\tbar$ in asocciation with additional jets, being the dominant
source the production of $t\tbar + b\bbar$. By applying a small set of
cuts it is shown in \cite{chinos} that the
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_4$ obtained by using $5\times
  10^4, 1 \times 10^4$ and $5\times 10^3$ simulated events for the SM
  case and the two $\mathrm{CP}$-mixed cases defined by
  $\kp=1,\kpt=\pm 1$. }
\label{table11}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|========|}
%\hhline{|--------|}
\multirow{2}{*}{$\kappa_t$} & \multirow{2}{*}{$\tilde{\kappa}_t$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=5\times 10^4$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=1\times 10^4$} & \multicolumn{2}{c|}{$N_{\mathrm{ev}}=5\times 10^3$} \\ \cline{3-8}
& & $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_4)$~~&$\mathcal{A}(\epsilon_4)/\sigma_{\mathcal{A}}$ \\
\hhline{|========|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0405$~~~ & $-9.1$~~~ & $-0.0426$~~~ & $-4.3$~~~ & $-0.0496$~~~ & $-3.5$~~~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0004$~ & $0.1$~ & $-0.0084$~~~ & $-0.8$~~~ & $-0.0004$~~~ & $-0.03$~~~ \\[0.6mm]
\hline
$1$ & $1$ & $0.0443$~ & $9.9$~ & $0.0434$~ & $4.2$~ & $\,0.0420$~ & $3.0\,\,$ \\
\hhline{|========|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{10}$ in the SM case and the
  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$ when the
  number of simulated events is reduced from $5\times 10^4$ to $1
  \times 10^4$.}
\label{table12}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|======|}
%\hhline{|--------|}
\multirow{2}{*}{$\kappa_t$} & \multirow{2}{*}{$\tilde{\kappa}_t$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=5\times 10^4$} & \multicolumn{2}{c|}{$N_{\mathrm{ev}}=1\times 10^4$} \\ \cline{3-6}
& & $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ \\
\hhline{|======|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $-0.0270$~~~ & $-6.0$~~~ & $-0.0184$~~~ & $-1.8$~~~  \\[0.6mm]
\hline
$1$ & $0$ & $0.0022$~ & $0.5$~ & $-0.0086$~~~ & $-0.9$~~~  \\[0.6mm]
\hline
$1$ & $1$ & $0.0313$~ & $7.0$~ & $0.0380$~ & $3.8\,$ \\
\hhline{|======|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\noindent
%
signal to background ratio is largely improved. On the other hand, a
rigorous treatment of the backgrounds and their impact with respect to
the signal is performed in \cite{atlasger} by using $20.3\,
\mathrm{fb}^{-1}$ of data at $\sqrt{s}=8\,\mathrm{TeV}$.  \par The
results shown in tables \ref{table11} and \ref{table12} reveal that
with $5\times 10^3$ and $1\times 10^4$ events respectively the
observables $\mathcal{A}(\epsilon_4)$ and $\mathcal{A}(\epsilon_{10})$
are still useful for testing $\kpt$. Without considering the lack of
events related to the experimental analysis, these numbers of events
correspond to a luminosity around $\sim
300\,$-$\,600\,\mathrm{fb}^{-1}$ for the SM and even smaller for the
$\mathrm{CP}$-mixed cases due to the larger cross section. This range
of luminosities is in principle achievable in the short term by the
LHC. We note that in order to be fully conclusive about the required
luminosity, it is important to include the effects of hadronization,
detector resolution, reconstruction eficciencies and so
forth. However, this kind of analysis is out of the scope of this
paper.
%%%%%%%%%%%% with Cuts
%51.46/17 -0.02 +- 0.08
%45.48/17  -1.09 +- 0.07
%65.60/17   0.96 +- 0.08
%28.84/17   0.02 +- 0.07
%%%%%%%
%9.13/17     0.01 +- 0.06
%9.05/17     -0.98 +- 0.07
%19.7/17     0.80 +- 0.07
%16.59/17    0.06 +- 0.07
%
%%%%%%%%%%%% without Cuts
%16.36/17    0.0022 +-0.06
%15.25/17    -0.82 +- 0.07
%12.80/17    0.81 +- 0.07
%19.38/17    0.11 +- 0.08
%%%%%%
%7.45/17    0.005 +- 0.06
%18.17/17   -0.77 +- 0.07
%9.59/17    0.73 +- 0.06
%12.39/17   0.09 +- 0.08
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec7}
%
In this paper we have presented a collection of $\mathrm{CP}$-odd
observables based on triple product correlations that are useful for
disentangling the relative sign between the scalar ($\kp$) and a
potential pseudoscalar ($\kpt$) top-Higgs couplings in the $t\tbar H$
production with both tops decaying leptonically. We have tested the
sensitivity of the proposed observables by considering three types of
observables: asymmetries, mean values and angular distributions.\par

Through the use of spinor techniques we have written the expression
for the differential cross section of the full process in such a
manner that the production and the decay parts are separated, although
connected by the spin vectors of the top and antitop which are given
in terms of the momenta of the leptons in the final state. Moreover,
we have indentified the terms linear in $\kp$ and $\kpt$ as those
involving TPs. Among these, we have explored the three that do not
involve the momenta of the incoming quarks/gluons and at the same time
incorporate both spin vectors: $\epsilon_1\equiv \TPa$,
$\epsilon_2\equiv \TPb$ and $\epsilon_3\equiv \TPc$.\par We have found
that $\epsilon_{1,2,3}$ allow to distinguish between the
$\mathrm{CP}$-mixed hypotheses by more than $\sim 20\sigma$ in the
case of asymmetries and $\sim 10\sigma$ in the case of mean values
when $1 \times 10^5$ simulated events are used. Furthermore, we have
shown that the angular distributions asocciated with these TPs are
also sensitive to the value of $\kp$ and $\kpt$ exhibiting a phase
shift that varies according to the values taken by these couplings. On
the other hand, by exploring TPs that incorporate the momenta of the
Higgs and the leptons instead of the spin vectors we can conclude that
the observables studied here appear to be more sensitive when the spin
vectors are used.\par

On the other hand, we have proposed a combination of the TPs
considered in the first place, $\epsilon_4\equiv
\epsilon_3-\epsilon_2$, that exhibits the highest sensitivity with the
separation between the $\mathrm{CP}$-mixed hypotheses being increased
by at least $3\sigma$ in the asymmetry for $1 \times 10^5$ events with
respect to $\mathcal{A}(\epsilon_{1,2,3})$. Again, when a similar
combination is constructed by using the leptons momenta instead of the
spin vectors ($\epsilon_8$), the sensitivity in the asymmetry is
decreased by $\sim 3\sigma$ compared to $\mathcal{A}(\epsilon_4)$ for
the same number of events, giving values compatible with those
obtained for the asymmetry of $\epsilon_2$ and $\epsilon_3$. \par

Taking into account the challenge of reconstructing the top and
antitop momenta due to the presence of two neutrinos in the final
state, we have proposed and tested two TP correlations that avoid this
difficulty. The first one is obtained by replacing the $t$ and $\tbar$
by the $b$ and $\bbar$ momenta ($\epsilon_9$), whereas the second
includes the visible part of the $t$ and $\tbar$ momenta
($\epsilon_{10}$). We have encountered that the latter is the most
sensitive leading to a discrimination of the $\mathrm{CP}$-mixed cases
under analysis by up to $\sim 16\sigma$.\par

Finally we have discussed the feasibility of the most sensitive
observables proposed here. We have found that with $5\times 10^3$ and
$1\times 10^4$ events respectively the observables
$\mathcal{A}(\epsilon_4)$ and $\mathcal{A}(\epsilon_{10})$ are still
useful for testing the hypotheses $(\kp=1,\kpt=\pm 1)$ giving rise to
separations of order $\sim 6\sigma$. These required number of events
would be reachable in principle in the short term by the LHC and hence
the capability of the observables studied here for testing the sign of
$\kpt/\kp$ could be probed in that context.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\noindent
{\bf Acknowledgments}
\noindent 
This work has been partially supported by ANPCyT under grants No. PICT
2013-0433 and No. PICT 2013-2266, and by CONICET (NM, AS). The work of
KK was supported by the U.S.  National Science Foundation under Grant
PHY-1215785. KK also acknowledges sabbatical support from Taylor
University.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{\refname}
\let\bibsection\relax

\setlength{\bibsep}{10pt}
\bibliography{PaperDraftbiblio}
\bibliographystyle{apsrev4-1}

\end{document}

### 2016-02-10 Paper_ttbarH_Draft.tex
Edits to abstract and first part of introduction

@@
 \author{Daniel Crane \vspace*{4mm}}
-\email{\hlkk{dkcrane@mtu.edu}}
+\email{dkcrane@mtu.edu}
 \tayloru
@@
 \author{Ethan Gegner}
-\email{ethan_gegner@taylor.edu}
+\email{ethan\_gegner@taylor.edu}
 \tayloru
@@
 sensitive to the corresponding relative sign. The proposed observables
-are based on triple products (TP) structures that we extract from the
-expression of the differential cross section in terms of the spin
-vectors of the top and antitop quarks. In order to explore other
-possibilities, we progressively modify these TPs, firstly, by
-combining them and then by replacing the spin vectors by the lepton
-momenta or the $t$ and $\tbar$ momenta by their visible parts. We
-obtain that the most promising observable can disentangle the
-hypotheses $\kp=1,\kpt=\pm 1$ by more than $\sim 20\sigma$ for $10^5$
-events that is within the expected order of magnitude of events at the
-HL-LHC. In the case of observables that do not need the reconstruction
-of the $t$ and $\tbar$ momenta, the power of discrimination is up to
-$\sim 16\sigma$ for the same ammount of events. We also show that the
+are based on triple product (TP) structures that we extract
+from the expression of the differential cross section in terms of the
+spin vectors of the top and antitop quarks. In order to explore other
+possibilities, we progressively modify these TPs, first
+by combining them, and then by replacing the spin vectors by the
+lepton momenta or the $t$ and $\tbar$ momenta by their visible parts.
+Assuming an integrated luminosity that is consistent with that
+  envisioned for the HL-LHC, we find that the most
+promising observable can disentangle the hypotheses $\kp=1,\kpt=\pm 1$
+by more than $\sim 20\sigma$.  In
+the case of observables that do not need the reconstruction of the $t$
+and $\tbar$ momenta, the power of discrimination is up to $\sim
+16\sigma$ for the same number of events. We also show that the
 capability of the most promising observables for separating the
 $\mathrm{CP}$-mixed hypotheses preveals even when a number of events
-plausible within the short term LHC is considered.
+plausible within the short term LHC is considered. {\bf (KK: reword last sentence a bit.)}
 
@@
 CMS \cite{cmsH} collaborations, it has become of crucial importance
-its characterization, namely the determination of its physical
-properties with the highest possible precision. Among the features of
-the new boson that are under investigation, the study of its couplings
-to the fermions is of great relevance, allowing us to study the nature
-of $H$ under the discrete symmetry $\mathrm{CP}$ and to clarify the
-extent to which this new particle is consistent to the Higgs boson
-predicted by the Standard Model (SM) of particle physics. In
-particular, the test of the Higgs coupling to the heaviest fermion,
-the top quark, is a priority since on the one hand, it rules the main
-production mechanism through gluon fusion and contributes to the
-important decay mode to two photons, and on the other hand, it is
-involved in the scalar-field naturalness problem giving rise to the
+ to determine its physical
+ properties with the highest possible precision.
+ The study of the new boson's couplings
+ to fermions is of great relevance
+ and will allow us to better understand this particle's $\mathrm{CP}$-transformation
+   properties, as well as the
+extent to which this particle is consistent with the Higgs boson
+predicted by the Standard Model (SM) of particle physics.
+It is particularly important to test the coupling of the putative ({\bf (KK: at some point
+  should we just start calling this the Higgs?  How do we make that transition?)}
+Higgs boson to
+the top quark.  This coupling governs
+the main Higgs boson production mechanism (which proceeds via gluon fusion)
+and it contributes to the
+important Higgs boson decay mode to two photons.
+It is also
+involved in the scalar-field naturalness problem -- giving rise to the
 leading dependence on the cut-off energy scale in the corrections to
-the Higgs mass and it may play an important role in the EWSB
-mechanism.\par
-
-Given the fact that the main Higgs boson production
-process, the gluon fusion, is dominated by a top quark loop and that
+the Higgs mass -- and it may play an important role in the EWSB {\bf KK: define EWSB?}
+mechanism.  {\bf (KK: I reworded a lot of this paragraph -- is it still
+  correct, or did I accidentally alter the meaning?)}\par
+
+Given that the main Higgs boson production
+process is dominated by a top quark loop and that
 the diphoton and digluon decay channels are also mediated by a top
@@
 pseudoscalar $tH$ couplings, $\kp$ and $\kpt$
-\cite{constraints1,constraints2, constraints3,constraints4}. However,
+\cite{constraints1,constraints2, constraints3,constraints4}.
+     {\bf (KK: OK to drop ``gluon fusion'' here, since we already said it was
+       the main production process above?  Alternatively, we could say it here
+       and skip it above.)}
+     However,
 these constraints assume that there are no other sources contributing
-to the corresponding effective couplings and, in the case of the
-diphoton decay channel which also involves a $W$ boson loop, that the
+to the corresponding effective couplings; furthermore, in the case of the
+diphoton decay channel (which also involves a $W$ boson loop), it is also
+assumed that the
 coupling of the Higgs boson to the $W$ is standard. In this sense, the
 constraints derived from measurements of Higgs rates are indirect
-constraints. In this direction, electric dipole moments (EDM) can also
+constraints. Electric dipole moments (EDM) can also
 impose stringent indirect constraints on $\kpt$ by assuming that there
@@
 predicted by the SM \cite{constraints1,edm}. In order to probe
-directly the $tH$ coupling, processes with smaller cross sections need
+the $tH$ coupling directly, processes with smaller cross sections need
 to be taken into account.  \par
@@
 $\mathrm{CP}$-odd hypothesis ($\kp=0,\kpt=1$).
-\newpage
+%\newpage
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Since the asymmetry is not changed by an overall positive definite
-factor, we will concentrate in the following combination arising from
+factor, we will concentrate on the following combination arising from
 the expression in Eq.~(\ref{eq34}),

### 2016-02-15 Paper_ttbarH_Draft.tex

@@
 predicted by the Standard Model (SM) of particle physics.
-It is particularly important to test the coupling of the putative ({\bf (KK: at some point
+It is of particular importance to test the coupling of the putative ({\bf (KK: at some point
   should we just start calling this the Higgs?  How do we make that transition?)}
@@
 coupling of the Higgs boson to the $W$ is standard. In this sense, the
-constraints derived from measurements of Higgs rates are indirect
-constraints. Electric dipole moments (EDM) can also
+constraints derived from measurements of Higgs boson decay rates
+{\bf (KK: correct to add ``boson decay'' here?)} are indirect
+constraints. Electric dipole moments (EDMs) {\bf (KK: delete ``EDM'' since we
+  never use it again?)} can also
 impose stringent indirect constraints on $\kpt$ by assuming that there
@@
 
-In contrast to the $\tau H$ coupling which can be studied trough the
-decay $H\rightarrow \tau^+\tau^-$ \cite{tau}, the $tH$ coupling is
-tested directly by making use of the production processes since the
-phase space forbids the Higgs to decay to the pair $t\tbar$. The
-production of the Higgs boson in association with the pair $t\tbar$
-and the production in association with a single top or antitop are the
-only two direct ways of probing the $tH$ coupling. The cross section
-of the single top (antitop) production is smaller and it is given by
+In contrast to the $\tau H$ coupling, which can be studied through the
+decay $H\rightarrow \tau^+\tau^-$ \cite{tau},
+the $tH$ coupling can only be tested directly via production processes, since the
+Higgs boson is kinematically forbidden from decaying to a $t\tbar$ pair.
+Two types of processes are of particular interest in this regard -- the
+production of a Higgs boson in association with a $t\tbar$ pair
+and in association with a single top or antitop. The cross section
+for associated Higgs production with a single top (antitop)
+{\bf (KK: did I phrase this correctly, calling it ``associated production'' in this way?)}
+is smaller than that for production with a $t\tbar$ pair, and involves
 the interference between a diagram in which the Higgs is radiated from
-the top (antitop) leg and one with the Higgs emmited from the
-intermediate virtual $W$ boson. This then implies that the contraints
-over $\kp$ and $\kpt$ derived from $tH$ and $\tbar H$ production are
-dependent on the asummption made on the coupling of the Higgs to the
-gauge boson $W$, $\kappa_W$. However, it is important to note that the
-interference between the above mentioned diagrams present in $tH$
-($\tbar H$) production can be exploited in order to determine the
+the top (antitop) leg and one with the Higgs emitted from the
+intermediate virtual $W$ boson. Interestingly, this implies that the contraints
+on $\kp$ and $\kpt$ derived from $tH$ and $\tbar H$ production are
+dependent on the assumption made regarding the coupling of the Higgs boson to the
+$W$ gauge boson, $\kappa_W$. Nevertheless, it is important to note that the
+interference between the above mentioned diagrams
+can be exploited to determine the
 relative sign between $\kp$ and $\kappa_W$ (see for example
-\cite{tHmaltoni}). From the point of view of $t\tbar H$ production,
-several observables sensitive to the couplings $\kp$ and $\kpt$ has
-been proposed. Examples of such observables are the cross section, the
+Ref.~\cite{tHmaltoni}).  Associated Higgs production with a
+$t\tbar$ pair has been studied by several authors {\bf (KK: true?)}, and
+various observables sensitive to the couplings $\kp$ and $\kpt$ have
+been proposed. Examples of such observables (all of which are
+$\mathrm{CP}$-even) are the cross section, 
 invariant mass distributions, the transverse Higgs momentum
-distribution or the azymuthal-angle separation between $t$ and $\tbar$
-just to name a few \citep{Guadagnoli}. An approach based on weighted
-moments and optimal observables has been developed in \cite
+distribution and the azimuthal angular separation between the $t$ and $\tbar$,
+to name a few \citep{Guadagnoli}. Also, an approach based on weighted
+moments and optimal observables has been developed in Ref.~\cite
 {Gunion1,*Gunion2,*Gunion3,*Gunion} to discriminate the hypothesis of
 a $\mathrm{CP}$-even Higgs from that of a $\mathrm{CP}$-mixed state
-within the context of a $e^+ e^-$ as well as a $pp$ collider. All the
-mentioned observables are $\mathrm{CP}$-even and hence are not
-sensitive to relative sign between the scalar and pseudoscalar
+within the context of an $e^+ e^-$ as well as a $pp$ collider.
+{\bf (KK: is this last one CP even, too?)}  Now, $\mathrm{CP}$-even observables are not
+sensitive to the relative sign between the scalar and pseudoscalar
 couplings $\kp$ and $\kpt$. Such observables are quadratically
-dependent on these couplings and then only provide an indirect measure
+dependent on these couplings and thus only provide an indirect measure
 of $\mathrm{CP}$ violation. In order to be sensitive to the relative
@@
 
-Since the quark top decays before it can hadronize, its spin
-information is passed on to the angular distributions of the decay
-products in such a way that these particles work as spin analyzers
-being the lepton the most powerful. On the other hand, it has been
-shown that in $t\tbar$ production the top quark and antiquark spins
-are strongly correlated \cite{Mahlon1,*Mahlon2,*Mahlon3,*atwood} and
-this manifests in the double angular distributions of the decay
-products of the $t$ and $\tbar$ systems. These correlations are
-dependent in turn on the production mechanism and in the case of
-$t\tbar H$ associated production are sensitive to the manner in which
-the top couples to the Higgs boson. In fact, observables that exploit
-the differences on the $t\tbar$ spin configurations are used in
-\cite{Biswas} to improve the discrimination of the $t\tbar H$ signal
-from the dominant irreducible background $t\tbar b\bbar$, in which the
-Higgs boson is not involved. \par
-
-In this paper, we define a set of observables linearly dependent on
-$\kp$ and $\kpt$ and hence sensitive to the relative sign of these
+Since the top quark decays before it can hadronize, its spin
+information is passed on to the angular distributions of its decay
+products in such a way that these particles work as spin analyzers.
+As is well known {\bf (ref)}, in the case of semileptonic top decay,
+the charged lepton is the most powerful in this regard.
+It is also known that the top quark and antiquark spins
+are highly correlated in $t\tbar$ production\cite{Mahlon1,*Mahlon2,*Mahlon3,*atwood},
+a feature that
+is manifested in the double angular distributions of the decay
+products of the $t$ and $\tbar$ systems {\bf (ref)}.
+%The spin correlations
+%between the $t$ and $\tbar$ are
+%dependent in turn on the $t\tbar$ production mechanism, and in
+In the case of
+$t\tbar H$ associated production, the $t\tbar$ spin correlations
+are also sensitive to the manner in which
+the top couples to the Higgs boson. {\bf (KK: Did I simplify this too much?
+  It seemed to repeat the previous idea a bit, but maybe I was misunderstanding it.)}
+In fact, observables that exploit
+the differences in the $t\tbar$ spin configurations were used in
+Ref.~\cite{Biswas} to improve the discrimination of the $t\tbar H$ signal
+from the dominant irreducible background $t\tbar b\bbar$, which does not
+involve the Higgs boson. {\bf (KK: did I preserve the physics meaning
+  correctly when I reworded this?)}
+
+In this paper, we define a set of observables that are linearly dependent on
+$\kp$ and $\kpt$ and are thus sensitive to the relative sign of these
 couplings. The proposed observables are based on a particular set of
-triple product structures (TP) that we extract naturally from the
-expression of the differential cross section, which makes use in turn
-of the fact that the kinematics of the decay products contain the
-information on the $t$ and $\tbar$ spins and thus is sensitive to the
-nature of the $tH$ coupling, just as was discussed in the previous
-paragraph. By using spinor thechniques we simply relate the top quark
-and antiquark spin vectors and the corresponding final state particle
+triple product (TP) structures that we extract naturally from the
+expression for the differential cross section for {\bf (name of process)},
+making use of the fact that the $t$ and $\tbar$ decay products
+contain spin information and are sensitive to the
+nature of the $tH$ coupling, as noted above.
+By using spinor techniques we relate the top
+and antitop spin vectors to final state particle
 momenta and separate the production process from the decay which
 allows to identify straightforwardly the contributions linearly
-sensitive to the couplings. Further, the TPs correlations in these
+sensitive to the couplings. {\bf (KK: can we simplify the previous
+  sentence?)}  Further, the TPs correlations in these
 contributions incorporate the $t$ and $\tbar$ spin vectors. Starting
@@
 types of observables by using simulated events: asymmetries, mean
-values and angular distributions. We note that TP correlations has
+values and angular distributions. We note that TP correlations have
 been used in \cite{Valencia1,*Valencia2} in the context of top-quark
@@
 %
-At the LHC the $t\bar{t}H$ production proceeds via $q\bar{q}$
-annihilation and $gg$ fusion processes. The relevant Feynman diagrams
-at leading order are displayed in Fig.~\ref{fig1}, where the two first
-rows correspond respectively to $q\bar{q}$ and $gg$ s-channels whereas
-the last one depicts the $gg$ t-channels. By exchanging the gluon
-lines in this row, three more $gg$-initiated diagrams can be
-obtained. We describe the $tH$ cupling with the effective lagrangian
+At the LHC $t\bar{t}H$ production proceeds via $q\bar{q}$
+annihilation and $gg$ fusion processes. The relevant leading-order Feynman
+diagrams are displayed in Fig.~\ref{fig1}, with the first two
+rows containing the $q\bar{q}$ and $gg$ $s$-channel diagrams, and
+the last one depicting the $gg$ $t$-channel diagrams. By exchanging the gluon
+lines in the third row, three more $gg$-initiated diagrams can be
+obtained. We describe the $tH$ coupling with the effective Lagrangian
 %
@@
 where $v=246~\mathrm{GeV}$ is the SM Higgs vacuum
-expectation value, and the coefficients $\kp$ and $\kpt$ determine the
-weigth of the scalar and pseudoscalar interaction, respectively. The
+expectation value, and the coefficients $\kp$ and $\kpt$ parameterize 
+the scalar and pseudoscalar interaction, respectively. The
 SM case is obtained for $\kp=1$ and $\kpt=0$, while the values $\kp=0$
-and $\kpt\neq 0$ parameterizes a $\mathrm{CP}$-odd Higgs. \par
+and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs. \par
 %%%%%%%%%%%%%%%%%%%% Figura 1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \vspace*{0.02\textwidth}
-\caption{Tree level Feynman diagrams contributing to $t\tbar H$ production at the LHC. Three more diagrams are obtained by exchanging the gluon lines in the t-channel diagrams.}
+\caption{Tree-level Feynman diagrams contributing to $t\tbar H$ production
+  at the LHC. Three more diagrams are obtained by exchanging the gluon
+  lines in the $t$-channel diagrams.}
 \label{fig1}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Since the total cross-section is dominated by the $gg$ contribution,
-let us focus on the $gg$-initiated production followed by the leptonic
-SM decay of both $t$ and $\tbar$. By using the narrow-width
+In this section we focus on the gluon fusion contributions
+to $t\tbar H$ production, since these dominate over the
+the quark-antiquark annihilation contributions.  Furthermore,
+we consider the case in which the top and antitop both decay
+semileptonically.  By using the narrow-width
 approximation for the top quark, it can be shown that the unpolarized
@@
 where $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$ is the differential
-cross section of the production of a top quark with spin vector $n_t$
+cross section for the production of a top quark with spin vector $n_t$
 plus an anti-top quark with spin vector $n_{\bar{t}}$ and a Higgs
-boson, whereas $d\Gamma(t(n_t)\to b{\ell}^+\nu_{\ell})$ and
+boson, and $d\Gamma(t(n_t)\to b{\ell}^+\nu_{\ell})$ and
 $d\Gamma(\tbar (n_{\tbar})\to \bbar {\ell}^-\nubar)$ are the

### 2016-02-22 Paper_ttbarH_Draft.tex
Changes in the bibliography, abstract and introduction

@@
 promising observable can disentangle the hypotheses $\kp=1,\kpt=\pm 1$
-by more than $\sim 20\sigma$.  In
+by more than the $\sim 20\sigma$ statistical level.  In
 the case of observables that do not need the reconstruction of the $t$
-and $\tbar$ momenta, the power of discrimination is up to $\sim
-16\sigma$ for the same number of events. We also show that the
+and $\tbar$ momenta, the power of discrimination is up to the $\sim
+16\sigma$ statistical level for the same number of events. We also show that the
 capability of the most promising observables for separating the
 $\mathrm{CP}$-mixed hypotheses preveals even when a number of events
-plausible within the short term LHC is considered. {\bf (KK: reword last sentence a bit.)}
+plausible within the short term LHC is considered.
 
@@
 predicted by the Standard Model (SM) of particle physics.
-It is of particular importance to test the coupling of the putative ({\bf (KK: at some point
-  should we just start calling this the Higgs?  How do we make that transition?)}
+It is of particular importance to test the coupling of the putative 
 Higgs boson to
@@
 leading dependence on the cut-off energy scale in the corrections to
-the Higgs mass -- and it may play an important role in the EWSB {\bf KK: define EWSB?}
-mechanism.  {\bf (KK: I reworded a lot of this paragraph -- is it still
-  correct, or did I accidentally alter the meaning?)}\par
+the Higgs mass -- and it may play an important role in the mechanism for electroweak symmetry breaking.\par
 
@@
 \cite{constraints1,constraints2, constraints3,constraints4}.
-     {\bf (KK: OK to drop ``gluon fusion'' here, since we already said it was
-       the main production process above?  Alternatively, we could say it here
-       and skip it above.)}
      However,
@@
 coupling of the Higgs boson to the $W$ is standard. In this sense, the
-constraints derived from measurements of Higgs boson decay rates
-{\bf (KK: correct to add ``boson decay'' here?)} are indirect
-constraints. Electric dipole moments (EDMs) {\bf (KK: delete ``EDM'' since we
-  never use it again?)} can also
+constraints derived from measurements of Higgs boson production and decay rates
+ are indirect constraints. Electric dipole moments can also
 impose stringent indirect constraints on $\kpt$ by assuming that there
 are no new physics (NP) particles contributing to the loops of the
-relevant diagrams and that the electron-Higgs coupling is that
+relevant diagrams and in the case of the EDM of the electron that the 
+electron-Higgs coupling is that
 predicted by the SM \cite{constraints1,edm}. In order to probe
@@
 for associated Higgs production with a single top (antitop)
-{\bf (KK: did I phrase this correctly, calling it ``associated production'' in this way?)}
 is smaller than that for production with a $t\tbar$ pair, and involves
@@
 Ref.~\cite{tHmaltoni}).  Associated Higgs production with a
-$t\tbar$ pair has been studied by several authors {\bf (KK: true?)}, and
+$t\tbar$ pair has been studied by several authors, and
 various observables sensitive to the couplings $\kp$ and $\kpt$ have
@@
 distribution and the azimuthal angular separation between the $t$ and $\tbar$,
-to name a few \citep{Guadagnoli}. Also, an approach based on weighted
+to name a few \cite{Guadagnoli,*Boosted,*Li,*Golden,*Khatibi}. Also, an approach based on weighted
 moments and optimal observables has been developed in Ref.~\cite
@@
 within the context of an $e^+ e^-$ as well as a $pp$ collider.
-{\bf (KK: is this last one CP even, too?)}  Now, $\mathrm{CP}$-even observables are not
+ Now, $\mathrm{CP}$-even observables are not
 sensitive to the relative sign between the scalar and pseudoscalar
@@
 products in such a way that these particles work as spin analyzers.
-As is well known {\bf (ref)}, in the case of semileptonic top decay,
+As is well known, in the case of semileptonic top decay,
 the charged lepton is the most powerful in this regard.
 It is also known that the top quark and antiquark spins
-are highly correlated in $t\tbar$ production\cite{Mahlon1,*Mahlon2,*Mahlon3,*atwood},
+are highly correlated in $t\tbar$ production,
 a feature that
 is manifested in the double angular distributions of the decay
-products of the $t$ and $\tbar$ systems {\bf (ref)}.
+products of the $t$ and $\tbar$ systems \cite{Mahlon1,*Mahlon2,*Mahlon3,*atwood}.
 %The spin correlations
@@
 are also sensitive to the manner in which
-the top couples to the Higgs boson. {\bf (KK: Did I simplify this too much?
-  It seemed to repeat the previous idea a bit, but maybe I was misunderstanding it.)}
+the top couples to the Higgs boson. 
 In fact, observables that exploit
@@
 from the dominant irreducible background $t\tbar b\bbar$, which does not
-involve the Higgs boson. {\bf (KK: did I preserve the physics meaning
-  correctly when I reworded this?)}
+involve the Higgs boson.
 
@@
 triple product (TP) structures that we extract naturally from the
-expression for the differential cross section for {\bf (name of process)},
+expression for the differential cross section for $\ppprocess$,
 making use of the fact that the $t$ and $\tbar$ decay products
@@
 and antitop spin vectors to final state particle
-momenta and separate the production process from the decay which
+momenta and separate the production process from the decay. This
 allows to identify straightforwardly the contributions linearly
-sensitive to the couplings. {\bf (KK: can we simplify the previous
-  sentence?)}  Further, the TPs correlations in these
+sensitive to the couplings.
+ Further, the TPs correlations in these
 contributions incorporate the $t$ and $\tbar$ spin vectors. Starting

### 2016-02-23 Paper_ttbarH_Draft.tex
a few changes made by KK to Sec. II

--- 2016-02-15 Paper_ttbarH_Draft.tex
@@
 annihilation and $gg$ fusion processes. The relevant leading-order Feynman
-diagrams are displayed in Fig.~\ref{fig1}, with the first two
-rows containing the $q\bar{q}$ and $gg$ $s$-channel diagrams, and
-the last one depicting the $gg$ $t$-channel diagrams. By exchanging the gluon
+diagrams are displayed in Fig.~\ref{fig1}, where the first two
+rows show the $q\bar{q}$ and $gg$ $s$-channel diagrams, and
+the last one depicts the $gg$ $t$-channel diagrams. By exchanging the gluon
 lines in the third row, three more $gg$-initiated diagrams can be
@@
 %dd\sigma(gg\to (bl^+\nu_l)(\bbar l^- \nubar) H)=\sum_{\substack{bl^+\nu_l \\ \tiny{\mathrm{spins}}}}\,\sum_{\substack{\bbar l^-\nubar \\ \mathrm{\tiny{spins}}}}\left(\frac{2}{\Gamma_t}\right)^2\,d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)\,d\Gamma(t(n_t)\to bl^+\nu_l)\,d\Gamma(\tbar (n_{\tbar})\to \bbar l^-\nubar)
-d\sigma =\sum_{\substack{b{\ell}^+\nu_l \\ \tiny{\mathrm{spins}}}}\,\sum_{\substack{\bbar {\ell}^-\nubar \\ \mathrm{\tiny{spins}}}}\left(\frac{2}{\Gamma_t}\right)^2\,d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)\,d\Gamma(t(n_t)\to b{\ell}^+\nu_{\ell})\,d\Gamma(\tbar (n_{\tbar})\to \bbar {\ell}^-\nubar),
+d\sigma =\sum_{\substack{b{\ell}^+\nu_l \\ \tiny{\mathrm{spins}}}}\,
+   \sum_{\substack{\bbar {\ell}^-\nubar \\ \mathrm{\tiny{spins}}}}\left(\frac{2}{\Gamma_t}\right)^2\,
+   d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)\,
+   d\Gamma(t\to b{\ell}^+\nu_{\ell})\,
+   d\Gamma(\tbar \to \bbar {\ell}^-\nubar),
 \eeq  
@@
 plus an anti-top quark with spin vector $n_{\bar{t}}$ and a Higgs
-boson, and $d\Gamma(t(n_t)\to b{\ell}^+\nu_{\ell})$ and
-$d\Gamma(\tbar (n_{\tbar})\to \bbar {\ell}^-\nubar)$ are the
-differential decay widths of a top with spin vector $n_t$ and an
-anti-top with spin vector $n_{\tbar}$, respectively. Also, the vectors
+boson, and $d\Gamma(t\to b{\ell}^+\nu_{\ell})$ and
+$d\Gamma(\tbar \to \bbar {\ell}^-\nubar)$ are the
+differential decay widths for an unpolarized top and
+anti-top, respectively. Also, the vectors
 $n_t$ and $n_{\tbar}$ are given by particular combinations of the
@@
 production of short-lived particles in $e^-e^+$ colliders
-\cite{kawasaki} and in particular for $t\tbar$ production both in
+\cite{kawasaki} and for $t\tbar$ production both in
 $e^-e^+$ colliders \cite{Arens} and $pp$ colliders
-\cite{ale1,*ale2,*ale3,*ale4}. \par We will outline now how to derive
+\cite{ale1,*ale2,*ale3,*ale4}. \par
+
+We will outline now how to derive
 Eq.~(\ref{eq2}) and to obtain the above definitions for the spin

### 2016-02-25 Paper_ttbarH_Draft.tex
substantial changes by KK to Sec. II; up to about Eq. (18)

@@
 %\section{Process \MakeLowercase{{\boldmath $pp\to t \bar{t}$}}$H\to$\MakeLowercase{{\boldmath $\left(b l^+ \nu_l \right) \left(\bar{b} l^-\bar{\nu}_l\right)$}}$H$. Theoretical framework}
-\section{Process \MakeLowercase{{\boldmath $pp\to t(\to b {\ell}^+ \nu_{\ell})\,\bar{t}(\to\bar{b} {\ell}^-\bar{\nu}_{\ell})$}}$\,H$. Theoretical framework}
+\section{Theoretical framework for \MakeLowercase{{\boldmath $pp\to t(\to b {\ell}^+ \nu_{\ell})\,\bar{t}(\to\bar{b} {\ell}^-\bar{\nu}_{\ell})$}}$\,H$}
 \label{sec2}
@@
 %
+Before turning to a discussion of $\mathrm{CP}$-odd observables,
+it is useful to consider a few theoretical aspects of
+the process $\ppprocess$.  In this section we derive a ``factorized''
+expression for the gluon fusion contribution to this process.
+We then use this expression to isolate various mathematical quantities
+that will be useful as we construct $\mathrm{CP}$-odd observables.
+
+\subsection{Factorized expression for the scattering cross section}
+
 At the LHC $t\bar{t}H$ production proceeds via $q\bar{q}$
@@
 rows show the $q\bar{q}$ and $gg$ $s$-channel diagrams, and
-the last one depicts the $gg$ $t$-channel diagrams. By exchanging the gluon
-lines in the third row, three more $gg$-initiated diagrams can be
-obtained. We describe the $tH$ coupling with the effective Lagrangian
+the last one depicts the $gg$ $t$-channel diagrams.  Three more
+$gg$-initiated diagrams are obtained by exchanging the gluon
+lines in the third row.
+We describe the $tH$ coupling with the effective Lagrangian
 %
@@
 SM case is obtained for $\kp=1$ and $\kpt=0$, while the values $\kp=0$
-and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs. \par
+and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs
+{\bf KK: ``boson''? I don't think PRD allows us to just say ``Higgs''}. \par
 %%%%%%%%%%%%%%%%%%%% Figura 1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 we consider the case in which the top and antitop both decay
-semileptonically.  By using the narrow-width
-approximation for the top quark, it can be shown that the unpolarized
-differential cross section for the full process $gg\to t(\to
-b{\ell}^+\nu_{\ell})\,\tbar(\to \bbar {\ell}^- \nubar)\,H$ takes the
-following form (we sketch the proof below)
+semileptonically.  As we shall show below, assuming the
+narrow width approximation for the top and antitop quarks, the unpolarized
+differential cross section for $gg\to t(\to
+b{\ell}^+\nu_{\ell})\,\tbar(\to \bbar {\ell}^- \nubar)\,H$ may be
+written in the following ``factorized'' form,\footnote{The reader
+  is referred to the discussion following Eq.~(\ref{eq17}) for some qualifying
+  remarks regarding the ``factorization'' of this expression.}
 %
@@
 where $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$ is the differential
-cross section for the production of a top quark with spin vector $n_t$
-plus an anti-top quark with spin vector $n_{\bar{t}}$ and a Higgs
-boson, and $d\Gamma(t\to b{\ell}^+\nu_{\ell})$ and
+cross section for the production of a top and antitop quark,
+with spin vectors $n_t$ and $n_{\bar{t}}$, respectively, along with a Higgs
+boson.  Also, $d\Gamma(t\to b{\ell}^+\nu_{\ell})$ and
 $d\Gamma(\tbar \to \bbar {\ell}^-\nubar)$ are the
-differential decay widths for an unpolarized top and
-anti-top, respectively. Also, the vectors
-$n_t$ and $n_{\tbar}$ are given by particular combinations of the
-momenta $t,\ell^+$ and $\tbar,\ell^-$ respectively \cite{Arens},
+partial differential decay widths for an unpolarized top and
+anti-top quark.  The four-vectors
+$n_t$ and $n_{\tbar}$ are not arbitrary, but are
+given by particular combinations of the
+momenta of the $t,\tbar, \ell^+$ and $\ell^-$~\cite{Arens},
 %
@@
 %
-Expressions similar to Eq.~(\ref{eq2}) have been derived for the
+Expressions similar to Eq.~(\ref{eq2}) have been derived previously for the
 production of short-lived particles in $e^-e^+$ colliders
@@
 
-We will outline now how to derive
-Eq.~(\ref{eq2}) and to obtain the above definitions for the spin
-vectors. The process $g_ag_b\to t(\to
-b_i{\ell}^+\nu_{\ell})\,\tbar(\to \bbar_j {\ell}^- \nubar)\,H$ can be
-drawn as in Fig.~\ref{fig2}, where $a$ and $b$ denote the gluons and
-$i$ and $j$ are the top and anti-top colours.
 %%%%%%%%%%%%%%%%% FIGURA 2 %%%%%%%%%%%%%%%%%%%%%%
 \begin{center}
-\begin{figure}[H]
+\begin{figure}[th]
 \centering
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\par
-%
-The diagrams displayed in Fig.~\ref{fig1} (second and third rows)
-contribute to the quantity $A^{ab,ij}$, so that
+
+To derive the above expressions, we begin by considering the
+schematic representation for the process $g_ag_b\to t(\to
+b_i{\ell}^+\nu_{\ell})\,\tbar(\to \bbar_j {\ell}^- \nubar)\,H$
+that is sketched in Fig.~\ref{fig2}.
+Here $a$ and $b$ denote the initial-state gluons and
+$i$ and $j$ refer to the colours of the top and antitop quarks.
+%\par
+%
+The amplitude for this process may be written in the following
+compact form
+%
+\beq
+\label{eq6}
+\mathcal{M}^{ab,ij}=\bar{\psi}_t\,\mathcal{A}^{ab,ij}\,\psi_{\tbar}\,,
+\eeq
+%
+where the spinors $\bar{\psi}_t$ and $\psi_{\tbar}$
+contain all of the information regarding the decay of the
+virtual top and anti-top, respectively,
+and where the quantity $A^{ab,ij}$ is given by
 %
@@
 \label{eq5}
-\mathcal{A}^{ab,ij}\equiv A^{ab,ij}_{\mu\nu}(\epsilon_{\lambda_a})^{\mu}(\epsilon_{\lambda_b})^{\nu}=\sum_{k=1}^8 \mathcal{A}^{ab,ij}_k =\kp \sum_{k=1}^8 \mathcal{S}^{ab,ij}_k + i\kpt \sum_{k=1}^8 \mathcal{P}^{ab,ij}_k,
-\eeq 
-%
-where $\epsilon_{\lambda_a}$ and $\epsilon_{\lambda_b}$ are the
-polarization vectors of $g_a$ and $g_b$ respectively and in the last
-equality the scalar piece of each diagram has been separated from the
-pseudoscalar one. The quantity $\mathcal{A}^{ab,ij}$ can be linked to
-the final states particles by using two spinors, $\psi_{t}$ and
-$\psi_{\tbar}$, that will contain the information on the decay of the
-virtual top and anti-top, respectively. Hence, the amplitude for the
-complete process depicted in Fig.~\ref{fig2} can be witten as
-%
-\beq
-\label{eq6}
-\mathcal{M}^{ab,ij}=\bar{\psi}_t\,\mathcal{A}^{ab,ij}\,\psi_{\tbar}\,.
-\eeq
-%
-If we assume $b,l$ and $\nu_l$ to be massless, we can make use of the
-spinor techniques\footnote{These spinors techniques can also be used
-  for massive particles. However, the derivation of Eq.~(\ref{eq2}) is
-  much simpler by assuming the final state particles to be massless
-  which is a sensible approximation in view of the energy involved in
-  the process.} developed in \cite{Kleiss} to write $\bar{\psi}_t$ and
-$\psi_{\tbar}$ as follows
+\mathcal{A}^{ab,ij}\equiv A^{ab,ij}_{\mu\nu}(\epsilon_{\lambda_a})^{\mu}(\epsilon_{\lambda_b})^{\nu}=\sum_{k=1}^8 \mathcal{A}^{ab,ij}_k =\kp \sum_{k=1}^8 \mathcal{S}^{ab,ij}_k + i\kpt \sum_{k=1}^8 \mathcal{P}^{ab,ij}_k.
+\eeq 
+%
+The sum over $k$ in the above expression
+corresponds to the eight gluon-initiated
+diagrams indicated in Fig.~\ref{fig1} {\bf (KK: correct?)}; also,
+$\epsilon_{\lambda_a}$ and $\epsilon_{\lambda_b}$ are the
+polarization vectors corresponding to $g_a$ and $g_b$, respectively.
+In the last equality in Eq.~(\ref{eq5})
+we have explicitly separated the amplitude into
+two sums, with one sum corresponding to the scalar contributions
+and the other to the pseudoscalar ones.
+Taking all of the final-state particles to be massless, we can use the
+spinor techniques
+developed in \cite{Kleiss} to write $\bar{\psi}_t$ and
+$\psi_{\tbar}$ as follows\footnote{These spinor techniques can also be used
+  for massive final-state particles. Given the
+  energy scale involved in the process in question, however, the assumption
+  of massless final-state particles is sensible and greatly
+  simplifies the derivation of Eq.~(\ref{eq2}).}
 %
@@
 \label{eq7}
-\bar{\psi}_t &=& -g^2\,\frac{1}{(t^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{((t-b)^2-M^2_W+im_W\Gamma_W)}\,\langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\
+\bar{\psi}_t &=& -g^2\, \mathbb{P}_t(t)\,\mathbb{P}_W(t-b)\,
+   \langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\
 \label{eq8}
-\psi_{\tbar} &=& -g^2\,\frac{1}{(\tbar^2-m^2_t+im_t\Gamma_t)}\frac{1}{((\tbar-\bbar)^2-M^2_W+im_W\Gamma_W)}\,\langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
+\psi_{\tbar} &=& -g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
+   \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
 \eea
 %
-where $|i+(-)\rangle \equiv P_{R(L)}\,\psi_i$ ($P_{R,L}=(1\pm
-\gamma^5)/2$) represents a right-handed(left-handed) chiral spinor for
-particle $i$, $\langle i+(-)|$ is the corresponding adjoint spinor and
-we have denoted the momenta through the symbols that represents the
-name of the particles \cite{Mangano}. The relevant quantity is
-$|\mathcal{M}^{ab,ij}|^2$, which from Eqs.~(\ref{eq6})-(\ref{eq8}) is
-proportional to $((t^2-m^2_t)^2+m^2_t\Gamma^2_t)^{-1}$ and
-$((\tbar^2-m^2_t)^2+m^2_t\Gamma^2_t)^{-1}$. Under the narrow-width
-approximation we can replace these factors by
-$(\pi/m_t\Gamma_t)\delta(t^2-m^2_t)$ and
-$(\pi/m_t\Gamma_t)\delta(\tbar^2-m^2_t)$ respectively. Hence, we can
-take directly $t^2=\tbar^2=m^2_t$ in the amplitude and write
+where $|i+(-)\rangle \equiv (1/2)(1\pm \gamma^5)\,\psi_i$
+represents a right-handed (left-handed) chiral spinor for final-state
+particle $i$ and $\langle i+(-)|$ represents the corresponding adjoint spinor.
+{\bf (KK: Do we mean the adjoint spinor, related by $C \psi^T$,
+  or whatever?)}
+Also, $\mathbb{P}_t(q)=(q^2-m^2_t+im_t\Gamma_t)^{-1}$ and
+$\mathbb{P}_W(q)=(q^2-M^2_W+im_W\Gamma_W)^{-1}$, and
+we have denoted the momenta of the various particles by the symbols
+that refer to the names of those particles~\cite{Mangano}.
+
+Using the expressions defined above for $\bar{\psi}_t$ and
+$\psi_{\tbar}$, we can write the amplitude $\mathcal{M}^{ab,ij}$
+in a form that is (in a sense) factorized.
+As a first step, we insert
+Eqs.~(\ref{eq7}) and (\ref{eq8}) into Eq.~(\ref{eq6}), yielding
 %
@@
 \label{eq9}
-\mathcal{M}^{ab,ij}=\!-g^4\,\mathbb{P}_t(t)\,\mathbb{P}_{\tbar}(\tbar)\,\mathbb{P}_W(t-b)\,\mathbb{P}_W(\tbar-\bbar)\,\langle b-|\nu_{\ell}+\rangle \langle\nubar+|\bbar-\rangle \sqrt{\strut2(t\cdot {\ell}^+)}\sqrt{\strut2(\tbar\cdot {\ell}^-)}\,[\bar{\phi}_t \mathcal{A}^{ab,ij}\phi_{\tbar}],
+\mathcal{M}^{ab,ij}=\!-g^4\,\mathbb{P}_t(t)\,\mathbb{P}_t(\tbar)\,\mathbb{P}_W(t-b)\,\mathbb{P}_W(\tbar-\bbar)\,\langle b-|\nu_{\ell}+\rangle \langle\nubar+|\bbar-\rangle \sqrt{\strut2(t\cdot {\ell}^+)}\sqrt{\strut2(\tbar\cdot {\ell}^-)}\,[\bar{\phi}_t \mathcal{A}^{ab,ij}\phi_{\tbar}],
 %\frac{1}{(t^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{(\tbar^2-m^2_t+im_t\Gamma_t)}\,\frac{1}{((t-b)^2-M^2_W)}\frac{1}{((\tbar-\bbar)^2-M^2_W)}\,\langle b-|\nu+\rangle\,\langle\nubar+|\bbar-\rangle
@@
 %
-where we have used the notation
-$\mathbb{P}_t(t)=(t^2-m^2_t+im_t\Gamma_t)^{-1}$,
-$\mathbb{P}_{\tbar}(\tbar)=(\tbar^2-m^2_t+im_t\Gamma_t)^{-1}$,
-$\mathbb{P}_W(t-b)=((t-b)^2-M^2_W+im_W\Gamma_W)^{-1}$ and
-$\mathbb{P}_W(\tbar-\bbar)=((\tbar-\bbar)^2-M^2_W+im_W\Gamma_W)^{-1}$. The
-spinors $\phi_{t}$ and $\phi_{\tbar}$ are defined as follows
+where the spinors $\phi_{t}$ and $\phi_{\tbar}$ are defined as
 %
@@
 \label{eq11}
-\phi_{\tbar}=\frac{(\tbslash -m_t)}{\sqrt{\strut2(\tbar\cdot {\ell}^-)}}|{\ell}^-+\rangle
-\eeq
-%
-and describe a top quark with spin vector $n_t$ and an anti-top quark
-with spin vector $n_{\tbar}$, since the corresponding projection
-operators are given by
+\phi_{\tbar}=\frac{(\tbslash -m_t)}{\sqrt{\strut2(\tbar\cdot {\ell}^-)}}|{\ell}^-+\rangle \,.
+\eeq
+%
+Note that in writing down the above expressions we have adopted the narrow-width
+approximation for the top and antitop quarks and for the $W^\pm$ gauge
+bosons.\footnote{Since Eq.~(\ref{eq9}) contains the top quark propagator
+  term
+  $\mathbb{P}_t(t)$, for example, $|\mathcal{M}^{ab,ij}|^2$ contains
+  the factor $((t^2-m^2_t)^2+m^2_t\Gamma^2_t)^{-1}$,
+  which is replaced by $(\pi/m_t\Gamma_t)\delta(t^2-m^2_t)$
+  in the narrow-width approximation.  Thus we take the four-vector
+  $t$ appearing in the definition of $\phi_t$ to be
+  on shell, satisfying $t^2 = m_t^2$.} {\bf (KK: Do I understand correctly
+  that $t$ is an on-shell four-vector in $t\cdot \ell^+$, but not
+  in $\mathbb{P}_t(t)$?  This is similar to saying $f(x)\delta(x-x_0) =
+  f(x_0)\delta(x-x_0)$\ldots?)}
+Working out the projection operators $\phi_t\,\bar{\phi}_t$
+and $\phi_{\tbar}\,\bar{\phi}_{\tbar}$, we have
 %
@@
 %
+and
+%
 \beq
@@
 %
-with $n_t$ and $n_{\tbar}$ being the vectors defined in
-Eq.~(\ref{eq3})-(\ref{eq4}). Moreover, if we use these spinors to
-compute the amplitude for a top(anti-) with spin vector
-$n_t$($n_{\tbar}$) to decay into
-$b{\ell}^+\nu_{\ell}$($\bar{b}{\ell}^-\bar{\nu}_{\ell}$) we obtain
+with $n_t$ and $n_{\tbar}$ being the four-vectors defined in
+Eqs.~(\ref{eq3}) and (\ref{eq4}).  Thus, $\phi_t$ and $\phi_{\tbar}$
+may be regarded as
+describing a top quark with spin vector $n_t$ and an antitop quark
+with spin vector $n_{\tbar}$, respectively.
+
+As a final step toward factorizing the amplitude $\mathcal{M}^{ab,ij}$,
+we note that the amplitude for a top quark with spin vector
+$n_t$ to decay into $b{\ell}^+\nu_{\ell}$ is given by
 %
@@
 \label{eq14}
-\mathcal{M}(t(n_t)\to b{\ell}^+\nu_{\ell})=ig^2\mathbb{P}_W(t-b)\langle b-|\nu_{\ell}+\rangle\sqrt{\strut2(t\cdot {\ell}^+)}
-\eeq
+\mathcal{M}(t(n_t)\to b{\ell}^+\nu_{\ell})=ig^2\mathbb{P}_W(t-b)\langle b-|\nu_{\ell}+\rangle\sqrt{\strut2(t\cdot {\ell}^+)} \,,
+\eeq
+%
+and likewise,
 %
@@
 %
-On the other hand, the term inside the square brackets in
-Eq.~(\ref{eq9}) is nothing but the amplitude for producing a top quark
+Furthermore, the term inside the square brackets in
+Eq.~(\ref{eq9}) is the amplitude for producing a top quark
 with spin vector $n_t$, along with an anti-top with spin vector
-$n_{\tbar}$ and a Higgs boson, i.e.
+$n_{\tbar}$ and a Higgs boson,
 %
@@
 %
-By combining Eqs.~(\ref{eq14})-(\ref{eq16}), we can write Eq.~(\ref{eq9}) as follows
+Combining Eqs.~(\ref{eq14})-(\ref{eq16}), we can write Eq.~(\ref{eq9})
+in a form that appears to be factorized,
 %
@@
 \label{eq17}
-\mathcal{M}^{ab,ij}=\mathbb{P}_t(t)\mathbb{P}_{\tbar}(\tbar)\,\mathcal{M}(t(n_t)\to b{\ell}^+\nu_{\ell})\,\mathcal{M}(\tbar(n_{\tbar})\to \bar{b}{\ell}^-\bar{\nu}_{\ell})\,\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H).
-\eeq
-%
-From Eq.~(\ref{eq17}), Eq.~(\ref{eq2}) can be derived. It's important
-to note that, even though Eqs.~(\ref{eq2}) and (\ref{eq9}) appear to
-be factorized into production and decay parts, these are not
-independent, since both parts share kinematical variables due to the
-presence of the spin vectors $n_t$ and $n_{\tbar}$ (see
-Eqs.~(\ref{eq14})-(\ref{eq16}) along with the definitions given in
-Eqs.~(\ref{eq3}) and (\ref{eq4})).\par
+\mathcal{M}^{ab,ij}=\mathbb{P}_t(t)\mathbb{P}_t(\tbar)\,\mathcal{M}(t(n_t)\to b{\ell}^+\nu_{\ell})\,\mathcal{M}(\tbar(n_{\tbar})\to \bar{b}{\ell}^-\bar{\nu}_{\ell})\,\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H) \,.
+\eeq
+%
+It is important
+to note that, even though the above expression has the appearance of being
+factorized into production and decay parts, this apparent
+factorization is a bit misleading.  In particular, the amplitude for
+$t\tbar H$ production contains the top and antitop quark
+spin four-vectors $n_t$ and $n_{\tbar}$, which
+depend on final-state kinematical quantities [see
+Eqs.~(\ref{eq3}) and (\ref{eq4})].
+With this qualification in mind, we may now use the
+amplitude in Eq.~(\ref{eq17})
+to determine the corresponding scattering cross section.
+After some manipulation of the phase space variables
+to take advantage of the presence of the
+propagator terms, $\mathbb{P}_t(t)$ and $\mathbb{P}_t(\tbar)$,
+we arrive at the expression in Eq.~(\ref{eq2}).  This expression
+also has the appearance of being factorized, but
+qualifying remarks, similar to those above, apply.
+{\bf (KK: I'm still a bit confused as to why $n_t$ appears
+  in the amplitude expression for the decay, but not
+  in the expression for the cross section.  That is, the top
+  spins are summed over in the width that appears in the
+  factorized expression for the cross section.  That part makes
+  sense to me, but I'm not so clear on how to get there from
+  Eq.~(17).  Probably need to look more closely at the notes!)}
+
 %%%%%%%%%%%%%%%%%%% Quitarlo %%%%%%%%%%%%%%%%%%%%

### 2016-02-27 Paper_ttbarH_Draft.tex
KK edits up to the end of Sec. II; diff.pdf file updated as well

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Let us focus now in the production amplitude in Eq.~(\ref{eq17})
-needed for computing the production part of the unpolarized
-differential cross-section. By summing over colour and gluon indices
+
+\subsection{Triple products}
+{\bf (KK: maybe we should change this title for the subsection\ldots.)}
+
+The expression derived above for the scattering cross
+section [see Eq.~(\ref{eq2}), as well as Eq.~(\ref{eq17})]
+provides significant insight into
+how one might analyze $\ppprocess$ in order to determine
+the nature of the top-Higgs coupling.  In particular,
+let us focus on the production amplitude,
+$\mathcal{M}(g_ag_b \to t^i(n_t)\tbar^j(n_{\tbar})H))$, which forms
+part of the overall amplitude in Eq.~(\ref{eq17}).
+The absolute value squared of the production amplitude
+is used to determine $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$,
+which in turn forms part of the expression for the ``factorized'' cross section
+in Eq.~(\ref{eq2}).  Summing over colour and gluon indices
 we have
@@
 %
-where we have separated the colour structure of each diagram by using
-the definitions $\mathcal{S}^{ab,ij}= C^{ab,ij}_k \mathcal{S}$ and
-$\mathcal{P}^{ab,ij}= C^{ab,ij}_k \mathcal{P}$. Also, the factors
-$g^2_s m_t/v$ and $-ig^2_s m_t/v$ arising from the vertices of the t-
-and s-channel diagrams respectively have been included in the
+where we have separated the colour structure of each diagram by defining
+{\bf (KK: do these need $k$ subscripts?)}
+$\mathcal{S}^{ab,ij}= C^{ab,ij}_k \mathcal{S}$ and
+$\mathcal{P}^{ab,ij}= C^{ab,ij}_k \mathcal{P}$
+[see Eqs.~(\ref{eq5}) and (\ref{eq16})]. Also, the factors
+$g^2_s m_t/v$ and $-ig^2_s m_t/v$ arising from the vertices of the $t$-
+and $s$-channel diagrams respectively have been included in the
 definition of $C^{ab,ij}_k$ for convenience. The terms linear in $\kp$
@@
 where the factor $\mathbb{C}_{kr}=\sum_{ab,ij}C^{ab,ij}_k
-C^{ab,ij*}_r$ is real and $\tilde{\mathcal{P}}_r = \gamma^0
-\mathcal{P}_r \gamma^0$. The only contributing terms are those with an
-odd number of $\gamma^5$ matrices and will lead to triple-products
-(TP) structures, i.e. contractions between the levi-civita tensor
-$\epsilon_{\alpha\beta\gamma\delta}$ with four momenta. In contrast,
+C^{ab,ij*}_r$ is real and where $\tilde{\mathcal{P}}_r = \gamma^0
+\mathcal{P}_r \gamma^0$ {\bf (KK: wouldn't this be
+  $\mathcal{P}_r^\dagger$? I didn't look for this in the notes
+  yet, so maybe I'm just missing something)}.
+The only terms that yield non-zero contributions
+in the above sum are those with an
+odd number of $\gamma^5$ matrices; these lead to triple-product
+(TP) structures
+of the form $\epsilon_{\alpha\beta\gamma\delta}\,p^{\alpha}_ap^{\beta}_bp^{\gamma}_cp^{\delta}_d$,
+where $p_a$-$p_d$ represent various four momenta associated with the process.
+In contrast,
 it can be seen from Eq.~(\ref{eq18}) that the terms proportional to
-$\kp^2$ and $\tilde{\kappa}^2_t$ contain an even number of $\gamma^5$
+$\kp^2$ and $\tilde{\kappa}^2_t$ descend from traces containing
+an even number of $\gamma^5$
 matrices and can be written in terms of scalar products of the
@@
 
-In order to state this more clearly, we will consider the form of the
-differential cross-section in terms of the momenta $q=(q_1-q_2)/2$,
+With the above considerations in mind, it is useful to
+write a general expression for the differential cross
+section $d\sigma(gg\to t(n_t)\tbar (n_{\tbar})H)$
+in terms of the momenta $q=(q_1-q_2)/2$,
 $Q=(q_1+q_2)/2$, $t$, $\bar{t}$, $n_t$ and $n_{\tbar}$, where
-$q_{1,2}$ denote the momenta of the gluons. Note that with this
+$q_{1,2}$ denote the momenta of the initial-state gluons. Note that with this
 choice, $q\cdot Q=0$ and $Q^2=-q^2=M^2_{t\tbar H}/4$, where $M_{t\tbar
-  H}$ is the invariant mass of the system $t\tbar H$. From these six
-vectors, fifteen TPs can be built\footnote{ We note that these fifteen
+  H}$ is the invariant mass of the $t\tbar H$ system.
+Fifteen TPs can be constructed from these six
+four-vectors,\footnote{We note that these fifteen
   TPs are not linearly independent (see the epsilon relations
-  discussed in \cite{identities}).}, and the general form of the
-production differential cross-section will be given by
+  discussed in Ref.~\cite{identities}).} so that
 %
@@
 $\epsilon_l=\epsilon_{\alpha\beta\gamma\delta}\,p^{\alpha}_ap^{\beta}_bp^{\gamma}_cp^{\delta}_d$
-denotes the $l$th TP, the Roman indices refer to any of the involved
-momenta and we adopt the convention $\epsilon_{0123}=+1$. The
+denotes the $l$th TP (we adopt the convention $\epsilon_{0123}=+1$) and where $p_i$ and $p_j$ refer to any of the
+six momenta.  The
 functions $f_{1,2}$ and $g_k$ depend only on the possible scalar
@@
 TPs. Hence, only the functions $f_{1,2}$ will contribute to the total
-cross-section, whereas the TPs terms will be sensitive to the sign of
-the anomalous coupling $\kpt$. From the fifteen TPs mentioned above,
-we will focus on those that do not include $q$ and contain both spin
-vectors $n_t$ and $n_{\tbar}$. The former is motivated in the fact
-that $q$ cannot be eliminated in terms of the momenta of final state
-particles (like $Q$ in virtue of momentum-energy conservation). The
-latter takes into account that for $t\tbar$ production at hadron
-colliders the top and antitop are not polarized but their spins are
-strongly correlated and observables combining the decay products of
-$t$ and $\tbar$ will be sensitive to this spin correlation
-\cite{Bernreuther}.  A similar behaviour is expected in $t\tbar H$
-production where it can be shown that the single-spin asymmetries
-vanish \cite{Ellis,Biswas}. Hence, in order to construct observables
-sensitive to the structure of the $tH$ coupling, we will prefer those
-TPs that include information on the decay products of both top and
+cross-section, whereas the TP terms will be sensitive to the sign of
+the anomalous coupling $\kpt$. Of the fifteen TPs mentioned above,
+we will focus on those that contain both of the spin
+vectors $n_t$ and $n_{\tbar}$, but do not include $q$.
+The decision not to consider $q$-dependent TPs is motivated by the fact
+that $q$ cannot be expressed in terms of the momenta of final state
+particles (as $Q$ can, by virtue of energy-momentum conservation). The
+decision to focus on TPs that contain both $n_t$ and $n_{\tbar}$
+is rooted in the fact that the spins of pair-produced top and antitop quarks
+are highly correlated at hadron colliders 
+(even though the quarks themselves are unpolarized). {\bf (KK: did I reword
+  this correctly?)}
+Observables that combine the decay products of the
+$t$ and $\tbar$ will be sensitive to this spin
+correlation~\cite{Bernreuther}.  A similar behaviour is expected in $t\tbar H$
+production, where it can be shown that single-spin asymmetries
+vanish~\cite{Ellis,Biswas}. Hence, in order to construct observables
+sensitive to the structure of the $tH$ coupling, we will restrict our attention
+to those
+TPs that include information on the decay products of both the top and
 anti-top quarks. Only five of the fifteen TPs in Eq.~(\ref{eq20}) do
-not involve the vector $q$ and, among these, we will focus on the
-three that include both $n_t$ and $n_{\tbar}\,$:
+not involve the four vector $q$ and, among these, only three
+include both $n_t$ and $n_{\tbar}\,$.  Thus, we will restrict our attention
+to the following TPs
 %
@@
 
-Finally, we remark that even though all the above discussion was given
+Before turning to a consideration of various CP-odd observables,
+we remark that even though all of the above discussion took place
 within the context of $gg$-initiated production, similar conclusions

### 2016-02-27 Paper_ttbarH_Draft.tex
KK edit: beginning of Sec. III; new diff. pdf file included as well

@@
 \label{sec3}
-We present below three types of observables based on the TPs discussed
-in Sec.~\ref{sec2}, mean values, asymmetries and angular
-distributions. These observables are sensitive not only to the
-magnitude of the pseudoscalar coupling $\kpt$ but also to its
-sign. With the aim of testing them, we have used in all the cases a
-set of $10^5$ events $\ppprocess$ simulated at parton level with
-$\mathtt{MadGraph5\_aMC@NLO}$ \cite{Madgraph} at a center-of-mass
-energy of $14\,\mathrm{TeV}$ for different values of the couplings
-$\kp$ and $\kpt$\footnote{Although we use the same number of events in
-  all the cases, the required luminosities are different since the
-  cross section depends on the value of $\kpt$.}. We have used this
-somewhat large number of events with the aim of determining clearly
-the extent to which the proposed observables are sensitive to the NP
-coupling. However, we will discuss the corresponding experimental
-viability in Sec.~\ref{sec6}. Finally, we have also imposed the
+In this section we present three types of observables based on the TPs discussed
+in Sec.~\ref{sec2}, namely, asymmetries, angular
+distributions and mean values. These observables are sensitive not only to the
+magnitude of the pseudoscalar coupling $\kpt$, but also to its
+sign.  In order to test the various observables, we have
+used $\mathtt{MadGraph5\_aMC@NLO}$ \cite{Madgraph} to simulate the process
+$\ppprocess$ at parton level for different values of the couplings
+$\kp$ and $\kpt$.  In all cases we have generated $10^5$ events
+and have assumed a center-of-mass energy of
+$14\,\mathrm{TeV}$.\footnote{Note that, since we generate
+  the same number of events in
+  each case, the corresponding integrated luminosities are different, since the
+  cross section depends on the value of $\kpt$.}
+We have also imposed the
 following set of cuts: $p_T$ of leptons $> 10\,\mathrm{GeV}$, $|\eta|$
 of leptons $< 2.5$, $|\eta|$ of b jets $< 2.5$ and $\Delta
-R_{\ell\ell}>0.4$.\par Under the assumption of no other new physics
-sources but the inclusion of the pseudoscalar coupling $\kpt$,
-indirect contraints based on the Higgs production from gluon fusion
-followed by its decay to two photons disfavour $\kp < 0$ without
-resolving the degeneracy in the sign of $\kpt$ \cite{Guadagnoli}. On
-the other hand, by assuming the tensor structure of the Lagrangian to
-be the same as in the SM and considering a parameterization with one
-universal Higgs coupling to vector bosons, $\kappa_V$, and one
-universal Higgs coupling to fermions, $\kappa_f$, the measured signal
-strengths provided by ATLAS and CMS collaborations are compatible with
-the values predicted by the SM, ($\kappa_f=1,\kappa_V=1$). Based on
-these facts, we will set the value of the scalar coupling to its SM
-value, $\kp=1$, and concentrate in modifications of the value as well
-as the sign of the pseudoscalar coupling. In particular, we have
-analized the cases $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm
-1$. However, we will give some results and comments regarding the pure
-$\mathrm{CP}$-odd hypothesis ($\kp=0,\kpt=1$).
+R_{\ell\ell}>0.4$.  Note that we have used this
+somewhat large number of events ($10^5$) in order to determine clearly
+the extent to which the proposed observables are sensitive to the NP
+coupling.  Section~\ref{sec6} contains an
+analysis of the experimental feasibility of the more promising observables.
+{\bf (KK: I may not have worded this quite correctly.)}
+
+Before continuing on to our analysis, let us make a few comments
+regarding the values that we choose for $\kp$ and $\kpt$.
+First of all, we note that if the pseudoscalar
+coupling $\kpt$ is the only source of physics beyond the SM,
+then indirect contraints (based on Higgs production via gluon fusion,
+followed by Higgs decay to two photons {\bf (KK: can we just say
+  something like $gg\to H \to \gamma\gamma$?  Or is that not
+  correct?)}) disfavour $\kp < 0$ but do not
+resolve the degeneracy {\bf (KK: did I reword this correctly?)}
+in the sign of $\kpt$ \cite{Guadagnoli}. On
+the other hand, if one assumes that the tensor structure of the
+Higgs interactions are the
+same as those of the SM and if one parameterizes these interactions via
+one universal Higgs coupling to vector bosons, $\kappa_V$, and one
+universal Higgs coupling to fermions, $\kappa_f$, then the measured signal
+strengths provided by the ATLAS and CMS collaborations are compatible with
+the values predicted by the SM, (namely, $\kappa_f=1$ and $\kappa_V=1$).
+With these facts in mind, we will, for the most part,
+set the value of the scalar coupling to its SM
+value ($\kp=1$) and will allow the pseudoscalar coupling to take on
+various values (including both possible signs). In particular, we
+analyze the cases $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm 1$.
+In addition, we also provide some analysis regarding the pure
+$\mathrm{CP}$-odd case ($\kp=0,\kpt=1$).
 %\newpage

### 2016-02-29 Paper_ttbarH_Draft.tex
Changes on secII based on Ken's corrections

--- 2016-02-25 Paper_ttbarH_Draft.tex
@@
 SM case is obtained for $\kp=1$ and $\kpt=0$, while the values $\kp=0$
-and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs
-{\bf KK: ``boson''? I don't think PRD allows us to just say ``Higgs''}. \par
+and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs boson. \par
 %%%%%%%%%%%%%%%%%%%% Figura 1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{center}
-\begin{figure}[th]
+\begin{figure}[H]
 \centering
@@
 corresponds to the eight gluon-initiated
-diagrams indicated in Fig.~\ref{fig1} {\bf (KK: correct?)}; also,
+diagrams indicated in Fig.~\ref{fig1}; also,
 $\epsilon_{\lambda_a}$ and $\epsilon_{\lambda_b}$ are the
@@
 \label{eq8}
-\psi_{\tbar} &=& -g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
+\psi_{\tbar} &=& g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
    \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
@@
 Also, $\mathbb{P}_t(q)=(q^2-m^2_t+im_t\Gamma_t)^{-1}$ and
-$\mathbb{P}_W(q)=(q^2-M^2_W+im_W\Gamma_W)^{-1}$, and
+$\mathbb{P}_W(q)=(q^2-m^2_W+im_W\Gamma_W)^{-1}$, and
 we have denoted the momenta of the various particles by the symbols

### 2016-03-01 Paper_ttbarH_Draft.tex
KK edits to Sec. IIIA.

--- 2016-02-27 Paper_ttbarH_Draft.tex
@@
 \label{sec3.1}
-The first type of $\mathrm{CP}$-odd observable we will consider is the
-asymmetry. For a certain TP, we define an asymmetry which gives the
-balance between the number of events with $\epsilon > 0$ and those for
-which $\epsilon < 0$:
+
+The first type of $\mathrm{CP}$-odd observable that we will consider is an
+asymmetry that compares the number of events
+for which a given TP is positive to that for which it is negative.
+Normalizing to the total number of events, we define
 %
@@
 %
+By construction, $\mathcal{A}\in [-1,+1]$.
 Based on the general expression given in Eq.~(\ref{eq20}), we expect
-the following shape for the asymmetry,
+the following functional form for the asymmetry,
 %
@@
 pseudoscalar coupling, whereas $b\equiv C/B$ quantifies the deviation
-from the linear behaviour.  The results for $\kp=1$ and $\kpt=0,\pm 1$
-are shown in Table \ref{table1}, where the values in terms of the
-corresponding statistical uncertainty are also included. It can be
-seen that the considered asymmetries are useful to separate the
-$\mathrm{CP}$-mixed cases from the SM case and also to discriminate
-the different sign of $\kpt$, giving deviations of order $10\sigma$ in
-the former case and $20\sigma$ in the latter.\par The sensitivity of
+from linear behaviour.
+
+Table~\ref{table1} shows numerical results for the
+asymmetries associated with three different TPs,
+$\epsilon_1$, $\epsilon_2$ and $\epsilon_3$, taking
+$\kp=1$ and $\kpt=0,\pm 1$.  The asymmetry $\mathcal{A}$
+is shown in each case, along with $\mathcal{A}/\sigma_{\mathcal{A}}$, where
+$\sigma_{\mathcal{A}}$ is the corresponding
+statistical uncertainty.  As is
+evident from the table, the asymmetries in question provide
+a clear separation between the SM and the 
+$\mathrm{CP}$-mixed cases, with typical deviations being of
+order $10\sigma$.  Furthermore, the asymmetries
+for the SM case are each statistically consistent with zero,
+as one would expect.
+The three asymmetries also allow one to
+determine the sign of $\kpt$,
+with deviations between the $\kpt = \pm 1$ cases typically
+being of order $20\sigma$.
+{\bf (KK: I guess what we're calculating here is the
+  difference between $\mathcal{A}/\sigma_{\mathcal{A}}$ for
+  one scenario and the same thing for another scenario.  But that
+  could never actually be measured, right\ldots?  Since the scenario
+  is either one or the other\ldots.)}
+The sensitivity of
 the asymmetry is quite similar for the three TPs, as can be seen by
 including other values of $\kpt$ and using the expression in
-Eq.~(\ref{eq23}) as fitting function (see Fig.~\ref{fig3}). In fact,
-we obtain the fit parameters $(a=-0.057\pm 0.006, b=0.5\pm 0.2),
+Eq.~(\ref{eq23}) as a fitting function (see Fig.~\ref{fig3}).
+Performing such a fit, 
+we obtain $(a=-0.057\pm 0.006, b=0.5\pm 0.2),
 (a=-0.056\pm 0.006, b=0.5 \pm 0.2)$ and $(a=0.058\pm 0.006, b=0.6 \pm
 0.2)$ for $\epsilon_1$, $\epsilon_2$ and $\epsilon_3$,
-respectively. In addition, we include in Fig.~\ref{fig4} the asymmetry
-for $\epsilon_1$ isolating the $gg$-initiated, $q\qbar$-initiated and
-$pp$ production. We see that the asymmetry is enhanced for
+respectively.
+
+The results shown in Table~\ref{table1}
+and Fig.~\ref{fig3} all assume a $pp$ initial state, which is
+actually a combination of events coming from $gg$ and $q\qbar$
+initial states.
+While this combination of initial states is the appropriate scenario
+to consider, it
+is interesting to consider the relative contributions to the asymmetry
+coming from the
+$gg$ and $q\qbar$ initial states.  Figure~\ref{fig4} shows
+three curves for the ``$\epsilon_1$'' case, one for $gg$-initiated
+events, one for $q\qbar$-initiated events, and one for the usual
+combination of these events (the``$pp$'' initial state).
+Interestingly, we see from Fig.~\ref{fig4} that the asymmetry for this TP
+is enhanced for
 $gg$-initiated production, while it is reduced and of opposite sign
-for the $q\qbar$-initiated case. The asymmetry for the $pp$ case is
-then dominated by the $gg$ contribution, albeit smaller due to the
+for the $q\qbar$-initiated events. The asymmetry for the $pp$ case is
+evidently
+dominated by the $gg$ contribution, but is somewhat smaller
+in magnitude due to the
 $q\qbar$ contribution.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace*{-6mm} \par On the other hand, we have also tested various
-linear combinations of the TPs $\epsilon_{1,2,3}$, with the result
-that the asymmetry is enhanced in the following case:
+\vspace*{-6mm}
+
+We have also tested various
+linear combinations of the TPs $\epsilon_{1,2,3}$ and have found
+that the asymmetry is enhanced for the following combination:
 %
@@
 %
-Note that in the $Q$ rest frame $\epsilon_4=Q^0
+Note that in the $Q$ rest frame, $\epsilon_4=Q^0
 (\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$ and the
 sign of this TP is determined by the quantity
-$(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$. The
-values obtained for the asymmetry of this TP are shown in
-\ref{table2}. We see by comparing the results in Tables \ref{table1}
-and \ref{table2} that the capability of the asymmetry to separate the
+$(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$.
+{\bf (KK: Is the result from the previous sentence used somewhere?)}
+The
+values obtained for the asymmetry associated with this TP are shown in
+Table~\ref{table2}. By comparing the results in Tables \ref{table1}
+and \ref{table2}, we see that the capability of this
+asymmetry to distinguish between the
 two $\mathrm{CP}$-mixed hypotheses is increased by at least $3\sigma$.
@@
 \end{table}
-\par Finally, it is worth noting that the asymmetry is not useful for
+\par Finally, it is worth noting that the asymmetries
+described in this subsection are not useful for
 discriminating between the SM hypothesis ($\kp=1,\kpt=0$) and the pure
-pseudoscalar hypothesis ($\kp=0,\kpt=1$) because, being linear in both
-$\kp$ and $\kpt$, it is expected to vanish in these cases. However, we
-will show in the next section that there exist angular distributions
-derived from the TPs that are actually suitable to distinguish these
+pseudoscalar hypothesis ($\kp=0,\kpt=1$).  Since
+the numerators of the {\bf (KK: did I reword this correctly?)}
+asymmetries are all linear in both
+$\kp$ and $\kpt$, they expected to vanish in these cases. However, we
+will show in the next section {\bf (KK: subsection?)}
+that there exist angular distributions
+derived from the TPs that are actually suitable for distinguishing between these
 two hyphothesis.

### 2016-03-01 Paper_ttbarH_Draft.tex

@@
 {\bf (KK: Do we mean the adjoint spinor, related by $C \psi^T$,
-  or whatever?)}
+  or whatever?, N: It is $\psi^{\dagger}\gamma^0$. I'm using the name given in Eq(2.28) of Bjorken and Drell's book.)}
 Also, $\mathbb{P}_t(q)=(q^2-m^2_t+im_t\Gamma_t)^{-1}$ and
-$\mathbb{P}_W(q)=(q^2-M^2_W+im_W\Gamma_W)^{-1}$, and
+$\mathbb{P}_W(q)=(q^2-m^2_W+im_W\Gamma_W)^{-1}$, and
 we have denoted the momenta of the various particles by the symbols
@@
 where we have separated the colour structure of each diagram by defining
-{\bf (KK: do these need $k$ subscripts?)}
-$\mathcal{S}^{ab,ij}= C^{ab,ij}_k \mathcal{S}$ and
-$\mathcal{P}^{ab,ij}= C^{ab,ij}_k \mathcal{P}$
+$\mathcal{S}^{\,ab,ij}_k= C^{ab,ij}_k \mathcal{S}_k$ and
+$\mathcal{P}^{\,ab,ij}_k= C^{ab,ij}_k \mathcal{P}_k$
 [see Eqs.~(\ref{eq5}) and (\ref{eq16})]. Also, the factors
@@
 C^{ab,ij*}_r$ is real and where $\tilde{\mathcal{P}}_r = \gamma^0
-\mathcal{P}_r \gamma^0$ {\bf (KK: wouldn't this be
-  $\mathcal{P}_r^\dagger$? I didn't look for this in the notes
-  yet, so maybe I'm just missing something)}.
+\mathcal{P}^{\dagger}_r \gamma^0$.
 The only terms that yield non-zero contributions
@@
 are highly correlated at hadron colliders 
-(even though the quarks themselves are unpolarized). {\bf (KK: did I reword
-  this correctly?)}
+(even though the quarks themselves are unpolarized).
 Observables that combine the decay products of the
@@
 analysis of the experimental feasibility of the more promising observables.
-{\bf (KK: I may not have worded this quite correctly.)}
 
@@
   correct?)}) disfavour $\kp < 0$ but do not
-resolve the degeneracy {\bf (KK: did I reword this correctly?)}
-in the sign of $\kpt$ \cite{Guadagnoli}. On
+resolve the degeneracy in the sign of $\kpt$ \cite{Guadagnoli}. On
 the other hand, if one assumes that the tensor structure of the
@@
 pseudoscalar hypothesis ($\kp=0,\kpt=1$).  Since
-the numerators of the {\bf (KK: did I reword this correctly?)}
+the numerators of the 
 asymmetries are all linear in both
-$\kp$ and $\kpt$, they expected to vanish in these cases. However, we
-will show in the next section {\bf (KK: subsection?)}
+$\kp$ and $\kpt$, they {\bf are} expected to vanish in these cases. However, we
+will show in the next subsection
 that there exist angular distributions

### 2016-03-01 Paper_ttbarH_Draft.tex
Changes discussed in skype meeting

@@
 We then use this expression to isolate various mathematical quantities
-that will be useful as we construct $\mathrm{CP}$-odd observables.
-
-\subsection{Factorized expression for the scattering cross section}
+that will be useful as we construct $\mathrm{CP}$-odd observables.\par
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-In this section we focus on the gluon fusion contributions
+\subsection{Factorized expression for the scattering cross section}
+
+In this subsection we focus on the gluon fusion contributions
 to $t\tbar H$ production, since these dominate over the
@@
 particle $i$ and $\langle i+(-)|$ represents the corresponding adjoint spinor.
-{\bf (KK: Do we mean the adjoint spinor, related by $C \psi^T$,
-  or whatever?, N: It is $\psi^{\dagger}\gamma^0$. I'm using the name given in Eq(2.28) of Bjorken and Drell's book.)}
 Also, $\mathbb{P}_t(q)=(q^2-m^2_t+im_t\Gamma_t)^{-1}$ and
@@
   which is replaced by $(\pi/m_t\Gamma_t)\delta(t^2-m^2_t)$
-  in the narrow-width approximation.  Thus we take the four-vector
-  $t$ appearing in the definition of $\phi_t$ to be
-  on shell, satisfying $t^2 = m_t^2$.} {\bf (KK: Do I understand correctly
-  that $t$ is an on-shell four-vector in $t\cdot \ell^+$, but not
-  in $\mathbb{P}_t(t)$?  This is similar to saying $f(x)\delta(x-x_0) =
-  f(x_0)\delta(x-x_0)$\ldots?)}
+  in the narrow-width approximation.  Thus, except for the propagator terms $\mathbb{P}_t(t)$ and $\mathbb{P}_t(\tbar)$,
+   we take the four-vector $t$ appearing in Eqs.~(\ref{eq9})-(\ref{eq11}) to be
+  on shell, satisfying $t^2 = m_t^2$.} 
 Working out the projection operators $\phi_t\,\bar{\phi}_t$
@@
 propagator terms, $\mathbb{P}_t(t)$ and $\mathbb{P}_t(\tbar)$,
-we arrive at the expression in Eq.~(\ref{eq2}).  This expression
+we arrive at the expression in Eq.~(\ref{eq2}).\footnote{The reader may note that in the differential widths of $t\to b{\ell}^+\nu_{\ell}$ and $\tbar\to \bar{b}{\ell}^-\bar{\nu}_{\ell}$ appearing in 
+Eq.~(\ref{eq2}), the spin states of the top an antitop have been averaged.
+Interestingly, under the assumption of massless final-state particles, the amplitudes $\mathcal{M}(t(-n_t)\to b{\ell}^+\nu_{\ell})$ and $\mathcal{M}(\tbar(-n_{\tbar})\to \bar{b}{\ell}^-\bar{\nu}_{\ell})$ vanish.
+} This expression
 also has the appearance of being factorized, but
 qualifying remarks, similar to those above, apply.
-{\bf (KK: I'm still a bit confused as to why $n_t$ appears
-  in the amplitude expression for the decay, but not
-  in the expression for the cross section.  That is, the top
-  spins are summed over in the width that appears in the
-  factorized expression for the cross section.  That part makes
-  sense to me, but I'm not so clear on how to get there from
-  Eq.~(17).  Probably need to look more closely at the notes!)}
 
@@
 
-\subsection{Triple products}
-{\bf (KK: maybe we should change this title for the subsection\ldots.)}
+\subsection{Origin of Triple product terms}
 
@@
 coupling $\kpt$ is the only source of physics beyond the SM,
-then indirect contraints (based on Higgs production via gluon fusion,
-followed by Higgs decay to two photons {\bf (KK: can we just say
-  something like $gg\to H \to \gamma\gamma$?  Or is that not
-  correct?)}) disfavour $\kp < 0$ but do not
+then indirect contraints (based on the signal strength of $gg\to H \to \gamma\gamma$) 
+disfavour $\kp < 0$ but do not
 resolve the degeneracy in the sign of $\kpt$ \cite{Guadagnoli}. On
@@
 being of order $20\sigma$.
-{\bf (KK: I guess what we're calculating here is the
-  difference between $\mathcal{A}/\sigma_{\mathcal{A}}$ for
-  one scenario and the same thing for another scenario.  But that
-  could never actually be measured, right\ldots?  Since the scenario
-  is either one or the other\ldots.)}
+{\bf (We couldn't figure out how to clarify this. If you find a way go ahead\ldots.)}
 The sensitivity of
@@
 asymmetries are all linear in both
-$\kp$ and $\kpt$, they {\bf are} expected to vanish in these cases. However, we
+$\kp$ and $\kpt$, they expected to vanish in these cases ({\bf ``..they are expected to.."? Maybe it's a typo? we are not sure}). However, we
 will show in the next subsection

### 2016-03-02 Paper_ttbarH_Draft.tex
KK edits up to Eq. (30)

@@
 %
-Before turning to a discussion of $\mathrm{CP}$-odd observables,
-it is useful to consider a few theoretical aspects of
-the process $\ppprocess$.  In this section we derive a ``factorized''
-expression for the gluon fusion contribution to this process.
-We then use this expression to isolate various mathematical quantities
-that will be useful as we construct $\mathrm{CP}$-odd observables.\par
 
@@
 SM case is obtained for $\kp=1$ and $\kpt=0$, while the values $\kp=0$
-and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs boson. \par
+and $\kpt\neq 0$ parameterize a $\mathrm{CP}$-odd Higgs boson.
+
+Before turning to a discussion of $\mathrm{CP}$-odd observables,
+it is useful to consider a few theoretical aspects of
+the process $\ppprocess$.
+In the following subsections we derive a ``factorized''
+expression for the gluon fusion contribution to this process
+and then use this expression
+to isolate various mathematical quantities
+that will be useful as we construct $\mathrm{CP}$-odd observables.\par
+
 %%%%%%%%%%%%%%%%%%%% Figura 1%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection{Factorized expression for the scattering cross section}
-
-In this subsection we focus on the gluon fusion contributions
+\label{subsec:factorize}
+
+In this subsection we focus on the gluon fusion
+{\bf (KK: seems repetitive to say ``gluon fusion'' right away
+  again\ldots maybe can change this; maybe OK to leave it?)}
+contributions
 to $t\tbar H$ production, since these dominate over the
@@
 
-\subsection{Origin of Triple product terms}
+\subsection{Origin of triple product terms}
+\label{subsec:origin}
 
@@
 events, one for $q\qbar$-initiated events, and one for the usual
-combination of these events (the``$pp$'' initial state).
+combination of these events (the ``$pp$'' initial state).
 Interestingly, we see from Fig.~\ref{fig4} that the asymmetry for this TP
@@
 \begin{table}[H]
-\caption{Asymmetries obtained by using $10^5$ simulated events for the
-  TPs $\epsilon_1=\TPa, \epsilon_2=\TPb$ and $\epsilon_3=\TPc$ in the
-  SM case and the two $\mathrm{CP}$-mixed cases defined by
-  $\kp=1,\kpt=\pm 1$.}
+  \caption{Asymmetries for three different scenarios,
+    obtained by using $10^5$ simulated events for the
+    TPs $\epsilon_1=\TPa, \epsilon_2=\TPb$ and $\epsilon_3=\TPc$.
+    The three scenarios
+  correspond to the SM ($\kp=1$ and $\kpt=\pm 0$) and
+  two $\mathrm{CP}$-mixed cases (defined by
+  $\kp=1$ and $\kpt=\pm 1$).}
 \label{table1}
@@
 $(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$.
-{\bf (KK: Is the result from the previous sentence used somewhere?)}
+{\bf (KK: try to connect previous sentences to something later on\ldots.)}
 The
@@
 asymmetries are all linear in both
-$\kp$ and $\kpt$, they expected to vanish in these cases ({\bf ``..they are expected to.."? Maybe it's a typo? we are not sure}). However, we
+$\kp$ and $\kpt$, they are expected to vanish in these cases. However, we
 will show in the next subsection
@@
 derived from the TPs that are actually suitable for distinguishing between these
-two hyphothesis.
+two hyphotheses.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec3.2}
-Given a certain TP, it is possible to define asocciated angular
-distributions that are also sensitive to the pseudoscalar coupling
+
+Given a certain TP, it is possible to define associated angular
+distributions that are sensitive to the pseudoscalar coupling
 $\kpt$. In order to clarify this, let us first consider the TP
 $\epsilon(t,\tbar,n_t,n_{\tbar})$. This TP can be written as
-$\epsilon(t+\tbar,\tbar,n_t,n_{\tbar})$ so that in the reference frame
+$\epsilon(t+\tbar,\tbar,n_t,n_{\tbar})$, so that in the reference frame
 defined by $\vec{t}+\vec{\tbar} =0$ and $\vec{\tbar}\parallel \hat{z}$
@@
 angles $\theta_{n_t}$ and $\theta_{n_{\tbar}}$ denote the polar angles
-of $\vec{n}_t$ and $\vec{n}_{\tbar}$ respectively and finally
+of $\vec{n}_t$ and $\vec{n}_{\tbar}$, respectively, and 
 $\Delta\phi(n_t,n_{\tbar})$ is the angular difference between the
 projections of $\vec{n}_t$ and $\vec{n}_{\tbar}$ onto the plane
-perpendicular to $\vec{\bar{t}}$. If we define this angle within the
+perpendicular to $\vec{\bar{t}}$. If we define the angle
+$\Delta\phi(n_t,n_{\tbar})$  to be within the
 range $[-\pi,\pi]$, we see from Eq.~(\ref{eq25}) that its sign will
-determine the sign of the TP. In this sense, the distribution of the
-number of the events with respect to the angle
+determine the sign of the TP. Thus, the distribution of the
+number of events with respect to the angle
 $\Delta\phi(n_t,n_{\tbar})$ is related to the asymmetry of the TP,
@@
 %
-where $N_T$ is the total number of events. Moreover, from a certain TP
+where $N_T$ is the total number of events.
+{\bf (KK: Have we checked numerically that the above
+  expression does indeed hold numerically for the various
+  distributions?  It's an exact relation, correct?)}
+Moreover, for a certain TP
 one can derive different angular distributions by considering
-different reference frames, but all of these will satisfy
-Eq.~(\ref{eq26}). In particular, we will analyze the following angular
-distributions based on the TPs defined in Sec.~\ref{sec2}:
-\begin{itemize}
-\item Related to $\epsilon_1 = \TPa$ we consider
-  $d\sigma/d\Delta\phi_1(n_t,n_{\tbar})$ in the rest frame of $t\tbar$
-  with $\vec{\tbar}$ in the $z$-axis. The angle
+different reference frames, although all of these will satisfy
+Eq.~(\ref{eq26}) (note that $\mathcal{A}(\epsilon)$
+is Lorentz invariant). Recalling the various TPs considered
+in Sec.~\ref{sec2}, we examine the following angular distributions.
+\begin{enumerate}
+\item {\boldmath $\epsilon_1 = \TPa$.}  To probe $\epsilon_1$, we construct
+  the distribution
+  $d\sigma/d\Delta\phi_1(n_t,n_{\tbar})$ in the rest frame of $t\tbar$,
+  taking $\vec{\tbar}$ to define the $z$-axis. The angle
   $\Delta\phi_1(n_t,n_{\tbar})$ is the angular difference between the
@@
   $\vec{\tbar}$.
-\item Related to $\epsilon_2 = \TPb$ we consider
-  $d\sigma/d\Delta\phi_2(n_t,n_{\tbar})$ in the rest frame of $Q$ with
-  $\vec{\tbar}$ in the $z$-axis. The angle
+\item {\boldmath $\epsilon_2 = \TPb$.}  In this case, we
+  define the distribution
+  $d\sigma/d\Delta\phi_2(n_t,n_{\tbar})$ in the rest frame of $Q$, taking
+  $\vec{\tbar}$ to define the $z$-axis. The angle
   $\Delta\phi_2(n_t,n_{\tbar})$ is the angular difference between the
@@
   $\vec{\tbar}$.
-\item Related to $\epsilon_3 = \TPc$ we consider
-  $d\sigma/d\Delta\phi_3(n_t,n_{\tbar})$ in the rest frame of $Q$ with
-  $\vec{t}$ in the $z$-axis. The angle $\Delta\phi_3(n_t,n_{\tbar})$
+\item {\boldmath $\epsilon_3 = \TPc$.}  The distribution
+  $d\sigma/d\Delta\phi_3(n_t,n_{\tbar})$ is also defined
+  in the rest frame of $Q$, but this time taking
+  $\vec{t}$ to be along the $z$-axis. The angle $\Delta\phi_3(n_t,n_{\tbar})$
   is the angular difference between the projection of the spin vectors
   in the plane perpendicular to $\vec{t}$.
-\end{itemize}
+\end{enumerate}
 \par
 %
-In Fig.~\ref{fig5} we present the normalized distributions obtained
-for the first case listed above with $\kp= 1,\kpt=0$
-($\mathrm{CP}$-even Higgs boson), $\kp= 1,\kpt=\pm 1$
-($\mathrm{CP}$-mixed Higgs boson) and $\kp= 0,\kpt=1$
-($\mathrm{CP}$-odd Higgs boson). In Fig.~\ref{fig6} we display in turn
+Figure~\ref{fig5} shows the normalized distributions obtained
+for the first case listed above.
+Four scenarios are considered, corresponding to the SM
+($\kp= 1$ and $\kpt=0$), two cases in which the Higgs boson
+has mixed $\mathrm{CP}$ couplings ($\kp= 1$ and $\kpt=\pm 1$)
+and a case in which the Higgs boson is purely 
+$\mathrm{CP}$-odd ($\kp= 0,\kpt=1$). Figure~\ref{fig6} shows
 the analogous distributions for $\epsilon_2$. The distributions
-correponding to $\epsilon_3$ are similar to those of $\epsilon_2$ but
-with the opposite shift for $\kp=\kpt=1$ and $\kp=-\kpt=1$ and then we
-do not include them here.
+corresponding to $\epsilon_3$ are similar to those of $\epsilon_2$,
+except that the ``shifts'' are in the opposite directions for
+the two mixed-$\mathrm{CP}$ cases.  Given the similarities of the
+plots we do not include them here.  {\bf (KK: did I reword this correctly?)}
 %%%%%%%%%%%%%%%%%%%%%%%%% FIGURA 5 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \caption{Angular distributions associated with the TP
-  $\epsilon(t,\tbar,n_t,n_{\tbar})$ for various values of
-  $(\kp,\kpt)$. The error bars correspond to the statistical
+  $\epsilon_1 = \epsilon(t,\tbar,n_t,n_{\tbar})$ for various values of
+  $\kp$ and $\kpt$. The error bars correspond to the statistical
   uncertainties.}
@@
 \subfloat{\includegraphics[scale=0.45]{TP2_1-1_nuevo.pdf}}
-\caption{Angular distributions associated with the TP $\TPb$ for
-  various values of $(\kp,\kpt)$. The error bars correspond to the
-  statistical uncertainties.}
+\caption{Angular distributions associated with the TP $\epsilon_2 = \TPb$ for
+  various values of $\kp$ and $\kpt$. The error bars indicate the statistical
+  uncertainties.}
 \label{fig6}
@@
 \end{center}
-\par As can be seen from Figs.~\ref{fig5} and \ref{fig6}, the peak of
-the distributions is shifted according to the values of the couplings
-$\kp, \kpt$. This shift appears to be approximately the same but with
-opposite sign for $\kp=\kpt=1$ and $\kp=-\kpt=1$, distinguishing then
-the sign of the pseudoscalar coupling. The last is the expected
-behaviour since the asymmetry is linear in $\kpt$ (see
-Sec.~\ref{sec3.1}) and the quantity $N(\epsilon < 0)/N_T$ is related
-to the angular distribution according to Eq.~(\ref{eq26}). The
-distributions for the SM and the pure pseudoscalar hypotheses are
-clearly different. While in the former case the distributions exhibit
-a minimum at $\Delta\phi_{1,2}(n_t,n_{\tbar})=0$, in the latter the
-similar distributions display a peak, so that the two hypotheses can
-be discriminated, in contrast to the asymmetry that vanishes for both
-hypotheses. In order to quantify the mentioned shifts, we have fitted
+\par As can be seen from Figs.~\ref{fig5} and \ref{fig6}, the
+peaks of the 
+distributions are shifted to the left or the right of the origin
+in the mixed-$\mathrm{CP}$
+cases ($\kp =1$ and $\kpt=\pm 1$).
+The magnitude of the shift appears to be approximately the
+same in both cases, but with
+opposite sign for $\kp=\kpt=1$ and $\kp=-\kpt=1$, thus allowing
+one to distinguish
+the sign of the pseudoscalar coupling. The observed dependence
+on the sign of $\kpt$ in these cases
+is consistent with the fact that the numerator of $\mathcal{A}(\epsilon)$
+is linear in $\kpt$ [see Eq.~(\ref{eq26})]
+and that the quantity $N(\epsilon < 0)/N_T$ is related
+to the angular distribution according to Eq.~(\ref{eq26}). The angular
+distributions for the SM case ($\kp =1$ and $\kpt=0$) and
+the pure pseudoscalar case ($\kp =0$ and $\kpt= 1$) are
+visibly different from each other and from the mixed-$\mathrm{CP}$
+scenarios. Comparing the SM and purely pseudoscalar cases,
+we note that while the angular distributions for the former case
+exhibit a minimum at $\Delta\phi_{1,2}(n_t,n_{\tbar})=0$, those
+for the latter case exhibit a peak at this location.
+Thus, these two scenarios can be distinguished from each other
+via these angular distributions.  This is to be contrasted
+with the situation for the asymmetries $\mathcal{A}(\epsilon)$, which vanish
+in both cases.  In order to quantify the mentioned shifts, we have fitted
 the simulated distributions with the following function proposed in

### 2016-03-02 Paper_ttbarH_Draft.tex
Minor changes plus new files for Figs.5 and 6

@@
 
-%
-
 At the LHC $t\bar{t}H$ production proceeds via $q\bar{q}$
@@
 it is useful to consider a few theoretical aspects of
-the process $\ppprocess$.
+the process $\ppprocess$, in which the top and antitop both decay
+semileptonically.
 In the following subsections we derive a ``factorized''
@@
 
-In this subsection we focus on the gluon fusion
-{\bf (KK: seems repetitive to say ``gluon fusion'' right away
-  again\ldots maybe can change this; maybe OK to leave it?)}
+In this subsection we focus on the $gg$-initiated
 contributions
 to $t\tbar H$ production, since these dominate over the
-the quark-antiquark annihilation contributions.  Furthermore,
-we consider the case in which the top and antitop both decay
-semileptonically.  As we shall show below, assuming the
+the quark-antiquark annihilation contributions. As we shall show below, assuming the
 narrow width approximation for the top and antitop quarks, the unpolarized
@@
 the two mixed-$\mathrm{CP}$ cases.  Given the similarities of the
-plots we do not include them here.  {\bf (KK: did I reword this correctly?)}
+plots we do not include them here. 
 %%%%%%%%%%%%%%%%%%%%%%%%% FIGURA 5 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\centering
-\hspace*{-0.52cm}
-\subfloat{\includegraphics[scale=0.45]{TP1_10_nuevo.pdf}}
+\hspace*{-0.55cm}
+%\subfloat{\includegraphics[scale=0.443]{TP1_10_nuevo.pdf}}
+\subfloat{\includegraphics[scale=0.45]{NEW_TP1_1_0.pdf}}
 \hspace*{-0.006\textwidth}
-\subfloat{\includegraphics[scale=0.45]{TP1_01_nuevo.pdf}} \\
-\hspace*{-0.45cm}
+\subfloat{\includegraphics[scale=0.45]{NEW_TP1_0_1.pdf}} \\
+\hspace*{-0.55cm}
 %\hspace*{0.03\textwidth}
-\subfloat{\includegraphics[scale=0.45]{TP1_11_nuevo.pdf}}
+\subfloat{\includegraphics[scale=0.45]{NEW_TP1_1_1.pdf}}
 \hspace*{-0.006\textwidth}
-\subfloat{\includegraphics[scale=0.45]{TP1_1-1_nuevo.pdf}}
+\subfloat{\includegraphics[scale=0.45]{NEW_TP1_1_-1.pdf}}
+\vspace*{1cm}
 \caption{Angular distributions associated with the TP
@@
 \hspace*{-0.52cm}
-\subfloat{\includegraphics[scale=0.45]{TP2_10_nuevo.pdf}}
+\subfloat{\includegraphics[scale=0.45]{NEW_TP2_1_0.pdf}}
 \hspace*{-0.006\textwidth}
-\subfloat{\includegraphics[scale=0.45]{TP2_01_nuevo.pdf}} \\
-\hspace*{-0.45cm}
+\subfloat{\includegraphics[scale=0.45]{NEW_TP2_0_1.pdf}} \\
+\hspace*{-0.56cm}
 %\hspace*{0.03\textwidth}
-\subfloat{\includegraphics[scale=0.45]{TP2_11_nuevo.pdf}}
-\hspace*{-0.006\textwidth}
-\subfloat{\includegraphics[scale=0.45]{TP2_1-1_nuevo.pdf}}
+\subfloat{\includegraphics[scale=0.45]{NEW_TP2_1_1.pdf}}
+\hspace*{0.002\textwidth}
+\subfloat{\includegraphics[scale=0.45]{NEW_TP2_1_-1.pdf}}
+%\subfloat{\includegraphics[scale=0.45]{TP2_1-1_nuevo.pdf}}
 \caption{Angular distributions associated with the TP $\epsilon_2 = \TPb$ for
@@
 is consistent with the fact that the numerator of $\mathcal{A}(\epsilon)$
-is linear in $\kpt$ [see Eq.~(\ref{eq26})]
+is linear in $\kpt$ [see Eq.~(\ref{eq23})]
 and that the quantity $N(\epsilon < 0)/N_T$ is related

### 2016-03-02 Paper_ttbarH_Draft.tex
KK edits to Sec. IIIB

--- 2016-03-02 Paper_ttbarH_Draft.tex
@@
 The magnitude of the shift appears to be approximately the
-same in both cases, but with
-opposite sign for $\kp=\kpt=1$ and $\kp=-\kpt=1$, thus allowing
+same in both cases, but is in the
+opposite direction for $\kp=\kpt=1$ compared to $\kp=-\kpt=1$, thus allowing
 one to distinguish
@@
 with the situation for the asymmetries $\mathcal{A}(\epsilon)$, which vanish
-in both cases.  In order to quantify the mentioned shifts, we have fitted
-the simulated distributions with the following function proposed in
-\cite{Ellis},
+in both cases.
+
+In order to quantify the shifts discussed above, we have fitted
+the simulated distributions with the following function, which was proposed in
+Ref.~\cite{Ellis},
 %
@@
 %
-To the extent that this equation is exact we note that
-Eq.~(\ref{eq29}) gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
-this fitting function, we obtain phase shifts approximately between
+To the extent that the above expression is exact, we note that
+Eq.~(\ref{eq26}) {\bf (KK: corrected the equation number; please check\ldots )}
+gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
+this fitting function, we obtain phase shifts $\delta$ that
+are approximately between
 $0.9$ and $1$ ($-1$ and $-0.9$) for $\kp=\kpt=1$ ($\kp=-\kpt=1$) both
 for $\epsilon_1$ and $\epsilon_2$. However, the quality of the fits is
-not good enough, being worse in the case of the $\epsilon_1$
-distributions for which $\chi^2/\mathrm{d.o.f}$ is in the range
-$1.69$-$3.86$, in contrast to the range $0.53$-$1.16$ obtained for
-$\epsilon_2$. The main impact on the deviation from the functional
-form proposed in Eq.~(\ref{eq27}) appears to be caused by the $\Delta
-R_{ll}$ cut we have imposed. In fact, when this cut is turned off the
-above ranges for $\chi^2/\mathrm{d.o.f}$ modify to $0.75$-$1.14$ and
-$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions
-respectively. In Tables \ref{table3} and \ref{table4} we list the
+not very good, particularly for $\epsilon_1$.  The
+$\chi^2/\mathrm{d.o.f}$ for the fits in this case are in the range
+$1.69$-$3.86$, while for $\epsilon_2$ they are in the range $0.53$-$1.16$.
+{\bf (KK: Did we do 4 fits for each $\epsilon$?  Or only 2?  If only 2, maybe
+  saying ``in the range'' is not quite correct, since the two
+  data points are simply the endpoints of the ``range''.  If
+  the range includes all 4 fits for each, maybe we could state that
+  explicitly, since the preceding sentences are only discussing the two
+  mixed-CP scenarios.)}
+The leading source of the deviation from the functional
+form proposed in Eq.~(\ref{eq27}) appears to be the $\Delta
+R_{ll}$ cut that we have imposed. In fact, when this cut is turned off, the
+above ranges for $\chi^2/\mathrm{d.o.f}$ become $0.75$-$1.14$ and
+$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions,
+respectively. Tables \ref{table3} and \ref{table4} list the
 results of the fits obtained when the $\Delta R_{\ell\ell}$ cut is
-relaxed. The results for the TP $\epsilon_3$ are pretty similar to
-those for $\epsilon_2$ but with opposite sign in the phase shifts of
-the $\mathrm{CP}$-mixed hypotheses and hence we do not include them
-here. In addition, we show in Fig.~\ref{fig7} the angular
-distributions along with the fit curves for both $\mathrm{CP}$-mixed
-cases when no cut is imposed in $\Delta R_{\ell\ell}$.
+relaxed.  Also, 
+Fig.~\ref{fig7} shows the angular
+distributions, along with the fit curves, for the $\mathrm{CP}$-mixed
+cases with the $\Delta R_{\ell\ell}$ cut turned off.
+The results for the TP $\epsilon_3$ are relatively similar to
+those for $\epsilon_2$, except that the phase shifts have the opposite
+sign in the $\mathrm{CP}$-mixed cases.  Given this similarity
+we do not include the results for the $\epsilon_3$ distribution
+here. 
 \renewcommand{\arraystretch}{1.2}
@@
 \caption{Fit results for the angular distribution $d\sigma/(\sigma
-  d\Delta\phi_1(n_t,n_{\tbar}))$ related to the TP
-  $\epsilon_1=\epsilon(t,\tbar,n_t,n_{\tbar})$ when the $\Delta
-  R_{\ell\ell}$ is turned off. Note that the parameter $a_1$ change
-  its sign for $\kp=0,\kp=1$.}
+  d\Delta\phi_1(n_t,n_{\tbar}))$ (related to the TP
+  $\epsilon_1=\epsilon(t,\tbar,n_t,n_{\tbar})$) with the $\Delta
+  R_{\ell\ell}$ cut turned off. Note that the sign of the parameter $a_1$
+  changes for $\kp=0,\kp=1$, compared to the
+  other cases.  {\bf (KK: Do we restrict $\delta$ to be between
+    $\pm \pi/2$?  If not, we could require $a_1$ to always
+    be positive, and absorb the sign change by a shift of $\delta$ by $\pi$
+    or ssomething.  Maybe we should clarify the range allowed for $\delta$.)} }
 \label{table3}
@@
 \caption{Fit results for the angular distribution $d\sigma/(\sigma
-  d\Delta\phi_2(n_t,n_{\tbar}))$ related to the TP
-  $\epsilon_2=\epsilon(Q,\tbar,n_t,n_{\tbar})$ when the $\Delta
-  R_{\ell\ell}$ is turned off. Note that the parameter $a_1$ change
-  its sign for $\kp=0,\kp=1$.}
+  d\Delta\phi_2(n_t,n_{\tbar}))$ (related to the TP
+  $\epsilon_2=\epsilon(Q,\tbar,n_t,n_{\tbar})$), with the $\Delta
+  R_{\ell\ell}$ cut turned off. As was the case in Table~\ref{table3},
+  the sign of the parameter $a_1$ changes for
+  $\kp=0,\kp=1$.}
 \label{table4}
@@
   d\Delta\phi_2(n_t,n_{\tbar}))$ (bottom) associated with the TPs
-  $\epsilon_1=\TPa$ and $\epsilon_2=\TPb$ respectively for the
+  $\epsilon_1=\TPa$ and $\epsilon_2=\TPb$, respectively, for the
   $\mathrm{CP}$-mixed cases $\kp=\kpt=1$ (left) and $\kp=-\kpt=1$
-  (right) when the $\Delta R_{\ell\ell}$ cut is turned off. Also, the
-  corresponding fit curves are displayed in red.}
+  (right).  The $\Delta R_{\ell\ell}$ cut was turned off when
+  generating these results. The
+  corresponding fit curves [see Eq.~(\ref{eq27})] are displayed in red.}
 \label{fig7}

### 2016-03-02 Paper_ttbarH_Draft.tex
KK edits up through the end of Sec. IIIB

--- 2016-03-02 Paper_ttbarH_Draft.tex
@@
 %
-To the extent that this equation is exact we note that
-Eq.~(\ref{eq29}) gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
-this fitting function, we obtain phase shifts approximately between
-$0.9$ and $1$ ($-1$ and $-0.9$) for $\kp=\kpt=1$ ($\kp=-\kpt=1$) both
-for $\epsilon_1$ and $\epsilon_2$. However, the quality of the fits is
-not good enough, being worse in the case of the $\epsilon_1$
-distributions for which $\chi^2/\mathrm{d.o.f}$ is in the range
-$1.69$-$3.86$, in contrast to the range $0.53$-$1.16$ obtained for
-$\epsilon_2$. The main impact on the deviation from the functional
-form proposed in Eq.~(\ref{eq27}) appears to be caused by the $\Delta
-R_{ll}$ cut we have imposed. In fact, when this cut is turned off the
-above ranges for $\chi^2/\mathrm{d.o.f}$ modify to $0.75$-$1.14$ and
-$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions
-respectively. In Tables \ref{table3} and \ref{table4} we list the
+To the extent that the above expression is exact, we note that
+Eq.~(\ref{eq26}) {\bf (KK: corrected the equation number; please check\ldots )}
+gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
+this fitting function, we obtain phase shifts $\delta$ that
+are approximately between
+$0.9$ and $1$ ($-1$ and $-0.9$) for $\kp=\kpt=1$ ($\kp=-\kpt=1$), both
+for $\epsilon_1$ and $\epsilon_2$.\footnote{The results for the
+  TP $\epsilon_3$ are relatively similar to
+  those for $\epsilon_2$, except that the phase shifts have the opposite
+  sign in the $\mathrm{CP}$-mixed cases.  Given this similarity
+  we do not include the corresponding results for the $\epsilon_3$ distribution
+  here. {\bf (KK: OK to move this to a footnote?)}}  However, the quality of the fits is
+not very good, particularly for $\epsilon_1$.  The
+$\chi^2/\mathrm{d.o.f}$ for the fits in this case are in the range
+$1.69$-$3.86$, while for $\epsilon_2$ they are in the range $0.53$-$1.16$.
+{\bf (KK: Did we do 4 fits for each $\epsilon$?  Or only 2?  If only 2, maybe
+  saying ``in the range'' is not quite correct, since the two
+  data points are simply the endpoints of the ``range''.  If
+  the range includes all 4 fits for each, maybe we could state that
+  explicitly, since the preceding sentences are only discussing the two
+  mixed-CP scenarios.)}
+The deviation from the functional
+form proposed in Eq.~(\ref{eq27}) appears to be due primarily to the $\Delta
+R_{ll}$ cut that we have imposed. In fact, when this cut is turned off, the
+above ranges for the $\chi^2/\mathrm{d.o.f}$ become $0.75$-$1.14$ and
+$0.44$-$1.07$ for the $\epsilon_1$ and $\epsilon_2$ distributions,
+respectively. Tables \ref{table3} and \ref{table4} list the
 results of the fits obtained when the $\Delta R_{\ell\ell}$ cut is
-relaxed. The results for the TP $\epsilon_3$ are pretty similar to
-those for $\epsilon_2$ but with opposite sign in the phase shifts of
-the $\mathrm{CP}$-mixed hypotheses and hence we do not include them
-here. In addition, we show in Fig.~\ref{fig7} the angular
-distributions along with the fit curves for both $\mathrm{CP}$-mixed
-cases when no cut is imposed in $\Delta R_{\ell\ell}$.
+relaxed.  Figure~\ref{fig7} shows the corresponding
+plots for a couple of the scenarios.
+As is evident from Tables \ref{table3} and \ref{table4}, the
+parameter $\delta$ is sensitive not only to the modulus of $\kpt$ but
+also to its sign, as would be expected from Eq.~(\ref{eq26}).
+The phase shift $\delta$ for the $\Delta\phi_1$ distribution
+appears to exhibit a slightly higher sensitivity than
+that obtained for the $\Delta\phi_2$ distribution, although the corresponding
+numerical values obtained for the various scenarios are
+compatible to within their statistical uncertainties. It is
+important to stress, however, that the fits for the $\Delta\phi_2$ distributions
+always yield smaller values for the $\chi^2/\mathrm{d.o.f}$.
+
 \renewcommand{\arraystretch}{1.2}
@@
 \end{table}
-\par From Tables \ref{table3} and \ref{table4} we see that the
-parameter $\delta$ is sensitive not only to the modulus of $\kpt$ but
-also to its sign, as expected if Eq.~(\ref{eq26}) is taken into
-account. The phase shift $\delta$ for the distribution of the angle
-$\Delta\phi_1$ appears to exhibit a slightly higher sensitivity than
-that obtained from the $\Delta\phi_2$-distribution, albeit both are
-still compatible within the statistical uncertainties. However, it is
-important to stress that the fits of the $\Delta\phi_2$-distributions
-give allways smaller values for $\chi^2/\mathrm{d.o.f}$.
+\par
+
 %%%%%%%%%%%%%%%%%%%%%%%%% FIGURA 7 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{center}
-\par Concerning the angular distributions that can be related to the
-combination $\epsilon_4$, we have analized the
-$\Delta\phi(n_t,n_{\tbar})$ distribution in the $Q$ rest frame with
-$H$ in the $z$-axis for various values of $\kp$ and $\kpt$. We have
-found that these distributions are not described by Eq.~(\ref{eq27})
+\par
+
+In Sec.~\ref{sec3.1} we defined a fourth triple product,
+$\epsilon_4 = \epsilon_3-\epsilon_2$.  We have constructed
+an angular distribution related to this TP as well.
+Specifically, we have analyzed the
+$\Delta\phi(n_t,n_{\tbar})$ distribution in the $Q$ rest frame,
+taking
+$H$ to define the $z$-axis.  By studying the distributions
+for various values of $\kp$ and $\kpt$, we have
+found that they are not well described by Eq.~(\ref{eq27})
 and their range of variation is larger than that of the distributions
-displayed in Figs.~\ref{fig5} and \ref{fig6}. Unlike the distributions
+displayed in Figs.~\ref{fig5} and \ref{fig6}.
+{\bf (KK: I'm not sure what this means.  Are they less cosine-like?
+  Or are the amplitudes or phase shifts larger than those for the other
+  TPs?)}
+Unlike the distributions
 related to $\epsilon_1$-$\epsilon_3$, those arising from $\epsilon_4$
-exhibit small changes in their shapes for all the considered
+exhibit small changes in their shapes {\bf (KK: I don't think I understand
+  this, since we said that the range of variation was larger in the last
+  sentence.  I think I'm missing something :) )} for all the considered
 hypotheses and for this reason we have not included the corresponding
 plots here. However, the larger range of variation of the $\epsilon_4$
-distributions leads to higher values for the asymmetry (as can be sees
+distributions leads to higher values for the asymmetry (as can be seen
 from Tables \ref{table1} and \ref{table2}) even when the changes in
-the respective shapes are smaller than in the case of the
+the respective shapes are smaller {\bf (KK: I don't understand what
+  this means.)} than in the case of the
 distributions described by Eq.~(\ref{eq27}).  \par

### 2016-03-03 Paper_ttbarH_Draft.tex
KK edits to Sec. IIIC

@@
 \label{sec3.3}
-We turn now to consider the last type of observables constructed from
-the TPs that are sensitive to $\kpt$, the mean value. Given a certain
+We turn now to consider the last type of observable that we will
+construct from the TPs, the mean value. As was the case for the
+observables considered in Secs.~\ref{sec3.1} and \ref{sec3.2},
+the mean value is sensitive to $\kpt$.  Given a certain
 TP, we define its mean value in the following manner,
@@
 %
-where $\Phi$ is the Lorentz invariant phase space corresponding to the
+{\bf (KK: PRD might change these to [\ldots].)}
+where $\Phi$ is the Lorentz-invariant phase space corresponding to the
 final state
 $b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H$. From
-Eq.~(\ref{eq20}) we see that only the terms linear in $\kp$ and $\kpt$
-will contribute to the mean value, so that we expect this observable
-to be sensitive not only to the value but also to the relative sign of
-the couplings.\par The results obtained for the TPs $\epsilon_1=
+Eq.~(\ref{eq20}) we see that only the terms linear in (both) $\kp$ and $\kpt$
+will contribute to the mean value.  Thus, we expect this observable
+to be sensitive not only to the magnitude of $\kp\kpt$,
+but also to the relative sign of
+the couplings.\par
+
+The results obtained for the TPs $\epsilon_1=
 \epsilon(t,\tbar,n_t,n_{\tbar})$, $\epsilon_2=
@@
 =\epsilon(Q,t,n_t,n_{\tbar})$ introduced in Sec.~\ref{sec2} are
-displayed in Table \ref{table5}, where we list the deviation of the
-mean values from the SM case ($\kpt = 0$) in terms of the
-corresponding statistical uncertainty of the estimator of $\langle
-\epsilon \rangle$, $\bar{\epsilon}$.
+displayed in Table~\ref{table5}.  For each TP we list the 
+mean value divided by the
+corresponding statistical uncertainty.
+{\bf (KK: I simplified this sentence and
+  removed the language about the estimator -- we can
+  certainly put it back in, but to be consistent, wouldn't we
+  need to say $\bar{\epsilon}/\sigma_{\bar{\epsilon}}$?}
+%A deviation  of the estimator of $\langle
+%\epsilon \rangle$, $\bar{\epsilon}$.
+We see that the three observables are capable of distinguishing the SM
+case from both $\mathrm{CP}$-mixed cases. Furthermore,
+two $\mathrm{CP}$-mixed cases
+are clearly disentangled, since the the observables are
+sensitive to the sign of $\kpt$. The observables $\langle \epsilon_2
+\rangle$ and $\langle \epsilon_3 \rangle$ appear to be slightly more
+sensitive than $\langle \epsilon_1 \rangle$. On the other hand, the
+mean value for the combination $\epsilon_4$ introduced in
+Sec.~\ref{sec3.1} gives slightly smaller values than those listed in
+Table \ref{table5}, yielding $-4.32$, $1.11$ and $7.23$ for the cases
+$(\kp=1,\kpt=-1,0,1)$, respectively. As with the asymmetry, the
+purely $\mathrm{CP}$-even and purely $\mathrm{CP}$-odd cases cannot be
+distinguished by the mean value, since it is linear in both $\kp$ and
+$\kpt$ (see Eqs.~(\ref{eq20}) and (\ref{eq28})). Comparing the results
+in Table~\ref{table5} with
+the results presented in Sec.~\ref{sec3.1}, we can conclude that
+the sensitivity to the NP contribution is smaller for the mean values
+of the TPs under consideration
+than for the corresponding asymmetries.
+
 \renewcommand{\arraystretch}{1.6}
@@
 \caption{Mean values obtained for the TPs $\epsilon_{1,2,3}$ for the
-  SM case and two $\mathrm{CP}$-mixed cases with opposite sign in the
-  pseudoscalar coupling. The values are obtained by using $10^5$
+  SM case and two $\mathrm{CP}$-mixed cases.
+  The values are obtained using a sample of $10^5$
   simulated events.}
@@
 \end{table}
-We see that the three observables are capable of disinguishing the SM
-case from both $\mathrm{CP}$-mixed cases. Further, the observables are
-sensitive to the sign of $\kpt$ and the two $\mathrm{CP}$-mixed cases
-are also clearly disentangled. The observables $\langle \epsilon_2
-\rangle$ and $\langle \epsilon_3 \rangle$ appear to be slightly more
-sensitive than $\langle \epsilon_1 \rangle$. On the other hand, the
-mean value for the combination $\epsilon_4$ introduced in
-Sec.~\ref{sec3.1} gives slightly smaller values than those listed in
-Table \ref{table5}, with $-4.32, 1.11$ and $7.23$ for the cases
-$(\kp=1,\kpt=-1,0,1)$ respectively. As with the asymmetry, the
-hypotheses $\mathrm{CP}$-even and $\mathrm{CP}$-odd cannot be
-distinguished by the mean value that is also linear in both $\kp$ and
-$\kpt$ (see Eqs.~(\ref{eq20}) and (\ref{eq28})). By taking into
-account the results given in Sec.~\ref{sec3.1}, we can conclude that
-the sensitivity to the NP contribution is smaller for the mean values
-than for the asymmetries of the TPs under consideration.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

### 2016-03-03 Paper_ttbarH_Draft.tex
KK edit -- part way through Sec. IV

@@
 So far we have considered three TPs involving the momenta $t,\tbar$
-and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ given in
-Eqs.~(\ref{eq3})-(\ref{eq4}). In fact, we have described the general
+and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ [defined in
+Eqs.~(\ref{eq3})-(\ref{eq4}].  Furthermore, we have described the general
 form of the differential cross-section in terms of these vectors in
-Eq.~(\ref{eq20}). Here, we will take into account another
+Eq.~(\ref{eq20}). In this section we consider other
 possibilities for the choice of the vectors from which the
@@
 \label{eq30}
-\TPb = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,\tbar,\ell^-\!,\ell^+)+\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(H,\tbar,t,\ell^-\!)\right)
+\TPb = \frac{m^2_t}{(t\cdot \ell^+)(\tbar\cdot \ell^-)}\left(\epsilon(t,\tbar,\ell^-\!,\ell^+)+\epsilon(H,\tbar,\ell^-\!,\ell^+)+\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(H,\tbar,t,\ell^-\!)\right) \,,
 \eeq
@@
 can also be tested by means of the observables introduced in
-Secs.~\ref{sec3.1}-\ref{sec3.3}. In the first place, we have found
-that TPs not including both lepton and anti-lepton momenta present a
-negligible sensitivity, and then we will concentrate here on the
+Secs.~\ref{sec3.1}-\ref{sec3.3}.  Now, we have found
+that TPs not including both the lepton and anti-lepton momenta yield
+negligible sensitivity to the value of $\kpt$.  For this reason,
+we concentrate here on the
 results obtained for the remaining TPs,
-$\epsilon_5\equiv\epsilon(t,\tbar,\ell^-\!,\ell^+),
-\epsilon_6\equiv\epsilon(H,t,\ell^-\!,\ell^+)$ and $\epsilon_7\equiv
-\epsilon(H,\tbar,\ell^-\!,\ell^+)$. The Tables \ref{table6} and
-\ref{table7} summarize the results for these TPs.
+%
+\beq
+\label{eqa5}
+\epsilon_5\equiv\epsilon(t,\tbar,\ell^-\!,\ell^+) \,,
+\vspace*{1mm}
+\eeq
+%
+\beq
+\label{eqa6}
+\epsilon_6\equiv\epsilon(H,t,\ell^-\!,\ell^+) \,,
+\vspace*{1mm}
+\eeq
+%
+\beq
+\label{eqa7}
+\epsilon_7\equiv\epsilon(H,\tbar,\ell^-\!,\ell^+) \,.
+\vspace*{1mm}
+\eeq
+%
+    {\bf (KK: Should we clarify somehow that $\epsilon_{4,5,6,7}$ are not the same as
+      $\epsilon_{4,5,6,7}$ in Eq.~(20)?  That seems like a potential source of confusion.)}
+
 \renewcommand{\arraystretch}{1.6}
@@
 %
+
+Tables~\ref{table6} and
+\ref{table7} summarize the results for the TPs $\epsilon_{5,6,7}$.
+    {\bf (KK: Should we interchange the two tables?  In the previous section
+      we considered asymmetries first, then mean values.  Seems like it might
+      flow better to follow that same order here.)}
 We see that the TP $\epsilon_5$ gives rise to asymmetries and mean
@@
 and $\epsilon_7$. This is in contrast to the TPs $\epsilon_{1,2,3}$,
-for which the asymmetries and mean values are comparable (see Tables
+for which the asymmetries and mean values are comparable for the TPs
+(see Tables
 \ref{table1} and \ref{table5}). We also note that the asymmetry for
-$\epsilon_5$ is exactly the same as for $\epsilon_1$ as was expected
+$\epsilon_5$ is exactly the same as for $\epsilon_1$, as was expected
 from Eq.~(\ref{eq29}) since the proportionality factor relating them
 is positive definite. Regarding the mean values, we see by comparing
-Tables \ref{table5} and \ref{table6} that the TPs $\epsilon_{1,2,3}$
+Tables~\ref{table5} and \ref{table6} that the TPs $\epsilon_{1,2,3}$
 appear to have a higher sensitivity to the pseudoscalar coupling than

### 2016-03-03 Paper_ttbarH_Draft.tex
KK edits through the end of Sec. IV

@@
 can also be tested by means of the observables introduced in
-Secs.~\ref{sec3.1}-\ref{sec3.3}.  Now, we have found
-that TPs not including both the lepton and anti-lepton momenta yield
+Secs.~\ref{sec3.1}-\ref{sec3.3}.  We have found
+that TPs that do not include both the lepton and anti-lepton momenta yield
 negligible sensitivity to the value of $\kpt$.  For this reason,
@@
 \ref{table1} and \ref{table5}). We also note that the asymmetry for
-$\epsilon_5$ is exactly the same as for $\epsilon_1$, as was expected
-from Eq.~(\ref{eq29}) since the proportionality factor relating them
+$\epsilon_5$ is exactly the same as for $\epsilon_1$, as is expected
+from Eq.~(\ref{eq29}), since the proportionality factor relating them
 is positive definite. Regarding the mean values, we see by comparing
@@
 appear to have a higher sensitivity to the pseudoscalar coupling than
-$\epsilon_{5,6,7}$.  \par It is important to mention that in the
+$\epsilon_{5,6,7}$.  \par
+
+It is important to mention that in the
 $t\tbar$ rest frame the sign of the TP $\epsilon_5$ is defined through
-the angle $\Delta\phi_{\ell^-\ell^+}$ (recall the discussion on
-Eq.~(\ref{eq28})), which is the angular difference between the
-projections of the leptons momenta onto the plane perpendicular to
+the angle $\Delta\phi_{\ell^-\ell^+}$ [see the discussion following
+  Eq.~(\ref{eq28}) {\bf (KK: should this be Eq~(\ref{eq25})?)}],
+which is the angular difference between the
+projections of the leptons' momenta onto the plane perpendicular to
 $\vec{\tbar}$. By a similar argument to that discussed at the
 beginning of Sec.~\ref{sec3.2}, we can construct an associated angular
-distribution that, being constrained by the $\mathcal{A}(\epsilon_5)$,
-will be also sensitive to the sign of the pseudoscalar coupling. This
-angular variable is nothing but that proposed in \cite{Ellis} as a
+distribution [see Eq.~(\ref{eq26})] that
+will be sensitive to the sign of the pseudoscalar coupling. This
+angular variable is the same as that proposed in Ref.~\cite{Ellis} as a
 useful $\mathrm{CP}$-odd observable. Moreover, it is shown in
-\cite{Ellis} that this angular distribution follows the functional
+Ref.~\cite{Ellis} that the corresponding
+angular distribution follows the functional
 form given in Eq.~(\ref{eq27}). Due to the fact that this distribution
-is constrained by $\mathcal{A}(\epsilon_5)$ which is equal to
+is constrained by the asymmetry $\mathcal{A}(\epsilon_5)$
+[via Eq.~(\ref{eq26})], {\bf (KK: correct, I think\ldots?)}
+which in turn is equal to
 $\mathcal{A}(\epsilon_1)$ and smaller than
@@
 obtained for different values of $\kpt$ are expected to be of the same
-order than those exhibited by the $\Delta\phi_1(n_t,n_{\tbar})$
-distribution and somewhat smaller than those observed in the
-$\Delta\phi_2(n_t,n_{\tbar})$ distribution.  \par In analogy to the
+order as those exhibited by the $\Delta\phi_1(n_t,n_{\tbar})$
+distribution and somewhat smaller than those obtained for the
+$\Delta\phi_2(n_t,n_{\tbar})$ distribution.
+{\bf (KK: A few comments\ldots (i) From Table I, it doesn't seem like
+  $\mathcal{A}(\epsilon_1)<\mathcal{A}(\epsilon_{3})$; (ii) I'm not
+  sure about this argument
+  regarding $\delta$ -- wouldn't the value of $\mathcal{A}$ depend
+  on both the phase shift and the amplitude of the cosine?  For example,
+  assuming
+  the functional form from the fit, it depends on $a_1\sin(\delta)$; but
+  that expression is not exact; (iii) I wonder if it might be best to
+  drop the connection to $\epsilon_2$, which seems a bit more tenuous,
+  and just make the comparison with $\epsilon_1$ and its $\delta$.  I suggest
+  the sentence that follows\ldots.)}
+Since this distribution
+is constrained by the asymmetry $\mathcal{A}(\epsilon_5)$
+[via Eq.~(\ref{eq26})],
+which in turn is equal to
+$\mathcal{A}(\epsilon_1)$, the corresponding shifts ($\delta$)
+obtained for different values of $\kpt$ are expected to be of the same
+order as those exhibited by the $\Delta\phi_1(n_t,n_{\tbar})$
+distribution.
+
+\par
+
+In analogy with the
 combination of TPs considered in Sec.~\ref{sec3}, we have found a
@@
 \times \vec{\ell}^-)$, where $M_{t\tbar H}$ is the invariant mass of
-the system $t\tbar H$. Hence, in this reference frame the sign of the
-combination $\epsilon_8$ is set by the quantity
+the $t\tbar H$ system. Hence, in the $t\tbar H$ rest frame the sign of 
+$\epsilon_8$ is determined by the quantity
 $(\vec{t}-\vec{\tbar})\cdot (\vec{\ell}^+\! \times
-\vec{\ell}^-)$. Taking into account Eqs.~(\ref{eq24}) and (\ref{eq32})
-along with the definition $Q=(t+\tbar+H)/2$, we see that the only
+\vec{\ell}^-)$. Comparing Eqs.~(\ref{eq24}) and (\ref{eq32})
+and noting that $Q=(t+\tbar+H)/2$, we see that the only
 relevant difference between $\epsilon_4$ and $\epsilon_8$ is that in
 the latter the spin vectors $n_t$ and $n_{\tbar}$ have been replaced
-by the momenta of the leptons $\ell^+$ and $\ell^-$ respectively. The
+by the momenta of the leptons $\ell^+$ and $\ell^-$, respectively. The
 values obtained for $\mathcal{A}(\epsilon_8)$ are shown in Table
@@
 instead of the spin vectors produces a decrease in the sensitivity of
-the asymmetry. \par From the TPs $\epsilon_5$-$\epsilon_7$ one can
-derive various angular distributions in the same manner we have
-discussed in Sec.~\ref{sec3.2} for $\epsilon_1$-$\epsilon_3$. Of
-course, in this case the corresponding angle will be defined in terms
-of the momenta of the leptons instead of using the spin vectors. These
-distributions have the same behaviour than those derived from
-$\epsilon_1$-$\epsilon_3$, but only the shift obtained in the case of
-$\epsilon_5$ is compatible to the values given in Tables for
-$\epsilon_1$-$\epsilon_3$. The shifts resulting from the fit of the
-distributions related to $\epsilon_6$ and $\epsilon_7$ are
-smaller. Taking into account these facts we do not give further
+the asymmetry. 
+{\bf (KK: I don't know that we should separate $\epsilon_2$ from
+  $\epsilon_{1,3}$ in this way.  They basically agree within their
+  uncertainties.  If we used another Monte Carlo data set, we might
+  get a different ordering.  I would suggest the following rewording\ldots.)}
+Compared to the TPs $\epsilon_1$-$\epsilon_3$ and
+$\epsilon_5$-$\epsilon_7$ (see Tables \ref{table1} and \ref{table7}),
+the asymmetry for $\epsilon_8$ has a comparable or slightly higher
+sensitivity for resolving the $\mathrm{CP}$-mixed cases.
+Comparing with $\mathcal{A}(\epsilon_4)$, however,
+we see that using the momenta of the leptons (in $\epsilon_8$)
+instead of the spin vectors produces a decrease in the sensitivity of
+the asymmetry.
+
+Having defined the TPs $\epsilon_5$-$\epsilon_7$, one can
+proceed, as in Sec.~\ref{sec3.2}, to define corresponding
+angular distributions.  Of
+course, in this case the corresponding angles will be defined in terms
+of the momenta of the leptons instead of using the spin vectors. The
+angular distributions based on $\epsilon_5$-$\epsilon_7$
+have the same overall behaviour as those derived from
+$\epsilon_1$-$\epsilon_3$.  Using Eq.~(\ref{eq27})
+to fit the distributions and comparing to the results obtained for
+$\epsilon_1$-$\epsilon_3$, we find that the phase shifts ($\delta$)
+are comparable for the $\epsilon_5$ angular distribution, but are
+smaller for the
+$\epsilon_6$ and $\epsilon_7$ distributions.  {\bf (KK: rewording OK/correct?)}
+Taking into account these facts we do not give further
 details of the angular distributions for the TPs discussed in this
-section.\par The mean value of $\epsilon_8$ for the hypotheses under
-consideration is comparable with the values listed in Table
+section.
+{\bf (KK: I would suggest deleting this last sentence.)}
+\par
+
+The mean values of $\epsilon_8$ for the scenarios under
+consideration are comparable with the values listed in Table
 \ref{table6} for $\epsilon_5$. Concerning the associated angular
-distributions, their range of variation is larger than in the case of
+distributions, their range of variation {\bf (KK: I'm not sure what
+  this means)} is larger than in the case of
 the distributions related to $\epsilon_5$-$\epsilon_7$ but exhibit
-smaller changes in their shapes for the different hypothesis and for
+smaller changes in their shapes for the different scenarios and for
 this reason we do not include here the corresponding plots.
+{\bf (KK: might need to reword this a bit after clarifying what 
+  range of variation means.)}
 \begin{table}[H]

### 2016-03-03 Paper_ttbarH_Draft.tex
Some changes to SecIII and IV based on Ken's changes

--- 2016-03-03 Paper_ttbarH_Draft.tex
@@
 To the extent that the above expression is exact, we note that
-Eq.~(\ref{eq26}) {\bf (KK: corrected the equation number; please check\ldots )}
+Eq.~(\ref{eq26}) 
 gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
@@
   we do not include the corresponding results for the $\epsilon_3$ distribution
-  here. {\bf (KK: OK to move this to a footnote?)}}  However, the quality of the fits is
+  here.}  However, the quality of the fits in the four considered scenarios is
 not very good, particularly for $\epsilon_1$.  The
-$\chi^2/\mathrm{d.o.f}$ for the fits in this case are in the range
+$\chi^2/\mathrm{d.o.f}$ for the fits corresponding to $\epsilon_1$ are in the range
 $1.69$-$3.86$, while for $\epsilon_2$ they are in the range $0.53$-$1.16$.
-{\bf (KK: Did we do 4 fits for each $\epsilon$?  Or only 2?  If only 2, maybe
-  saying ``in the range'' is not quite correct, since the two
-  data points are simply the endpoints of the ``range''.  If
-  the range includes all 4 fits for each, maybe we could state that
-  explicitly, since the preceding sentences are only discussing the two
-  mixed-CP scenarios.)}
 The deviation from the functional
@@
 \label{eq28}
-\langle \epsilon \rangle = \frac{\int\epsilon\, \{d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi\}\,d\Phi}{\int \{d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi\}\,d\Phi},
-\eeq
-%
-{\bf (KK: PRD might change these to [\ldots].)}
+\langle \epsilon \rangle = \frac{\int\epsilon\, [d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi]\,d\Phi}{\int [d\sigma (pp\to b\,\ell^+\nu_{\ell}\,\bbar\,\ell^-\bar{\nu}_{\ell}H)/ d\Phi]\,d\Phi},
+\eeq
+%
 where $\Phi$ is the Lorentz-invariant phase space corresponding to the
@@
 we concentrate here on the
-results obtained for the remaining TPs,
+results obtained for the remaining TPs,\footnote{These TPs should not be confused with those introduced in Eq.~(\ref{eq20}).}
 %
@@
 %
-    {\bf (KK: Should we clarify somehow that $\epsilon_{4,5,6,7}$ are not the same as
-      $\epsilon_{4,5,6,7}$ in Eq.~(20)?  That seems like a potential source of confusion.)}
+
+\renewcommand{\arraystretch}{1.4}
+\begin{table}[H]
+\caption{Asymmetries for the TPs $\epsilon_{5,6,7}$ for the SM case
+  and the two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm
+  1$. The values correspond to $10^5$ simulated events.}
+\label{table7}
+\begin{center}
+\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
+%\begin{tabular}{|c|r||r|c||r|c||r|c|}
+\hhline{|========|}
+%\hhline{|--------|}
+$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_5)$~~&$\mathcal{A}(\epsilon_5)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_6)$~~&$\mathcal{A}(\epsilon_6)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_7)$~~&$\mathcal{A}(\epsilon_7)/\sigma_{\mathcal{A}}$  \\
+\hhline{|========|} 
+%\hhline{|--------|}
+$1$ & $-1$~~~ & $0.0315$~ & $10.0$~ & $-0.0134$~~~ & $-4.2$~~~ & $0.0111$~ & $3.5$~\\[0.6mm]
+\hline
+$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $-0.0011$~~~ & $-0.3$~~~ & $0.0009$~& $0.3$~\\[0.6mm]
+\hline
+$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $0.0143$~ & $4.5$~ & $-0.0137$~~~ & $\,-4.3$~~~  \\[0.6mm]
+\hhline{|========|}
+%\hhline{|--------|}
+\end{tabular}
+\end{center} 
+\end{table}
 
@@
 \end{table}
-\renewcommand{\arraystretch}{1.4}
-\begin{table}[H]
-\caption{Asymmetries for the TPs $\epsilon_{5,6,7}$ for the SM case
-  and the two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm
-  1$. The values correspond to $10^5$ simulated events.}
-\label{table7}
-\begin{center}
-\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
-%\begin{tabular}{|c|r||r|c||r|c||r|c|}
-\hhline{|========|}
-%\hhline{|--------|}
-$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_5)$~~&$\mathcal{A}(\epsilon_5)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_6)$~~&$\mathcal{A}(\epsilon_6)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_7)$~~&$\mathcal{A}(\epsilon_7)/\sigma_{\mathcal{A}}$  \\
-\hhline{|========|} 
-%\hhline{|--------|}
-$1$ & $-1$~~~ & $0.0315$~ & $10.0$~ & $-0.0134$~~~ & $-4.2$~~~ & $0.0111$~ & $3.5$~\\[0.6mm]
-\hline
-$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $-0.0011$~~~ & $-0.3$~~~ & $0.0009$~& $0.3$~\\[0.6mm]
-\hline
-$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $0.0143$~ & $4.5$~ & $-0.0137$~~~ & $\,-4.3$~~~  \\[0.6mm]
-\hhline{|========|}
-%\hhline{|--------|}
-\end{tabular}
-\end{center} 
-\end{table}
 \par
@@
 
-Tables~\ref{table6} and
-\ref{table7} summarize the results for the TPs $\epsilon_{5,6,7}$.
-    {\bf (KK: Should we interchange the two tables?  In the previous section
-      we considered asymmetries first, then mean values.  Seems like it might
-      flow better to follow that same order here.)}
+Tables~\ref{table7} and
+\ref{table6} summarize the results for the TPs $\epsilon_{5,6,7}$.
 We see that the TP $\epsilon_5$ gives rise to asymmetries and mean

### 2016-03-03 Paper_ttbarH_Draft.tex
KK edits through Sec. V

--- 2016-03-03 Paper_ttbarH_Draft.tex
@@
 \label{sec5}
-All the observables discussed in the above sections involve the
-momenta of the top and anti-top quarks thus requiring the full
+The observables discussed in the preceding sections all involve the
+momenta of the top and/or anti-top quarks and thus require the full
 reconstruction of the kinematics of the individual $t$ and $\tbar$
 systems in order to be measured. Although challenging due to the
-presence of two neutrinos in the final state, this can be in principle
-done by applying a kinematic reconstruction method such that the
-neutrino weighting technique \cite{atlasconf,atlascharge}. Another
-possibility is to define observables that are not dependent on the $t$
-and $\tbar$ momenta but make use of the quarks $b$ and $\bbar$. In
-order to construct such observables we will modify here the most
-sensitive observables studied in Secs.~\ref{table3} and \ref{sec4},
-namely the combinations $\epsilon_4$ and $\epsilon_8$
-respectively. Let us first consider the combination $\epsilon_8$
-defined in Eq.~(\ref{eq32}) and replace the top and antitop momenta by
-the bottom and antibottom momenta respectively. Thus, we define
+presence of the two neutrinos in the final state, this can in principle be
+done by applying a kinematic reconstruction method such as the
+neutrino weighting technique~\cite{atlasconf,atlascharge}. Another
+possibility is to define observables that do not depend on the $t$
+and $\tbar$ momenta but instead make use of the momenta of the
+$b$ and $\bbar$ quarks to which the $t$ and $\tbar$ decay. In
+order to construct such observables we will take as our starting
+point the most
+sensitive observables studied in Secs.~\ref{sec3} and \ref{sec4},
+{\bf (KK: note that I changed the reference from table3 to sec3.)}
+namely those associated with the TPs $\epsilon_4$ and $\epsilon_8$,
+respectively.
+
+Let us first consider the TP combination $\epsilon_8$, which is
+defined in Eq.~(\ref{eq32}).  Replacing the momenta of the
+$t$ and $\tbar$ quarks by the momenta of the $b$ and $\bbar$ quarks,
+respectively, we have a new TP,
 %
@@
 %
-Note that now the sign of the TP $\epsilon_9$ is set by the sign of
+Note that the sign of $\epsilon_9$ is determined by the sign of
 the quantity $(\vec{b}-\vec{\bbar})\cdot(\vec{\ell}^+\!\times
-\vec{\ell}^-)$ in the $b\bbar H$ rest frame. This quantity is in fact
-used in \cite{Guadagnoli} but in the lab frame in order to define a
+\vec{\ell}^-)$ in the $b\bbar H$ rest frame. This combination
+of three vectors (determined in the lab frame instead
+of the $b\bbar H$ rest frame) is
+used in Ref.~\cite{Guadagnoli} to define a
 $\mathrm{CP}$-odd observable that only depends on lab frame
 variables. The values of the asymmetry for $\epsilon_9$ are listed in
-Table \ref{table9}. By comparing Tables \ref{table8} and \ref{table9}
-we see that the use of the $b,\bbar$ instead of $t,\tbar$ leads to a
-decrese in the sensitivity of the asymmetry by $\sim 5\sigma$ for
-$\kp=1,\kpt=\pm 1$. However, the observable is still capable of
-discriminating not only between the two $\mathrm{CP}$-mixed hypotheses
+Table~\ref{table9}. Comparing Tables~\ref{table8} and \ref{table9}
+we see that the use of the $b$ and $\bbar$ momenta
+instead of the $t$ and $\tbar$ momenta leads to a
+decrease in the sensitivity of the asymmetry by $\sim 5\sigma$ for
+$\kp=1,\kpt=\pm 1$. Nevertheless, the observable can still
+discriminate not only between the two $\mathrm{CP}$-mixed scenarios
 but also between these and the SM case.
 %\newpage
-We proceed now in a similar way with the combination $\epsilon_4$. By
-using Eq.~(\ref{eq24}) along with the definitions of the spin vectors
-in Eqs.~(\ref{eq3})-(\ref{eq4}), we can write
-%
-\beq
-\label{eq34}
-\epsilon_4 = \frac{m^2_t}{(t\cdot\ell^+)\cdot(\tbar\cdot\ell^-)}\,\epsilon(Q,t-\tbar,\ell^-,\ell^+)+\frac{1}{(t\cdot\ell^+)}\,\epsilon(Q,t,\ell^+,\tbar)-\frac{1}{(\tbar\cdot \ell^-)}\,\epsilon(Q,\tbar,t,\ell^-).
-\eeq
-%
-Since the asymmetry is not changed by an overall positive definite
-factor, we will concentrate on the following combination arising from
-the expression in Eq.~(\ref{eq34}),
-%
-\beq
-\label{eq35}
-\epsilon(Q,t-\tbar,\ell^-,\ell^+)+\frac{(\tbar\cdot \ell^-)}{m^2_t}\epsilon(Q,t,\ell^+,\tbar)-\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(Q,\tbar,t,\ell^-),
-\eeq
-%
-\begin{table}[H]
+
+%
+\begin{table}[th]
 \caption{Asymmetry for the TP $\epsilon_{9}$ for the SM case and the
   two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
-  values are obtained with $10^5$ simulated events.}
+  values are obtained with $10^5$ simulated events.
+  {\bf (KK: I repositioned the table in the file, please double check to make
+  sure I didn't mess anything up :)}}
 \label{table9}
@@
 \end{table}
-\noindent
-%
-and instead of replacing $t$ and $\tbar$ directly by $b$ and $\bbar$,
-we use their visible parts, namely $b+\ell^+$ and $\bbar +\ell^-$
+%
+
+We proceed in a similar manner with the TP $\epsilon_4$. Starting from
+Eq.~(\ref{eq24}) and using the definitions of the spin vectors
+in Eqs.~(\ref{eq3})-(\ref{eq4}), we have
+%
+\beq
+\label{eq34}
+\epsilon_4 = \frac{m^2_t}{(t\cdot\ell^+)\cdot(\tbar\cdot\ell^-)}\,\epsilon(Q,t-\tbar,\ell^-,\ell^+)+\frac{1}{(t\cdot\ell^+)}\,\epsilon(Q,t,\ell^+,\tbar)-\frac{1}{(\tbar\cdot \ell^-)}\,\epsilon(Q,\tbar,t,\ell^-).
+\eeq
+%
+Since the asymmetry is not changed by the presence
+of an overall positive definite multiplicative
+factor, let us concentrate instead on the following combination
+of TPs,
+%
+\beq
+\label{eq35}
+\epsilon(Q,t-\tbar,\ell^-,\ell^+)+\frac{(\tbar\cdot \ell^-)}{m^2_t}\epsilon(Q,t,\ell^+,\tbar)-\frac{(t\cdot\ell^+)}{m^2_t}\epsilon(Q,\tbar,t,\ell^-).
+\eeq
+Instead of replacing $t$ and $\tbar$ directly by $b$ and $\bbar$,
+we use the visible contributions, namely $b+\ell^+$ and $\bbar +\ell^-$,
 respectively. This results in the following definition
@@
 where $\tilde{Q}\equiv (b+\ell^+\!+\bbar +\ell^-)/2$ stands for the
-visible part of $Q$, $c_{b\bbar}=(1-w_1)\,b-(1-w_2)\,\bbar$ and the
+visible part of $Q$, $c_{b\bbar}=(1-w_1)\,b-(1-w_2)\,\bbar$, and the
 weights $w_{1,2}$ are given by $(\bbar\cdot \ell^-)/m^2_t $ and
-$(b\cdot \ell^+)/m^2_t$ respectively. Also, the contribution
+$(b\cdot \ell^+)/m^2_t$, respectively. Also, the contribution
 $m^2_{\ell}/m^2_t$ has been neglected both in $w_1$ and in $w_2$. Note
@@
 $\epsilon_9 /2$ and $\mathcal{A}(\epsilon_{10})$ becomes equal to
-$\mathcal{A}(\epsilon_9)$. The results obatined for the asymmetry of
+$\mathcal{A}(\epsilon_9)$. The results obtained for the asymmetry of
 $\epsilon_{10}$ are given in Table \ref{table10}. By comparing Tables
@@
 observable for discriminating the $\mathrm{CP}$ nature of the Higgs
-boson, with the corresponding asymmetry having a sensitivity even
-higher than that of $\epsilon_9$, as can be checked by taking into
-account Tables \ref{table9} and \ref{table10}. More precisely, the
-separation between the $\mathrm{CP}$-mixed hypotheses is enhanced by
-about $3\sigma$. This improvement in the asymmetry of $\epsilon_{10}$
-with respect to $\epsilon_9$ may be due to two facts. In the first
+boson, with the corresponding asymmetry having a sensitivity that is
+higher than that of $\epsilon_9$.
+
+Comparing
+Tables~\ref{table9} and \ref{table10}, we see that the
+separation between the $\mathrm{CP}$-mixed scenarios is enhanced by
+about $3\sigma$ for $\mathcal{A}(\epsilon_{10})$ compared
+  to $\mathcal{A}(\epsilon_{9})$.
+    This improvement in the asymmetry may be due to two facts. In the first
 place, as was pointed out in Sec.~\ref{sec4} when comparing the TPs
 $\epsilon_4$ and $\epsilon_8$, the asymmetry appears to be higher when
-the spin vectors are used instead of the lepton momenta and we see
+the spin vectors are used instead of the lepton momenta.  We see
 from Eqs.~(\ref{eq33}) and (\ref{eq36}) that $\epsilon_{10}$, being
 obtained from $\epsilon_4$, contains the information on the spin
-vectors, as opposed to $\epsilon_9$ that depends directly on the
+vectors; by way of contrast, $\epsilon_9$ depends directly on the
 lepton momenta because it is derived from $\epsilon_8$. In the second
-place, in order to obtain $\epsilon_{10}$ we have replaced in the
-expression for $\epsilon_4$ the top and antitop momenta by their
-visible part, while in the case of $\epsilon_9$ the bottom and
+place, in order to obtain $\epsilon_{10}$, we have replaced
+the top and antitop momenta by their 
+visible parts, while in the case of $\epsilon_9$ the bottom and
 antibottom momenta have been used.
-\begin{table}[H]
+
+%
+\begin{table}[th]
 \caption{Asymmetry for the TP $\epsilon_{10}$ for the SM case and the
@@
 \end{table}
-\par
-%
-By using our set of simulated events we have also tested, for
-comparison purposes, the asymmetry of the lab frame observable given
-in \cite{Guadagnoli}. We have obtained that this observable appears to
+%
+
+For comparison purposes, we have also used our simulated events
+to test the asymmetry corresponding to the lab frame observable given
+in Ref.~\cite{Guadagnoli}. {\bf (KK: Is this lab frame observable
+  just a TP, like we have used?  It seems strange to talk about an
+  asymmetry associated with an observable, when normally an asymmetry
+  is itself considered to be an observable.  I'm wondering if we are
+  considering an asymmetry associated with a TP, or if we are actually
+  just looking at whatever observable they have defined\ldots.  Sorry for
+  my confusion on this!)}  We have found that this observable
+{\bf (KK: ``asymmetry''?)}
+appears to
 be slightly less sensitive than the combination $\epsilon_{10}$,
-giving rise to a separation between the $\mathrm{CP}$-mixed hypotheses
-smaller by about $1.4\sigma$.
+{\bf (KK: ``$\mathcal{A}(\epsilon_{10})$''?)}
+giving rise to a separation between the $\mathrm{CP}$-mixed scenarios
+that is smaller by about $1.4\sigma$.
 \section{Experimental Feasibility}

### 2016-03-03 Paper_ttbarH_Draft.tex

--- 2016-03-03 Paper_ttbarH_Draft.tex
@@
 corresponding statistical uncertainty.
-{\bf (KK: I simplified this sentence and
-  removed the language about the estimator -- we can
-  certainly put it back in, but to be consistent, wouldn't we
-  need to say $\bar{\epsilon}/\sigma_{\bar{\epsilon}}$?}
 %A deviation  of the estimator of $\langle
@@
 the angle $\Delta\phi_{\ell^-\ell^+}$ [see the discussion following
-  Eq.~(\ref{eq28}) {\bf (KK: should this be Eq~(\ref{eq25})?)}],
+  Eq.~(\ref{eq25})],
 which is the angular difference between the
@@
 angular distribution follows the functional
-form given in Eq.~(\ref{eq27}). Due to the fact that this distribution
-is constrained by the asymmetry $\mathcal{A}(\epsilon_5)$
-[via Eq.~(\ref{eq26})], {\bf (KK: correct, I think\ldots?)}
-which in turn is equal to
-$\mathcal{A}(\epsilon_1)$ and smaller than
-$\mathcal{A}(\epsilon_{2,3})$, the corresponding shifts ($\delta$)
+form given in Eq.~(\ref{eq27}). The ascociated shifts ($\delta$)
 obtained for different values of $\kpt$ are expected to be of the same
 order as those exhibited by the $\Delta\phi_1(n_t,n_{\tbar})$
-distribution and somewhat smaller than those obtained for the
-$\Delta\phi_2(n_t,n_{\tbar})$ distribution.
-{\bf (KK: A few comments\ldots (i) From Table I, it doesn't seem like
-  $\mathcal{A}(\epsilon_1)<\mathcal{A}(\epsilon_{3})$; (ii) I'm not
-  sure about this argument
-  regarding $\delta$ -- wouldn't the value of $\mathcal{A}$ depend
-  on both the phase shift and the amplitude of the cosine?  For example,
-  assuming
-  the functional form from the fit, it depends on $a_1\sin(\delta)$; but
-  that expression is not exact; (iii) I wonder if it might be best to
-  drop the connection to $\epsilon_2$, which seems a bit more tenuous,
-  and just make the comparison with $\epsilon_1$ and its $\delta$.  I suggest
-  the sentence that follows\ldots.)}
-Since this distribution
+distribution since this distribution
 is constrained by the asymmetry $\mathcal{A}(\epsilon_5)$
@@
 which in turn is equal to
-$\mathcal{A}(\epsilon_1)$, the corresponding shifts ($\delta$)
-obtained for different values of $\kpt$ are expected to be of the same
-order as those exhibited by the $\Delta\phi_1(n_t,n_{\tbar})$
-distribution.
-
+$\mathcal{A}(\epsilon_1)$. Also, we note that $\mathcal{A}(\epsilon_5)$ is slightly smaller 
+than $\mathcal{A}(\epsilon_2)$,
+as can be seen from Table \ref{table1}. {\bf (N: We have followed your proposal but
+also added that the asymmetry for this TP, which is the one proposed by Ellis, is slightly less sensitive
+ than in the case of $\epsilon_2$. This is in order to emphasize that we tend to prefer the latter (even when
+ the improvement in the sensitivity is small in terms of the statistical uncertainty).) }
 \par
@@
 values obtained for $\mathcal{A}(\epsilon_8)$ are shown in Table
-\ref{table8}. Compared to the TPs $\epsilon_5$-$\epsilon_7$ and
-$\epsilon_1, \epsilon_3$ (see Tables \ref{table1} and \ref{table7}),
-the chosen combination exhibits a slightly higher sensitivity in the
-asymmetry for resolving the $\mathrm{CP}$-mixed cases. This is not
-true in the case of the TPs $\epsilon_2$ and $\epsilon_4$, for which
-the asymmetry is larger (see Tables \ref{table1}, \ref{table2} and
-\ref{table8}). In particular, the comparison between $\epsilon_4$ and
-$\epsilon_8$ indicates that the use of the momenta of the leptons
-instead of the spin vectors produces a decrease in the sensitivity of
-the asymmetry. 
-{\bf (KK: I don't know that we should separate $\epsilon_2$ from
-  $\epsilon_{1,3}$ in this way.  They basically agree within their
-  uncertainties.  If we used another Monte Carlo data set, we might
-  get a different ordering.  I would suggest the following rewording\ldots.)}
-Compared to the TPs $\epsilon_1$-$\epsilon_3$ and
+\ref{table8}. Compared to the TPs $\epsilon_1$-$\epsilon_3$ and
 $\epsilon_5$-$\epsilon_7$ (see Tables \ref{table1} and \ref{table7}),
@@
 instead of the spin vectors produces a decrease in the sensitivity of
-the asymmetry.
+the asymmetry (see Tables \ref{table2} and
+\ref{table8}).
 
@@
 smaller for the
-$\epsilon_6$ and $\epsilon_7$ distributions.  {\bf (KK: rewording OK/correct?)}
-Taking into account these facts we do not give further
-details of the angular distributions for the TPs discussed in this
-section.
-{\bf (KK: I would suggest deleting this last sentence.)}
+$\epsilon_6$ and $\epsilon_7$ distributions.  
 \par

### 2016-03-04 Paper_ttbarH_Draft.tex
KK edits up through Sec. VI

--- 2016-03-03 Paper_ttbarH_Draft.tex
@@
 that is smaller by about $1.4\sigma$.
+
+%
 \section{Experimental Feasibility}
@@
 %
-By considering the mild selection cuts introduced in Sec.~\ref{sec3},
-the SM cross section for $\ppprocess$, $\ell=e,\mu$ at
-$14\,\mathrm{TeV}$ is $\sim 15.3\,\mathrm{fb}$ and hence the number of
+
+In our numerical analyses so far we have used relatively large
+samples of events ($10^5$ events per sample)
+in order to clearly distinguish
+which observables would be most promising.  
+The number of events expected at the HL-LHC, however, is
+smaller than the number of events that we have used in our
+simulations.  In this section we reexamine
+the more promising observables, using sample sizes that are
+more attainable in the near future.  {\bf (KK: OK?)}
+
+Let us first make some estimates regarding the number of signal events
+expected at the HL-LHC.
+In Sec.~\ref{sec3} we introduced several mild selection cuts.
+Implementing these cuts, and assuming that the final state leptons
+could be either electrons or muons, {\bf (KK: factor of 4\ldots?)}
+the SM cross section for $\ppprocess$ at
+$14\,\mathrm{TeV}$ is $\sim 15.3\,\mathrm{fb}$; thus, the number of
 events expected within the context of the HL-LHC is $\sim
 15.3\,\mathrm{fb} \times 3000\,\mathrm{fb}^{-1} = 4.59\times
-10^4$. This number is expected to be even larger in the case of
-$\kp=1,\kpt\neq 0$ since the corresponding cross section is then
-higher than the SM one. By taking into account NLO corrections to the
-production process and considering a $K$-factor around $1.2$
-\cite{Dawson,Beenakker,Dittmaier}, the number of events can be raised
-up to $\sim 5.49 \times 10^4$. On the other hand, additional cuts as
-well as the efficiency related to the reconstruction of particles
-momenta will contribute to decrease this number. For instance, in
-order to obtain the asymmetry of $\epsilon_4$, the $t$ and $\tbar$
-momenta need to be reconstructed. This is challenging not only due to
-the presence of two neutrinos in the final state which escape the
-detector undetected but also because final state objects need to be
-asocciated with the respective parent quark \cite{atlasconf}. As was
-already mentioned in Sec.~\ref{sec5}, a possibility is to use the
+10^4$. This number is expected to be larger
+if $\kpt\neq 0$ (assuming $\kp=1$),
+since the corresponding cross section is
+larger than the SM cross section in this case.
+Taking into account NLO corrections (to the
+production process) via a $K$ factor of approximately
+$1.2$~\cite{Dawson,Beenakker,Dittmaier}, we find that
+the expected number of
+events increases to $\sim 5.49 \times 10^4$.
+{\bf (KK: should we use 5.5 at this point, since
+  the $K$ factor is only two sig figs?)}
+On the other hand, additional cuts, as
+well as a reduction in efficiency related to momentum reconstruction,
+will lead to a decrease in this number.  In
+order to measure the asymmetry $\mathcal{A}(\epsilon_4)$,
+for example, the $t$ and $\tbar$
+momenta need to be reconstructed. This is challenging, not only due to
+the presence of two neutrinos in the final state (which escape the
+detector undetected), but also because final state objects need to be
+associated with their respective parent quark~\cite{atlasconf}.
+{\bf (KK: maybe we can talk about this for a minute; I don't think I
+  understand it\ldots.  Wait -- do we mean that the quarks and leptons
+  need to be associated with either the top or antitop?  If so, maybe
+  we can reword this a bit.  Suggestion follows\ldots, maybe this
+  is too explicit now, because we also wanted it to refer to the Higgs.)}
+but also because the (visible) quarks and charged leptons in the final
+state need to be correctly associated with the corresponding
+parent particle (i.e., the top or antitop quark)~\cite{atlasconf}.
+As was
+already noted in Sec.~\ref{sec5}, one possibility is to use the
 neutrino weighting technique along with the kinematic equations
@@
 as well as from the energy-momentum conservation at each of the decay
-vertices involved in the process. Within the context of $t\tbar$ this
-procedure has been used, for instance, in order to obtain measurements
-of spin correlation \cite{atlasconf} and charge asymmetry
-\cite{atlascharge}. Also, events reconstructed with this technique has
-been used in \cite{dosSantos} for analyzing angular distributions that
+vertices involved in the process. {\bf (KK: Can we either simplify the
+  previous sentence or split it
+  into 2 or 3 sentences?  I'm not 100\% clear on which ideas go
+  together, so I wonder if one of you could give it a try.  My preference
+  would be to simplify it to something like ``\ldots weighting technique,
+  along with associated kinematic constraints'' or something like
+  that, and then give a reference.)}
+Within the context of $t\tbar$ production {\bf (KK: correct?)} this
+procedure has been used, for instance, to obtain 
+spin correlation~\cite{atlasconf} and charge
+asymmetry~\cite{atlascharge} measurements.
+Also, events reconstructed using this technique have
+been used in the analysis of angular distributions that
 are useful for discriminating the signal from the backgrounds in
-$t\tbar H (H\rightarrow b\bbar)$. In all these cases the corresponding
-efficiency in the reconstruction of the momenta is up to $\sim 80
-\%$.\par Based on the discussion given in the previous paragraph, we
-have simulated sets of $5\times 10^4, 1\times 10^4$ and $5\times 10^3$
-events and recalculated the most sensitive observable, namely
+$t\tbar H (H\rightarrow b\bbar)$~\cite{dosSantos}.
+{\bf (KK: do we need an initial state
+  on this process?)} In all these cases the corresponding
+efficiency in the reconstruction of the momenta is up to $\sim 80\%$.
+{\bf (KK: Does this mean that none of them exceeds 80\% or that
+  they all have an efficiency of at least 80\%?)}
+
+Given the discussion in the previous paragraph, we
+have generated sets of $5\times 10^4, 1\times 10^4$ and $5\times 10^3$
+events and have recalculated the most sensitive observable, 
 $\mathcal{A}(\epsilon_4)$, for each case. The results are displayed in
-Table \ref{table11}, where it can be seen that for a number of events
-close to that roughly estimated above within the context of the
-HL-LHC, the observable is still sensitive to $\kpt$ allowing to
-separate the $\mathrm{CP}$-mixed cases by $19\sigma$. As expected, the
-sensitivity worsen as the number of events is reduced, but even with
+Table \ref{table11}, where it can be seen that for $5\times 10^4$ events
+(which is close to our rough estimate above for the
+total number of signal events for the
+HL-LHC), {\bf (KK: stated correctly?)}
+the observable is still very sensitive to $\kpt$.
+In this case, the $\mathrm{CP}$-mixed scenarios are
+effectively separated by $19\sigma$. As expected, the
+sensitivity worsens as the number of events is reduced, but even with
 $5\times 10^3$ events the separation between the $\mathrm{CP}$-mixed
-hypotheses under consideration is around $6.5\sigma$. \par Although
-the combination $\epsilon_{10}$ discussed in Sec.~\ref{sec5} avoids
-the problem of reconstructing the top and antitop momenta, we have
-also considered the respective asymmetry obtained for more
-conservative numbers of events. In Table \ref{table12} we show the
-results for $\mathcal{A}(\epsilon_{10})$ when the number of events is
-reduced from $5\times 10^4$ to $1\times 10^4$. We see in this case
-that even with $1\times 10^4$ simulated events the observable is
-capable to discriminate the $\mathrm{CP}$-mixed cases by
-$5.6\sigma$.\par Finally, it is important to mention that a realistic
+scenarios under consideration is $\sim 6.5\sigma$. \par
+
+In Sec.~\ref{sec5} we defined the TP combination $\epsilon_{10}$,
+which does not depend directly on the top or antitop momenta.
+Although the top and antitop momenta would not need to be
+reconstructed to measure $\mathcal{A}(\epsilon_{10})$,
+it is still useful to examine this observable for more
+conservative numbers of events. Table~\ref{table12} shows the
+results obtained for 
+$5\times 10^4$ and $1\times 10^4$ events. We see in this case
+that even with $1\times 10^4$ events the observable is
+able to distinguish the $\mathrm{CP}$-mixed cases by
+$5.6\sigma$.\par
+
+Finally, it is important to mention that a realistic
 analysis of the sensistivity of the observables discussed in this
-paper requires the study of the impact of the backgrounds as well as
+paper requires a study of the impact of the backgrounds, as well as
 the hadronization of the quarks in the final state and the effects of
-the detector. If we consider the dominant decay mode of the higgs,
+the detector. If we consider the dominant decay mode of the Higgs boson,
 $H\rightarrow b\bbar$, in order to maximize the cross section of the
 process, the signature is given by $4$ $b$-jets, two leptons and
-missing energy, while the main background arise from the production of
-$t\tbar$ in asocciation with additional jets, being the dominant
-source the production of $t\tbar + b\bbar$. By applying a small set of
-cuts it is shown in \cite{chinos} that the
-\begin{table}[H]
-\caption{Asymmetry for the TP $\epsilon_4$ obtained by using $5\times
-  10^4, 1 \times 10^4$ and $5\times 10^3$ simulated events for the SM
-  case and the two $\mathrm{CP}$-mixed cases defined by
-  $\kp=1,\kpt=\pm 1$. }
+missing energy.  The main background arises from the production of
+$t\tbar$ in association with additional jets, with the dominant
+source being the production of $t\tbar + b\bbar$.
+In Ref.~\cite{chinos} it is shown that the application of a small
+set of cuts results in a large improvement in the signal to background
+ratio.  {\bf (KK: please check that I didn't say this incorrectly.)}
+On the experimental side, a
+rigorous treatment of the signal and backgrounds
+for the process {\bf (KK: \ldots process\ldots)}
+is performed in Ref.~\cite{atlasger}, using $20.3\,
+\mathrm{fb}^{-1}$ of data at $\sqrt{s}=8\,\mathrm{TeV}$.
+       {\bf (KK: please check that I didn't alter the meaning
+         of this last sentence when I edited it.  Also, do we need
+         to say anything about this study other than that it was done?)}
+
+\begin{table}[th]
+\caption{Asymmetry for the TP $\epsilon_4$ obtained using $5\times
+  10^4, 1 \times 10^4$ and $5\times 10^3$ events for the SM
+  case and the two $\mathrm{CP}$-mixed cases. }
 \label{table11}
@@
 \end{table}
-\begin{table}[H]
+
+\begin{table}[th]
 \caption{Asymmetry for the TP $\epsilon_{10}$ in the SM case and the
-  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$ when the
-  number of simulated events is reduced from $5\times 10^4$ to $1
-  \times 10^4$.}
+  two $\mathrm{CP}$-mixed cases for
+  $5\times 10^4$ and $1\times 10^4$ events.}
 \label{table12}
@@
 \end{table}
-\noindent
-%
-signal to background ratio is largely improved. On the other hand, a
-rigorous treatment of the backgrounds and their impact with respect to
-the signal is performed in \cite{atlasger} by using $20.3\,
-\mathrm{fb}^{-1}$ of data at $\sqrt{s}=8\,\mathrm{TeV}$.  \par The
-results shown in tables \ref{table11} and \ref{table12} reveal that
-with $5\times 10^3$ and $1\times 10^4$ events respectively the
+%
+
+The
+results shown in Tables \ref{table11} and \ref{table12} reveal that
+with $5\times 10^3$ and $1\times 10^4$ events, respectively, the
 observables $\mathcal{A}(\epsilon_4)$ and $\mathcal{A}(\epsilon_{10})$
-are still useful for testing $\kpt$. Without considering the lack of
-events related to the experimental analysis, these numbers of events
-correspond to a luminosity around $\sim
+are still useful for testing $\kpt$. Without taking into account
+the loss of events that would take place in a realistic 
+experimental analysis, these numbers of events
+correspond to a luminosity of $\sim
 300\,$-$\,600\,\mathrm{fb}^{-1}$ for the SM and even smaller for the
-$\mathrm{CP}$-mixed cases due to the larger cross section. This range
+$\mathrm{CP}$-mixed cases (due to their larger cross section). This range
 of luminosities is in principle achievable in the short term by the
@@
 luminosity, it is important to include the effects of hadronization,
-detector resolution, reconstruction eficciencies and so
-forth. However, this kind of analysis is out of the scope of this
+detector resolution, reconstruction efficiencies and so
+forth. Such an analysis, however, is beyond the scope of this
 paper.
@@
 incorporate both spin vectors: $\epsilon_1\equiv \TPa$,
-$\epsilon_2\equiv \TPb$ and $\epsilon_3\equiv \TPc$.\par We have found
+$\epsilon_2\equiv \TPb$ and $\epsilon_3\equiv \TPc$.\par
+
+We have found
 that $\epsilon_{1,2,3}$ allow to distinguish between the

### 2016-03-04 Paper_ttbarH_Draft.tex

--- 2016-03-03 Paper_ttbarH_Draft.tex
@@
 sensitive observables studied in Secs.~\ref{sec3} and \ref{sec4},
-{\bf (KK: note that I changed the reference from table3 to sec3.)}
 namely those associated with the TPs $\epsilon_4$ and $\epsilon_8$,
@@
 %
-\begin{table}[th]
+\begin{table}[H]
 \caption{Asymmetry for the TP $\epsilon_{9}$ for the SM case and the
@@
   values are obtained with $10^5$ simulated events.
-  {\bf (KK: I repositioned the table in the file, please double check to make
-  sure I didn't mess anything up :)}}
+  }
 \label{table9}
@@
 For comparison purposes, we have also used our simulated events
-to test the asymmetry corresponding to the lab frame observable given
+to test the lab frame observable given
 in Ref.~\cite{Guadagnoli}. {\bf (KK: Is this lab frame observable
@@
   just looking at whatever observable they have defined\ldots.  Sorry for
-  my confusion on this!)}  We have found that this observable
-{\bf (KK: ``asymmetry''?)}
+  my confusion on this!) (N: They compute the asymmetry of a quantity that is basically the product
+  of an angle and the sign of a TP)}  We have found that this observable
 appears to
-be slightly less sensitive than the combination $\epsilon_{10}$,
-{\bf (KK: ``$\mathcal{A}(\epsilon_{10})$''?)}
+be slightly less sensitive than $\mathcal{A}(\epsilon_{10})$,
 giving rise to a separation between the $\mathrm{CP}$-mixed scenarios

### 2016-03-04 Paper_ttbarH_Draft.tex

--- 2016-03-04 Paper_ttbarH_Draft.tex
@@
 the more promising observables, using sample sizes that are
-more attainable in the near future.  {\bf (KK: OK?)}
+more attainable in the near future.
 
@@
 the expected number of
-events increases to $\sim 5.49 \times 10^4$.
-{\bf (KK: should we use 5.5 at this point, since
-  the $K$ factor is only two sig figs?)}
+events increases to $\sim 5.5 \times 10^4$.
 On the other hand, additional cuts, as
@@
 the presence of two neutrinos in the final state (which escape the
-detector undetected), but also because final state objects need to be
-associated with their respective parent quark~\cite{atlasconf}.
-{\bf (KK: maybe we can talk about this for a minute; I don't think I
-  understand it\ldots.  Wait -- do we mean that the quarks and leptons
-  need to be associated with either the top or antitop?  If so, maybe
-  we can reword this a bit.  Suggestion follows\ldots, maybe this
-  is too explicit now, because we also wanted it to refer to the Higgs.)}
-but also because the (visible) quarks and charged leptons in the final
+detector undetected), but also because the (visible) quarks and charged leptons in the final
 state need to be correctly associated with the corresponding
@@
 already noted in Sec.~\ref{sec5}, one possibility is to use the
-neutrino weighting technique along with the kinematic equations
-arising from kinematic constraints related to the top and $W$ masses
-as well as from the energy-momentum conservation at each of the decay
-vertices involved in the process. {\bf (KK: Can we either simplify the
-  previous sentence or split it
-  into 2 or 3 sentences?  I'm not 100\% clear on which ideas go
-  together, so I wonder if one of you could give it a try.  My preference
-  would be to simplify it to something like ``\ldots weighting technique,
-  along with associated kinematic constraints'' or something like
-  that, and then give a reference.)}
-Within the context of $t\tbar$ production {\bf (KK: correct?)} this
+neutrino weighting technique along with associated kinematic constraints {\bf (N:add references)}.
+Within the context of $t\tbar$ production this
 procedure has been used, for instance, to obtain 
@@
 are useful for discriminating the signal from the backgrounds in
-$t\tbar H (H\rightarrow b\bbar)$~\cite{dosSantos}.
-{\bf (KK: do we need an initial state
-  on this process?)} In all these cases the corresponding
+$t\tbar H (H\rightarrow b\bbar)$ at the LHC~\cite{dosSantos}.
+ In all these cases the corresponding
 efficiency in the reconstruction of the momenta is up to $\sim 80\%$.
@@
 total number of signal events for the
-HL-LHC), {\bf (KK: stated correctly?)}
+HL-LHC), 
 the observable is still very sensitive to $\kpt$.
@@
 set of cuts results in a large improvement in the signal to background
-ratio.  {\bf (KK: please check that I didn't say this incorrectly.)}
+ratio.  
 On the experimental side, a
 rigorous treatment of the signal and backgrounds
-for the process {\bf (KK: \ldots process\ldots)}
+for $t\tbar H$ production with $H\to b\bbar$ 
 is performed in Ref.~\cite{atlasger}, using $20.3\,

### 2016-03-04 Paper_ttbarH_Draft.tex
Edition until Section VII

@@
 promising observable can disentangle the hypotheses $\kp=1,\kpt=\pm 1$
-by more than the $\sim 20\sigma$ statistical level.  In
+by more than the $\sim 20\sigma$ statistical level ({\bf N: OK to keep ``disentangle" here or do we need to change to something like ``can disentangle the hypotheses with effective separations of order...?"}).
+In
 the case of observables that do not need the reconstruction of the $t$
@@
 determine the sign of $\kpt$,
-with deviations between the $\kpt = \pm 1$ cases typically
-being of order $20\sigma$.
-{\bf (We couldn't figure out how to clarify this. If you find a way go ahead\ldots.)}
+with the $\kpt = \pm 1$ cases effectively separated by more than $20\sigma$.
 The sensitivity of
@@
 and \ref{table2}, we see that the capability of this
-asymmetry to distinguish between the
+asymmetry to distinguish ({\bf N: Do we add ``effectively" ?}) between the
 two $\mathrm{CP}$-mixed hypotheses is increased by at least $3\sigma$.
@@
 where $N_T$ is the total number of events.
-{\bf (KK: Have we checked numerically that the above
-  expression does indeed hold numerically for the various
-  distributions?  It's an exact relation, correct?)}
 Moreover, for a certain TP
@@
   changes for $\kp=0,\kp=1$, compared to the
-  other cases.  {\bf (KK: Do we restrict $\delta$ to be between
-    $\pm \pi/2$?  If not, we could require $a_1$ to always
-    be positive, and absorb the sign change by a shift of $\delta$ by $\pi$
-    or ssomething.  Maybe we should clarify the range allowed for $\delta$.)} }
+  other cases.  We restrict $\delta$ to be between
+    $\pm \pi/2$}
 \label{table3}
@@
   the sign of the parameter $a_1$ changes for
-  $\kp=0,\kp=1$.}
+  $\kp=0,\kp=1$ and we restrict $\delta$ to be between
+    $\pm \pi/2$}
 \label{table4}
@@
 than $\mathcal{A}(\epsilon_2)$,
-as can be seen from Table \ref{table1}. {\bf (N: We have followed your proposal but
-also added that the asymmetry for this TP, which is the one proposed by Ellis, is slightly less sensitive
- than in the case of $\epsilon_2$. This is in order to emphasize that we tend to prefer the latter (even when
- the improvement in the sensitivity is small in terms of the statistical uncertainty).) }
+as can be seen from Table \ref{table1}.
 \par
@@
 to test the lab frame observable given
-in Ref.~\cite{Guadagnoli}. {\bf (KK: Is this lab frame observable
-  just a TP, like we have used?  It seems strange to talk about an
-  asymmetry associated with an observable, when normally an asymmetry
-  is itself considered to be an observable.  I'm wondering if we are
-  considering an asymmetry associated with a TP, or if we are actually
-  just looking at whatever observable they have defined\ldots.  Sorry for
-  my confusion on this!) (N: They compute the asymmetry of a quantity that is basically the product
-  of an angle and the sign of a TP)}  We have found that this observable
+in Ref.~\cite{Guadagnoli}. We have found that this observable
 appears to
@@
 Implementing these cuts, and assuming that the final state leptons
-could be either electrons or muons, {\bf (KK: factor of 4\ldots?)}
-the SM cross section for $\ppprocess$ at
+could be either electrons or muons, the SM cross section for $\ppprocess$ at
 $14\,\mathrm{TeV}$ is $\sim 15.3\,\mathrm{fb}$; thus, the number of
@@
 already noted in Sec.~\ref{sec5}, one possibility is to use the
-neutrino weighting technique along with associated kinematic constraints {\bf (N:add references)}.
+neutrino weighting technique along with associated kinematic constraints~\cite{atlasconf,atlascharge,dosSantos}.
 Within the context of $t\tbar$ production this
@@
  In all these cases the corresponding
-efficiency in the reconstruction of the momenta is up to $\sim 80\%$.
-{\bf (KK: Does this mean that none of them exceeds 80\% or that
-  they all have an efficiency of at least 80\%?)}
+efficiencies in the reconstruction of the momenta are of order $80\%$.
 
@@
 sensitivity worsens as the number of events is reduced, but even with
-$5\times 10^3$ events the separation between the $\mathrm{CP}$-mixed
+$5\times 10^3$ events the effective separation between the $\mathrm{CP}$-mixed
 scenarios under consideration is $\sim 6.5\sigma$. \par
@@
 able to distinguish the $\mathrm{CP}$-mixed cases by
-$5.6\sigma$.\par
+$5.6\sigma$ ({\bf N: Do we add ``effectively" distinguish?}).\par
 
@@
 \mathrm{fb}^{-1}$ of data at $\sqrt{s}=8\,\mathrm{TeV}$.
-       {\bf (KK: please check that I didn't alter the meaning
-         of this last sentence when I edited it.  Also, do we need
-         to say anything about this study other than that it was done?)}
 
@@
 when $1 \times 10^5$ simulated events are used. Furthermore, we have
-shown that the angular distributions asocciated with these TPs are
+shown that the angular distributions associated with these TPs are
 also sensitive to the value of $\kp$ and $\kpt$ exhibiting a phase

### 2016-03-05 Paper_ttbarH_Draft.tex
KK edits to Conclusions

@@
 angular distribution follows the functional
-form given in Eq.~(\ref{eq27}). The ascociated shifts ($\delta$)
+form given in Eq.~(\ref{eq27}). The associated shifts ($\delta$)
 obtained for different values of $\kpt$ are expected to be of the same
@@
 than $\mathcal{A}(\epsilon_2)$,
-as can be seen from Table \ref{table1}.
+as can be seen from Table~\ref{table1}.
 \par
@@
 In this paper we have presented a collection of $\mathrm{CP}$-odd
-observables based on triple product correlations that are useful for
+observables based on triple product correlations
+in $\ppprocess$ that are useful for
 disentangling the relative sign between the scalar ($\kp$) and a
-potential pseudoscalar ($\kpt$) top-Higgs couplings in the $t\tbar H$
-production with both tops decaying leptonically. We have tested the
-sensitivity of the proposed observables by considering three types of
-observables: asymmetries, mean values and angular distributions.\par
+potential pseudoscalar ($\kpt$) top-Higgs couplings.
+We have tested the
+sensitivity of the various triple product correlations
+{\bf (KK: OK? ``observables'' was repeated)}
+by considering three types of
+observables: asymmetries, angular distributions, and mean values.
+Using these observables, we have examined several benchmark
+scenarios, focusing in particular on the SM ($\kp=1$ and $\kpt=0$)
+and on two ``$\mathrm{CP}$-mixed'' scenarios ($\kp=1$ and $\kpt=\pm1$).
+\par
 
@@
 manner that the production and the decay parts are separated, although
-connected by the spin vectors of the top and antitop which are given
+connected by the spin vectors of the top and antitop, which are given
 in terms of the momenta of the leptons in the final state. Moreover,
-we have indentified the terms linear in $\kp$ and $\kpt$ as those
+we have identified the terms linear in $\kp$ and $\kpt$ as those
 involving TPs. Among these, we have explored the three that do not
@@
 We have found
-that $\epsilon_{1,2,3}$ allow to distinguish between the
-$\mathrm{CP}$-mixed hypotheses by more than $\sim 20\sigma$ in the
+that $\epsilon_{1,2,3}$ allow one to distinguish between the
+$\mathrm{CP}$-mixed scenarios by more than $\sim 20\sigma$ in the
 case of asymmetries and $\sim 10\sigma$ in the case of mean values
@@
 shown that the angular distributions associated with these TPs are
-also sensitive to the value of $\kp$ and $\kpt$ exhibiting a phase
-shift that varies according to the values taken by these couplings. On
-the other hand, by exploring TPs that incorporate the momenta of the
-Higgs and the leptons instead of the spin vectors we can conclude that
+also sensitive to the value of $\kp$ and $\kpt$, exhibiting a phase
+shift that varies according to the values taken by these couplings.
+By exploring TPs that incorporate the momenta of the
+Higgs and the leptons instead of the spin vectors, we have concluded that
 the observables studied here appear to be more sensitive when the spin
@@
 
-On the other hand, we have proposed a combination of the TPs
-considered in the first place, $\epsilon_4\equiv
-\epsilon_3-\epsilon_2$, that exhibits the highest sensitivity with the
-separation between the $\mathrm{CP}$-mixed hypotheses being increased
-by at least $3\sigma$ in the asymmetry for $1 \times 10^5$ events with
-respect to $\mathcal{A}(\epsilon_{1,2,3})$. Again, when a similar
-combination is constructed by using the leptons momenta instead of the
+We have also proposed a combination of the TPs,
+$\epsilon_4\equiv \epsilon_3-\epsilon_2$,
+which has a greater sensitivity than $\epsilon_1$-$\epsilon_3$.
+With $1\times 10^5$ events, for example, the asymmetry associated
+with this TP gives an effective separation 
+between the $\mathrm{CP}$-mixed scenarios that
+exceeds those coming from $\epsilon_1$-$\epsilon_3$
+by at least $3\sigma$.  {\bf (KK: please check my rewording for accuracy.)}
+When a similar
+combination is constructed by using the leptons' momenta instead of the
 spin vectors ($\epsilon_8$), the sensitivity in the asymmetry is
-decreased by $\sim 3\sigma$ compared to $\mathcal{A}(\epsilon_4)$ for
+decreased by $\sim 3\sigma$ compared to the asymmetry associated
+with $\epsilon_4$ for
 the same number of events, giving values compatible with those
-obtained for the asymmetry of $\epsilon_2$ and $\epsilon_3$. \par
+obtained for the asymmetries of $\epsilon_2$ and $\epsilon_3$. \par
 
@@
 difficulty. The first one is obtained by replacing the $t$ and $\tbar$
-by the $b$ and $\bbar$ momenta ($\epsilon_9$), whereas the second
+momenta by the $b$ and $\bbar$ momenta ($\epsilon_9$), whereas the second
 includes the visible part of the $t$ and $\tbar$ momenta
-($\epsilon_{10}$). We have encountered that the latter is the most
-sensitive leading to a discrimination of the $\mathrm{CP}$-mixed cases
-under analysis by up to $\sim 16\sigma$.\par
-
-Finally we have discussed the feasibility of the most sensitive
+($\epsilon_{10}$). We have found that the latter is the more
+sensitive of the two,
+leading to a discrimination of the $\mathrm{CP}$-mixed cases
+by up to $\sim 16\sigma$.\par
+
+Finally, we have discussed the experimental {\bf (KK: OK?)}
+feasibility of the most sensitive
 observables proposed here. We have found that with $5\times 10^3$ and
-$1\times 10^4$ events respectively the observables
-$\mathcal{A}(\epsilon_4)$ and $\mathcal{A}(\epsilon_{10})$ are still
-useful for testing the hypotheses $(\kp=1,\kpt=\pm 1)$ giving rise to
-separations of order $\sim 6\sigma$. These required number of events
-would be reachable in principle in the short term by the LHC and hence
-the capability of the observables studied here for testing the sign of
-$\kpt/\kp$ could be probed in that context.
+$1\times 10^4$ events, respectively, the asymmetries
+associated with $\epsilon_4$ and $\epsilon_{10}$ are still
+useful for testing the hypotheses $(\kp=1,\kpt=\pm 1)$, giving rise to
+separations of order $\sim 6\sigma$. These numbers of events
+are within reach in the short term at the LHC,
+so that these observables could in principle be used
+to test the sign of $\kpt/\kp$ within that context.
+{\bf (KK: maybe reword this sentence a bit\ldots?)}
 
@@
 2013-0433 and No. PICT 2013-2266, and by CONICET (NM, AS). The work of
-KK was supported by the U.S.  National Science Foundation under Grant
-PHY-1215785. KK also acknowledges sabbatical support from Taylor
-University.
+DC, EG and KK was supported by the U.S.  National Science Foundation under Grant
+PHY-1215785.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-03-08 Paper_ttbarH_Draft.tex
KK edit to paragraph at the end of Sec. IIIB

@@
 taking
-$H$ to define the $z$-axis.  By studying the distributions
-for various values of $\kp$ and $\kpt$, we have
-found that they are not well described by Eq.~(\ref{eq27})
-and their range of variation is larger than that of the distributions
-displayed in Figs.~\ref{fig5} and \ref{fig6}.
-{\bf (KK: I'm not sure what this means.  Are they less cosine-like?
-  Or are the amplitudes or phase shifts larger than those for the other
-  TPs?)}
-Unlike the distributions
-related to $\epsilon_1$-$\epsilon_3$, those arising from $\epsilon_4$
-exhibit small changes in their shapes {\bf (KK: I don't think I understand
-  this, since we said that the range of variation was larger in the last
-  sentence.  I think I'm missing something :) )} for all the considered
-hypotheses and for this reason we have not included the corresponding
-plots here. However, the larger range of variation of the $\epsilon_4$
-distributions leads to higher values for the asymmetry (as can be seen
-from Tables \ref{table1} and \ref{table2}) even when the changes in
-the respective shapes are smaller {\bf (KK: I don't understand what
-  this means.)} than in the case of the
-distributions described by Eq.~(\ref{eq27}).  \par
+$H$ to define the $z$-axis.  We have studied the distributions
+for various values of $\kp$ and $\kpt$ and have
+found that they are not well described by Eq.~(\ref{eq27}).
+Instead of resembling sinusoids that are shifted to the left or
+right for different values of the parameters, the distributions
+remain peaked near $\Delta\phi(n_t,n_{\tbar})=0$, but become
+slightly distorted in such a way that there is a non-zero
+asymmetry [see Eq.~(\ref{eq26})].  Interestingly, while there
+is not much visible change in the $\epsilon_4$ angular distribution
+for different
+parameter values, the associated asymmetry values are
+larger than the asymmetries for the other TPs [see
+  Tables \ref{table1} and \ref{table2}].  Since this angular
+distribution does not exhibit much visible change for
+different values of $\kp$ and $\kpt$, we do not include the corresponding
+plots here.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-03-08 Paper_ttbarH_Draft.tex
Small edits in the conclusions

--- 2016-03-05 Paper_ttbarH_Draft.tex
@@
 sensitivity of the various triple product correlations
-{\bf (KK: OK? ``observables'' was repeated)}
 by considering three types of
@@
 exceeds those coming from $\epsilon_1$-$\epsilon_3$
-by at least $3\sigma$.  {\bf (KK: please check my rewording for accuracy.)}
+by at least $3\sigma$.  
 When a similar
@@
 
-Finally, we have discussed the experimental {\bf (KK: OK?)}
+Finally, we have discussed the experimental 
 feasibility of the most sensitive

### 2016-03-08 Paper_ttbarH_Draft.tex

--- 2016-03-08 Paper_ttbarH_Draft.tex
@@
 sensitive to the corresponding relative sign. The proposed observables
-are based on triple product (TP) structures that we extract
+are based on triple product (TP) structures {\bf (N: correlations?)} that we extract
 from the expression of the differential cross section in terms of the
@@
   envisioned for the HL-LHC, we find that the most
-promising observable can disentangle the hypotheses $\kp=1,\kpt=\pm 1$
-by more than the $\sim 20\sigma$ statistical level ({\bf N: OK to keep ``disentangle" here or do we need to change to something like ``can disentangle the hypotheses with effective separations of order...?"}).
+promising observable can disentangle the hypotheses {\bf (N: scenarios?)} $\kp=1,\kpt=\pm 1$
+by more than the $\sim 20\sigma$ statistical level {\bf (N: OK to keep ``disentangle" here or do we need to change to something like ``can disentangle the hypotheses with effective separations of order...?")}.
 In

### 2016-03-09 Paper_ttbarH_Draft.tex
KK: small edit at the end of Sec. IV

@@
 consideration are comparable with the values listed in Table
-\ref{table6} for $\epsilon_5$. Concerning the associated angular
-distributions, their range of variation {\bf (KK: I'm not sure what
-  this means)} is larger than in the case of
-the distributions related to $\epsilon_5$-$\epsilon_7$ but exhibit
-smaller changes in their shapes for the different scenarios and for
-this reason we do not include here the corresponding plots.
-{\bf (KK: might need to reword this a bit after clarifying what 
-  range of variation means.)}
+\ref{table6} for $\epsilon_5$.
+We have also studied the associated angular distributions.
+We do not include plots of these distributions, however,
+because they
+do not exhibit much visible variation for the different
+scenarios under consideration.  (The situation is similar
+to that encountered for the angular distribution
+associated with $\epsilon_4$ -- see the discussion
+at the end of Sec.~\ref{sec3.2}.)
+{\bf (KK: have I worded this correctly?
+  Does the distribution look similar even in the
+  purely CP-odd case, for example?)}
+
 \begin{table}[H]

### 2016-03-09 Paper_ttbarH_Draft.tex
KK edits to a few of the bold-faced questions/comments; added a few new comments/questions

@@
 sensitive to the corresponding relative sign. The proposed observables
-are based on triple product (TP) structures {\bf (N: correlations?)} that we extract
-from the expression of the differential cross section in terms of the
+are based on triple product (TP) correlations that we extract
+from the expression for the differential cross section in terms of the
 spin vectors of the top and antitop quarks. In order to explore other
@@
 lepton momenta or the $t$ and $\tbar$ momenta by their visible parts.
+We generate Monte Carlo data sets for several benchmark scenarios,
+including the Standard Model ($\kp=1$, $\kpt=0$) and
+two scenarios with mixed $\mathrm{CP}$ properties ($\kp=1$, $\kpt=\pm 1$).
+{\bf (KK: worded correctly?)}
 Assuming an integrated luminosity that is consistent with that
-  envisioned for the HL-LHC, we find that the most
-promising observable can disentangle the hypotheses {\bf (N: scenarios?)} $\kp=1,\kpt=\pm 1$
-by more than the $\sim 20\sigma$ statistical level {\bf (N: OK to keep ``disentangle" here or do we need to change to something like ``can disentangle the hypotheses with effective separations of order...?")}.
-In
-the case of observables that do not need the reconstruction of the $t$
-and $\tbar$ momenta, the power of discrimination is up to the $\sim
-16\sigma$ statistical level for the same number of events. We also show that the
-capability of the most promising observables for separating the
-$\mathrm{CP}$-mixed hypotheses preveals even when a number of events
-plausible within the short term LHC is considered.
-
-%We also show that the sensitivity of the most promising observables is not spoiled when a number of events affordable by the short term LHC is considered.
-
-%We also show that even when the number of events is reduced by an order of magnitude the most promising observables are still useful for testing the couplings
+envisioned for the HL-LHC, and taking into account
+only statistical uncertainties,
+{\bf (KK: do we need to define the HL-LHC?)}
+we find that the most
+promising observable can disentangle the
+``$\mathrm{CP}$-mixed'' scenarios 
+with an effective separation of $\sim 20\sigma$.  In
+the case of observables that do not require the reconstruction of the $t$
+and $\tbar$ momenta, the power of discrimination is up to $\sim
+16\sigma$ for the same number of events. We also show that the
+most promising observables can still disentangle the
+$\mathrm{CP}$-mixed scenarios when the number of events
+is reduced to be consistent with that expected
+in the short term at the LHC.
+
 \end{abstract}
@@
 analyze the cases $\kpt=0,\pm 0.25, \pm 0.5, \pm 0.75,\pm 1$.
+We shall often focus on the scenarios with $\kp=1$ and
+$\kpt=\pm 1$, which we shall refer to as the ``$\mathrm{CP}$-mixed''
+scenarios.
 In addition, we also provide some analysis regarding the pure
@@
   correspond to the SM ($\kp=1$ and $\kpt=\pm 0$) and
-  two $\mathrm{CP}$-mixed cases (defined by
+  two ``$\mathrm{CP}$-mixed'' cases (defined by
   $\kp=1$ and $\kpt=\pm 1$).}
@@
 $(\vec{t}-\vec{\tbar}\,)\cdot(\vec{n}_t\times \vec{n}_{\tbar})$.
-{\bf (KK: try to connect previous sentences to something later on\ldots.)}
 The
 values obtained for the asymmetry associated with this TP are shown in
-Table~\ref{table2}. By comparing the results in Tables \ref{table1}
+Table~\ref{table2}. By comparing the results in Tables~\ref{table1}
 and \ref{table2}, we see that the capability of this
-asymmetry to distinguish ({\bf N: Do we add ``effectively" ?}) between the
-two $\mathrm{CP}$-mixed hypotheses is increased by at least $3\sigma$.
+asymmetry to distinguish between the
+two $\mathrm{CP}$-mixed scenarios is increased by at least $3\sigma$.
 \vspace{4mm}
@@
 \caption{Asymmetry for the TP $\epsilon_{4}$ for the SM case and the
-  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
+  two $\mathrm{CP}$-mixed scenarios.  The
   values are obtained by using $10^5$ simulated events.}
@@
 the numerators of the 
-asymmetries are all linear in both
+asymmetries are linear in both
 $\kp$ and $\kpt$, they are expected to vanish in these cases. However, we
@@
 except that the ``shifts'' are in the opposite directions for
-the two mixed-$\mathrm{CP}$ cases.  Given the similarities of the
+the two $\mathrm{CP}$-mixed cases.  Given the similarities of the
 plots we do not include them here. 
@@
 distributions are shifted to the left or the right of the origin
-in the mixed-$\mathrm{CP}$
+in the $\mathrm{CP}$-mixed
 cases ($\kp =1$ and $\kpt=\pm 1$).
@@
 the pure pseudoscalar case ($\kp =0$ and $\kpt= 1$) are
-visibly different from each other and from the mixed-$\mathrm{CP}$
+visibly different from each other and from the $\mathrm{CP}$-mixed
 scenarios. Comparing the SM and purely pseudoscalar cases,
@@
 that even with $1\times 10^4$ events the observable is
-able to distinguish the $\mathrm{CP}$-mixed cases by
-$5.6\sigma$ ({\bf N: Do we add ``effectively" distinguish?}).\par
+effectively able to distinguish the $\mathrm{CP}$-mixed cases by
+$5.6\sigma$.
 
@@
 so that these observables could in principle be used
-to test the sign of $\kpt/\kp$ within that context.
-{\bf (KK: maybe reword this sentence a bit\ldots?)}
+to test the relative sign of $\kp$ and $\kpt$ within that context.
 

### 2016-03-09 Paper_ttbarH_Draft.tex
KK edits to the abstract and intro

@@
 Assuming an integrated luminosity that is consistent with that
-envisioned for the HL-LHC, and taking into account
+envisioned for the High Luminosity Large Hadron Collider,
+and taking into account
 only statistical uncertainties,
-{\bf (KK: do we need to define the HL-LHC?)}
 we find that the most
@@
 $\mathrm{CP}$-mixed scenarios when the number of events
-is reduced to be consistent with that expected
-in the short term at the LHC.
+is reduced to values consistent with expectations
+for the Large Hadron Collider in the near term.
 
@@
 the $tH$ coupling directly, processes with smaller cross sections need
-to be taken into account.  \par
+to be considered.  \par
 
@@
 couplings. The proposed observables are based on a particular set of
-triple product (TP) structures that we extract naturally from the
+triple product (TP) structures that we extract from the
 expression for the differential cross section for $\ppprocess$,
@@
 momenta and separate the production process from the decay. This
-allows to identify straightforwardly the contributions linearly
+allows for the straightforward identification of the contributions
+that are linearly
 sensitive to the couplings.
- Further, the TPs correlations in these
-contributions incorporate the $t$ and $\tbar$ spin vectors. Starting
+TPs correlations in these
+contributions incorporate the $t$ and $\tbar$ spin vectors; starting
 with these TPs, we not only recover the observables given in
-\cite{Ellis,Guadagnoli} but also propose additional possibilities that
-increase the sensitivity. In order to establish a hierarchy in the
-sensitivity of the TPs under analysis we investigate three different
-types of observables by using simulated events: asymmetries, mean
+Refs.~\cite{Ellis,Guadagnoli} but also propose additional possibilities that
+have an increased sensitivity to the $tH$ coupling.
+In order to establish a hierarchy in the
+sensitivity of the TPs under analysis we use simulated events
+to investigate three different
+types of observables: asymmetries, mean
 values and angular distributions. We note that TP correlations have
-been used in \cite{Valencia1,*Valencia2} in the context of top-quark
-production and decay and in \cite{Valencia3} in the framework of
+been used in Ref.~\cite{Valencia1,*Valencia2} in the context of top-quark
+production and decay and in Ref.~\cite{Valencia3} in the framework of
 anomalous color dipole operators.  \par
@@
 $\ppprocess$ and derive a general expression for the differential
-cross section from which a first set of TP correlations is
-extracted. In Sec.~\ref{sec3} we probe the sensitivity of these TPs to
+cross section.  A first set of TP correlations is then
+extracted from this expression.
+In Sec.~\ref{sec3} we probe the sensitivity of these TPs to
 the $tH$ coupling by using various $\mathrm{CP}$-odd
-observables. Subsequent sections are dedicated to explore another
-possibilities of $\mathrm{CP}$-odd observables. In particular,
-observables based on TPs that incorporate the Higgs momentum are
-discussed in Sec.~\ref{sec4}, whereas observables obtained without
-using the $t$ and $\tbar$ momenta are studied in
-Sec.~\ref{sec5}. Finally, Sec.~\ref{sec6} is devoted to the discussion
-on the experimental feasibility of the most promising observables
+observables. Subsequent sections are dedicated to the analysis of
+other $\mathrm{CP}$-odd observables. In particular,
+observables based on TPs that incorporate the Higgs momentum
+{\bf (KK: not all of them involve the Higgs momentum in this section\ldots
+  is this the best way to describe this section?
+  I'm fine with it, either way.)} are
+discussed in Sec.~\ref{sec4}, and observables that do not
+involve the $t$ and $\tbar$ momenta are studied in
+Sec.~\ref{sec5}.  In Sec.~\ref{sec6} we discuss
+the experimental feasibility of the most promising observables
 encountered here. The main conclusions are summarized in
@@
 
-At the LHC $t\bar{t}H$ production proceeds via $q\bar{q}$
+At the Large Hadron Collider (LHC) $t\bar{t}H$ production proceeds via $q\bar{q}$
 annihilation and $gg$ fusion processes. The relevant leading-order Feynman
@@
 which observables would be most promising.  
-The number of events expected at the HL-LHC, however, is
+The number of events expected at the High Luminosity Large
+Hadron Collider (HL-LHC), however, is
 smaller than the number of events that we have used in our

### 2016-03-10 Paper_ttbarH_Draft.tex
KK: small edits to much of paper; also included a new diff.pdf file

@@
   b_i{\ell}^+\nu_{\ell})\tbar(\to \bbar_j {\ell}^- \nubar) H$. The
-  indices $i,j$ denote the colour of the quarks while $a,b$ are gluon
+  indices $i,j$ denote the colours of the quarks, while $a,b$ are gluon
   indices.}
@@
 spinor techniques
-developed in \cite{Kleiss} to write $\bar{\psi}_t$ and
+developed in Ref.~\cite{Kleiss} to write $\bar{\psi}_t$ and
 $\psi_{\tbar}$ as follows\footnote{These spinor techniques can also be used
@@
 approximation for the top and antitop quarks and for the $W^\pm$ gauge
-bosons.\footnote{Since Eq.~(\ref{eq9}) contains the top quark propagator
+bosons{\bf (KK: remove ``\ldots and for the\ldots''?)}.\footnote{Since Eq.~(\ref{eq9}) contains the top quark propagator
   term
@@
 we arrive at the expression in Eq.~(\ref{eq2}).\footnote{The reader may note that in the differential widths of $t\to b{\ell}^+\nu_{\ell}$ and $\tbar\to \bar{b}{\ell}^-\bar{\nu}_{\ell}$ appearing in 
-Eq.~(\ref{eq2}), the spin states of the top an antitop have been averaged.
+Eq.~(\ref{eq2}), the spin states of the top and antitop have been averaged.
 Interestingly, under the assumption of massless final-state particles, the amplitudes $\mathcal{M}(t(-n_t)\to b{\ell}^+\nu_{\ell})$ and $\mathcal{M}(\tbar(-n_{\tbar})\to \bar{b}{\ell}^-\bar{\nu}_{\ell})$ vanish.
@@
 $g^2_s m_t/v$ and $-ig^2_s m_t/v$ arising from the vertices of the $t$-
-and $s$-channel diagrams respectively have been included in the
+and $s$-channel diagrams, respectively, have been included in the
 definition of $C^{ab,ij}_k$ for convenience. The terms linear in $\kp$
@@
 TPs. Hence, only the functions $f_{1,2}$ will contribute to the total
-cross-section, whereas the TP terms will be sensitive to the sign of
+cross section, whereas the TP terms will be sensitive to the sign of
 the anomalous coupling $\kpt$. Of the fifteen TPs mentioned above,
@@
 following set of cuts: $p_T$ of leptons $> 10\,\mathrm{GeV}$, $|\eta|$
-of leptons $< 2.5$, $|\eta|$ of b jets $< 2.5$ and $\Delta
+of leptons $< 2.5$, $|\eta|$ of $b$ jets $< 2.5$ and $\Delta
 R_{\ell\ell}>0.4$.  Note that we have used this
 somewhat large number of events ($10^5$) in order to determine clearly
-the extent to which the proposed observables are sensitive to the NP
+the extent to which the proposed observables are sensitive to the anomalous
 coupling.  Section~\ref{sec6} contains an
@@
   \caption{Asymmetries for three different scenarios,
-    obtained by using $10^5$ simulated events for the
+    obtained by using $10^5$ simulated events, for the
     TPs $\epsilon_1=\TPa, \epsilon_2=\TPb$ and $\epsilon_3=\TPc$.
     The three scenarios
-  correspond to the SM ($\kp=1$ and $\kpt=\pm 0$) and
+  correspond to the SM ($\kp=1$ and $\kpt= 0$) and the
   two ``$\mathrm{CP}$-mixed'' cases (defined by
@@
 two $\mathrm{CP}$-mixed scenarios is increased by at least $3\sigma$.
+{\bf (KK: looks like 2.5$\sigma$ is the min difference?  maybe a rounding
+  thing; but see also the comment in the table caption.)}
 \vspace{4mm}
@@
   two $\mathrm{CP}$-mixed scenarios.  The
-  values are obtained by using $10^5$ simulated events.}
+  values are obtained using sets of $10^5$ simulated events.
+{\bf (KK: In the previous table we used 3 sig figs for the ratios like ``12.0'', etc.  Should we do the same in both tables for consistency?)}}
 \label{table2}
@@
   $\Delta\phi_1(n_t,n_{\tbar})$ is the angular difference between the
-  projection of the spin vectors in the plane perpendicular to
+  projection of the spin vectors onto the plane perpendicular to
   $\vec{\tbar}$.
@@
   $\Delta\phi_2(n_t,n_{\tbar})$ is the angular difference between the
-  projection of the spin vectors in the plane perpendicular to
+  projection of the spin vectors onto the plane perpendicular to
   $\vec{\tbar}$.
@@
   is the angular difference between the projection of the spin vectors
-  in the plane perpendicular to $\vec{t}$.
+  onto the plane perpendicular to $\vec{t}$.
 \end{enumerate}
@@
 Eq.~(\ref{eq26}) 
-gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$. With
+gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$ {\bf (KK: sign
+  incorrect? numbers don't agree between Tables I and III otherwise)}. With
 this fitting function, we obtain phase shifts $\delta$ that
@@
   we do not include the corresponding results for the $\epsilon_3$ distribution
-  here.}  However, the quality of the fits in the four considered scenarios is
+  here.}  However, the quality of the fits in the four scenarios considered is
 not very good, particularly for $\epsilon_1$.  The
@@
   other cases.  We restrict $\delta$ to be between
-    $\pm \pi/2$}
+    $\pm \pi/2$.}
 \label{table3}
@@
   $\kp=0,\kp=1$ and we restrict $\delta$ to be between
-    $\pm \pi/2$}
+    $\pm \pi/2$.}
 \label{table4}
@@
 case from both $\mathrm{CP}$-mixed cases. Furthermore,
-two $\mathrm{CP}$-mixed cases
+the two $\mathrm{CP}$-mixed cases
 are clearly disentangled, since the the observables are
@@
 \rangle$ and $\langle \epsilon_3 \rangle$ appear to be slightly more
-sensitive than $\langle \epsilon_1 \rangle$. On the other hand, the
+sensitive than $\langle \epsilon_1 \rangle$.  Also, the
 mean value for the combination $\epsilon_4$ introduced in
 Sec.~\ref{sec3.1} gives slightly smaller values than those listed in
-Table \ref{table5}, yielding $-4.32$, $1.11$ and $7.23$ for the cases
+Table~\ref{table5} for $\langle \epsilon_2
+\rangle$ and $\langle \epsilon_3 \rangle$,
+       {\bf (KK: explicit reference to $\epsilon_2$ and $\epsilon_3$ correct?
+         Seems like $\epsilon_4$ is actually a bit better than $\epsilon_1$)}
+yielding $-4.32$, $1.11$ and $7.23$ for the cases
 $(\kp=1,\kpt=-1,0,1)$, respectively. As with the asymmetry, the
@@
 and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ [defined in
-Eqs.~(\ref{eq3})-(\ref{eq4}].  Furthermore, we have described the general
-form of the differential cross-section in terms of these vectors in
+Eqs.~(\ref{eq3})-(\ref{eq4})].  Furthermore, we have described the general
+form of the differential cross section in terms of these vectors in
 Eq.~(\ref{eq20}). In this section we consider other
@@
 $\mathrm{CP}$-odd observables can be constructed. From the definitions
-in Eqs.~(\ref{eq3})-(\ref{eq4}), we see that the TPs
+in Eqs.~(\ref{eq3}) and (\ref{eq4}), we see that the TPs
 $\epsilon_{1,2,3}$ can be written as follows,
@@
 \caption{Asymmetries for the TPs $\epsilon_{5,6,7}$ for the SM case
-  and the two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm
-  1$. The values correspond to $10^5$ simulated events.}
+  and the two $\mathrm{CP}$-mixed cases.
+  The values correspond to $10^5$ simulated events.}
 \label{table7}
@@
 \begin{table}[H]
-\caption{Mean values obtained for the TPs $\epsilon_{5,6,7}$ for the
-  SM case and two $\mathrm{CP}$-mixed cases with opposite sign in the
-  pseudoscalar coupling. The values correspond to $10^5$ simulated
+\caption{Mean values obtained for $\epsilon_{5,6,7}$ for the
+  SM case and the two $\mathrm{CP}$-mixed cases.
+  The values correspond to $10^5$ simulated
   events.}
@@
 \ref{table6} summarize the results for the TPs $\epsilon_{5,6,7}$.
-We see that the TP $\epsilon_5$ gives rise to asymmetries and mean
-values that are clearly higher than those obtained from $\epsilon_6$
+We see that $\epsilon_5$ gives rise to asymmetries and mean
+values that are clearly higher than those obtained for $\epsilon_6$
 and $\epsilon_7$. This is in contrast to the TPs $\epsilon_{1,2,3}$,
-for which the asymmetries and mean values are comparable for the TPs
+for which the asymmetries and mean values are comparable among the
+TPs
 (see Tables
@@
 Tables~\ref{table5} and \ref{table6} that the TPs $\epsilon_{1,2,3}$
-appear to have a higher sensitivity to the pseudoscalar coupling than
+appear to have a higher sensitivity to the pseudoscalar coupling than do
 $\epsilon_{5,6,7}$.  \par
@@
 $t\tbar$ rest frame the sign of the TP $\epsilon_5$ is defined through
-the angle $\Delta\phi_{\ell^-\ell^+}$ [see the discussion following
+the angle $\Delta\phi(\ell^-,\ell^+)$ {\bf (KK: notation change OK? making this
+  similar to the others)} [see the discussion following
   Eq.~(\ref{eq25})],
@@
 projections of the leptons' momenta onto the plane perpendicular to
-$\vec{\tbar}$. By a similar argument to that discussed at the
-beginning of Sec.~\ref{sec3.2}, we can construct an associated angular
+$\vec{\tbar}$.  As in Sec.~\ref{sec3.2}, we can construct an associated angular
 distribution [see Eq.~(\ref{eq26})] that
-will be sensitive to the sign of the pseudoscalar coupling. This
-angular variable is the same as that proposed in Ref.~\cite{Ellis} as a
+will be sensitive to the sign of the pseudoscalar coupling. The
+angular variable $\Delta\phi(\ell^-,\ell^+)$ {\bf (KK: OK?)}
+is the same as that proposed in Ref.~\cite{Ellis} as a
 useful $\mathrm{CP}$-odd observable. Moreover, it is shown in
@@
 order as those exhibited by the $\Delta\phi_1(n_t,n_{\tbar})$
-distribution since this distribution
+distribution since the $\Delta\phi(\ell^-,\ell^+)$ distribution {\bf (KK: OK?)}
 is constrained by the asymmetry $\mathcal{A}(\epsilon_5)$
@@
 which in turn is equal to
-$\mathcal{A}(\epsilon_1)$. Also, we note that $\mathcal{A}(\epsilon_5)$ is slightly smaller 
+$\mathcal{A}(\epsilon_1)$. Also, we note that $\mathcal{A}(\epsilon_5)$ is slightly less sensitive
 than $\mathcal{A}(\epsilon_2)$,
@@
 
+{\bf (KK: moved this paragraph, since we have already
+  discussed the $\epsilon_5$ angular distribution.)}
+In addition to the $\epsilon_5$ angular distribution
+(defined above), one can also define angular distributions
+corresponding to $\epsilon_6$ and $\epsilon_7$.  As was the case
+for the $\epsilon_5$ distribution,
+the corresponding angles will be defined in terms
+of the momenta of the leptons instead of in terms of the spin vectors
+(as was done in Sec.~\ref{sec3.2}). The
+angular distributions based on $\epsilon_5$-$\epsilon_7$
+have the same overall behaviour as those derived from
+$\epsilon_1$-$\epsilon_3$.  Using Eq.~(\ref{eq27})
+to fit the distributions and comparing to the results obtained for
+$\epsilon_1$-$\epsilon_3$, we find that the phase shifts ($\delta$)
+are comparable for the $\epsilon_5$ angular distribution, but are
+smaller for the
+$\epsilon_6$ and $\epsilon_7$ distributions.  
+\par
+
 In analogy with the
@@
 combination of the TPs $\epsilon_{5,6,7}$ for which the asymmetry is
-enhanced with respect to $\epsilon_5$-$\epsilon_7$,
+enhanced compared to those for $\epsilon_5$-$\epsilon_7$,
 %
@@
 $(\vec{t}-\vec{\tbar})\cdot (\vec{\ell}^+\! \times
-\vec{\ell}^-)$. Comparing Eqs.~(\ref{eq24}) and (\ref{eq32})
+\vec{\ell}^-)$. Comparing Eqs.~(\ref{eq24}) and (\ref{eq32}),
 and noting that $Q=(t+\tbar+H)/2$, we see that the only
@@
 
-Having defined the TPs $\epsilon_5$-$\epsilon_7$, one can
-proceed, as in Sec.~\ref{sec3.2}, to define corresponding
-angular distributions.  Of
-course, in this case the corresponding angles will be defined in terms
-of the momenta of the leptons instead of using the spin vectors. The
-angular distributions based on $\epsilon_5$-$\epsilon_7$
-have the same overall behaviour as those derived from
-$\epsilon_1$-$\epsilon_3$.  Using Eq.~(\ref{eq27})
-to fit the distributions and comparing to the results obtained for
-$\epsilon_1$-$\epsilon_3$, we find that the phase shifts ($\delta$)
-are comparable for the $\epsilon_5$ angular distribution, but are
-smaller for the
-$\epsilon_6$ and $\epsilon_7$ distributions.  
-\par
-
 The mean values of $\epsilon_8$ for the scenarios under
@@
 \caption{Asymmetry for the TP $\epsilon_{8}$ for the SM case and the
-  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
+  two $\mathrm{CP}$-mixed scenarios. The
   values are obtained with $10^5$ simulated events.}
@@
 \caption{Asymmetry for the TP $\epsilon_{9}$ for the SM case and the
-  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
+  two $\mathrm{CP}$-mixed cases. The
   values are obtained with $10^5$ simulated events.
@@
 Eq.~(\ref{eq24}) and using the definitions of the spin vectors
-in Eqs.~(\ref{eq3})-(\ref{eq4}), we have
+in Eqs.~(\ref{eq3}) and (\ref{eq4}), we have
 %
@@
 \caption{Asymmetry for the TP $\epsilon_{10}$ for the SM case and the
-  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
+  two $\mathrm{CP}$-mixed cases. The
   values are obtained by using $10^5$ simulated events.}
@@
 $t\tbar H (H\rightarrow b\bbar)$ at the LHC~\cite{dosSantos}.
- In all these cases the corresponding
+ In all of these cases the corresponding
 efficiencies in the reconstruction of the momenta are of order $80\%$.
@@
 that even with $1\times 10^4$ events the observable is
-effectively able to distinguish the $\mathrm{CP}$-mixed cases by
+able to distinguish the $\mathrm{CP}$-mixed cases by
 $5.6\sigma$.
@@
 Finally, it is important to mention that a realistic
-analysis of the sensistivity of the observables discussed in this
+analysis of the sensitivity of the observables discussed in this
 paper requires a study of the impact of the backgrounds, as well as
@@
 disentangling the relative sign between the scalar ($\kp$) and a
-potential pseudoscalar ($\kpt$) top-Higgs couplings.
+potential pseudoscalar ($\kpt$) top-Higgs coupling.
 We have tested the
@@
 shown that the angular distributions associated with these TPs are
-also sensitive to the value of $\kp$ and $\kpt$, exhibiting a phase
+also sensitive to the values of $\kp$ and $\kpt$, exhibiting a phase
 shift that varies according to the values taken by these couplings.
@@
 exceeds those coming from $\epsilon_1$-$\epsilon_3$
-by at least $3\sigma$.  
+by at least $3\sigma$. {\bf (KK: 2.5$\sigma$ is the min difference?)}   
 When a similar
@@
 with $\epsilon_4$ for
-the same number of events, giving values compatible with those
+the same number of events, giving values comparable with those
 obtained for the asymmetries of $\epsilon_2$ and $\epsilon_3$. \par
@@
 sensitive of the two,
-leading to a discrimination of the $\mathrm{CP}$-mixed cases
-by up to $\sim 16\sigma$.\par
+leading to a separation between the $\mathrm{CP}$-mixed cases
+of $\sim 16\sigma$. {\bf (KK: wording change OK?)}\par
 

### 2016-03-10 Paper_ttbarH_Draft.tex
fixed two small typos

@@
 sensitive to the couplings.
-TPs correlations in these
+TP correlations in these
 contributions incorporate the $t$ and $\tbar$ spin vectors; starting
@@
 We see that $\epsilon_5$ gives rise to asymmetries and mean
-values that are clearly higher than those obtained for $\epsilon_6$
+values that are clearly larger than those obtained for $\epsilon_6$
 and $\epsilon_7$. This is in contrast to the TPs $\epsilon_{1,2,3}$,

### 2016-03-10 Paper_ttbarH_Draft.tex
Small edits

--- 2016-03-10 Paper_ttbarH_Draft.tex
@@
 two scenarios with mixed $\mathrm{CP}$ properties ($\kp=1$, $\kpt=\pm 1$).
-{\bf (KK: worded correctly?)}
 Assuming an integrated luminosity that is consistent with that
@@
 ``$\mathrm{CP}$-mixed'' scenarios 
-with an effective separation of $\sim 20\sigma$.  In
+with an effective separation of $\sim 20\sigma$ {\bf (N: In previous version it said ``statistical level" because we wanted 
+to stress that we are not considering systematic uncertainties.)}.  In
 the case of observables that do not require the reconstruction of the $t$
@@
 other $\mathrm{CP}$-odd observables. In particular,
-observables based on TPs that incorporate the Higgs momentum
+observables based on TPs that {\bf (N: ``do not contain the $t$ and $\tbar$ spin vectors and
+in certain cases incorporate")} the Higgs momentum
 {\bf (KK: not all of them involve the Higgs momentum in this section\ldots
@@
   I'm fine with it, either way.)} are
-discussed in Sec.~\ref{sec4}, and observables that do not
+discussed in Sec.~\ref{sec4} {\bf (N: ;)} and observables that do not
 involve the $t$ and $\tbar$ momenta are studied in
@@
 Note that in writing down the above expressions we have adopted the narrow-width
-approximation for the top and antitop quarks and for the $W^\pm$ gauge
-bosons{\bf (KK: remove ``\ldots and for the\ldots''?)}.\footnote{Since Eq.~(\ref{eq9}) contains the top quark propagator
+approximation for the top and antitop quarks.\footnote{Since Eq.~(\ref{eq9}) contains the top quark propagator
   term
@@
   the factor $((t^2-m^2_t)^2+m^2_t\Gamma^2_t)^{-1}$,
-  which is replaced by $(\pi/m_t\Gamma_t)\delta(t^2-m^2_t)$
+  which is replaced by $(\pi/(m_t\Gamma_t))\delta(t^2-m^2_t)$
   in the narrow-width approximation.  Thus, except for the propagator terms $\mathbb{P}_t(t)$ and $\mathbb{P}_t(\tbar)$,
@@
 
-We have also tested various
-linear combinations of the TPs $\epsilon_{1,2,3}$ and have found
+We have also tested various combinations of the TPs $\epsilon_{1,2,3}$ and have found
 that the asymmetry is enhanced for the following combination:
@@
 asymmetry to distinguish between the
-two $\mathrm{CP}$-mixed scenarios is increased by at least $3\sigma$.
-{\bf (KK: looks like 2.5$\sigma$ is the min difference?  maybe a rounding
-  thing; but see also the comment in the table caption.)}
+two $\mathrm{CP}$-mixed scenarios is increased by at least $2.8\sigma$.
 \vspace{4mm}
@@
   values are obtained using sets of $10^5$ simulated events.
-{\bf (KK: In the previous table we used 3 sig figs for the ratios like ``12.0'', etc.  Should we do the same in both tables for consistency?)}}
+}
 \label{table2}
@@
 %\hhline{|--------|}
-$1$ & $-1$~~~ & $-0.0371$~~~ & $-12$~~~ \\[0.6mm]
+$1$ & $-1$~~~ & $-0.0371$~~~ & $-11.7$~~ \\[0.6mm]
 \hline
@@
 \hline
-$1$ & $1$ & $0.0461$~ & $14\,$ \\[0.6mm]
+$1$ & $1$ & $0.0461$~ & $14.6$ \\[0.6mm]
 \hhline{|====|}
@@
 Eq.~(\ref{eq26}) 
-gives $\mathcal{A}(\epsilon_i)=4a_1 \sin\delta$ {\bf (KK: sign
-  incorrect? numbers don't agree between Tables I and III otherwise)}. With
+gives $\mathcal{A}(\epsilon_i)=-4a_1 \sin\delta$. With
 this fitting function, we obtain phase shifts $\delta$ that
@@
        {\bf (KK: explicit reference to $\epsilon_2$ and $\epsilon_3$ correct?
-         Seems like $\epsilon_4$ is actually a bit better than $\epsilon_1$)}
+         Seems like $\epsilon_4$ is actually a bit better than $\epsilon_1$) (N: The effective separation
+         for $\epsilon_4$ is $11.55$ while for $\epsilon_1$ is $12.24$)}
 yielding $-4.32$, $1.11$ and $7.23$ for the cases
@@
 The above equations express the TPs studied in the last sections as
-linear combination of TPs involving the momenta $t,\tbar,H,\ell^+$ and
+a combination of TPs involving the momenta $t,\tbar,H,\ell^+$ and
 $\ell^-$, with coefficients that are functions of phase space
@@
 $t\tbar$ rest frame the sign of the TP $\epsilon_5$ is defined through
-the angle $\Delta\phi(\ell^-,\ell^+)$ {\bf (KK: notation change OK? making this
-  similar to the others)} [see the discussion following
+the angle $\Delta\phi(\ell^-,\ell^+)$ [see the discussion following
   Eq.~(\ref{eq25})],
@@
 will be sensitive to the sign of the pseudoscalar coupling. The
-angular variable $\Delta\phi(\ell^-,\ell^+)$ {\bf (KK: OK?)}
+angular variable $\Delta\phi(\ell^-,\ell^+)$ 
 is the same as that proposed in Ref.~\cite{Ellis} as a
@@
 order as those exhibited by the $\Delta\phi_1(n_t,n_{\tbar})$
-distribution since the $\Delta\phi(\ell^-,\ell^+)$ distribution {\bf (KK: OK?)}
+distribution since the $\Delta\phi(\ell^-,\ell^+)$ distribution 
 is constrained by the asymmetry $\mathcal{A}(\epsilon_5)$
@@
 
-{\bf (KK: moved this paragraph, since we have already
-  discussed the $\epsilon_5$ angular distribution.)}
 In addition to the $\epsilon_5$ angular distribution
@@
 exceeds those coming from $\epsilon_1$-$\epsilon_3$
-by at least $3\sigma$. {\bf (KK: 2.5$\sigma$ is the min difference?)}   
+by at least $2.8\sigma$.  
 When a similar
@@
 spin vectors ($\epsilon_8$), the sensitivity in the asymmetry is
-decreased by $\sim 3\sigma$ compared to the asymmetry associated
+decreased by $\sim 3.1\sigma$ compared to the asymmetry associated
 with $\epsilon_4$ for
@@
 leading to a separation between the $\mathrm{CP}$-mixed cases
-of $\sim 16\sigma$. {\bf (KK: wording change OK?)}\par
+of $\sim 16\sigma$.\par
 

### 2016-03-10 Paper_ttbarH_Draft.tex
small edits and replies to comments/questions

@@
 with an effective separation of $\sim 20\sigma$ {\bf (N: In previous version it said ``statistical level" because we wanted 
-to stress that we are not considering systematic uncertainties.)}.  In
+  to stress that we are not considering systematic uncertainties.
+  KK: This was why I added the new phrase, ``and taking into account
+  only statistical uncertainties.''  You can certainly
+  change this back if you like,
+  though.  The previous way of wording it seemed not completely fluid,
+  so I was trying to find a way of rewording it.)}.  In
 the case of observables that do not require the reconstruction of the $t$
@@
 other $\mathrm{CP}$-odd observables. In particular,
-observables based on TPs that {\bf (N: ``do not contain the $t$ and $\tbar$ spin vectors and
-in certain cases incorporate")} the Higgs momentum
-{\bf (KK: not all of them involve the Higgs momentum in this section\ldots
-  is this the best way to describe this section?
-  I'm fine with it, either way.)} are
-discussed in Sec.~\ref{sec4} {\bf (N: ;)} and observables that do not
+observables based on TPs that do not contain the $t$ and $\tbar$
+spin vectors, and
+in certain cases incorporate the Higgs momentum, are
+discussed in Sec.~\ref{sec4}; observables that do not
 involve the $t$ and $\tbar$ momenta are studied in
@@
 \rangle$ and $\langle \epsilon_3 \rangle$,
-       {\bf (KK: explicit reference to $\epsilon_2$ and $\epsilon_3$ correct?
-         Seems like $\epsilon_4$ is actually a bit better than $\epsilon_1$) (N: The effective separation
-         for $\epsilon_4$ is $11.55$ while for $\epsilon_1$ is $12.24$)}
+       {\bf (KK: is my explicit reference to $\epsilon_2$ and $\epsilon_3$ correct?  I think so\ldots.)}
 yielding $-4.32$, $1.11$ and $7.23$ for the cases

### 2016-03-10 Paper_ttbarH_Draft.tex
New version

@@
 ``$\mathrm{CP}$-mixed'' scenarios 
-with an effective separation of $\sim 20\sigma$ {\bf (N: In previous version it said ``statistical level" because we wanted 
-  to stress that we are not considering systematic uncertainties.
-  KK: This was why I added the new phrase, ``and taking into account
-  only statistical uncertainties.''  You can certainly
-  change this back if you like,
-  though.  The previous way of wording it seemed not completely fluid,
-  so I was trying to find a way of rewording it.)}.  In
+with an effective separation of $\sim 20\sigma$. In
 the case of observables that do not require the reconstruction of the $t$
@@
 In Sec.~\ref{sec3.1} we defined a fourth triple product,
-$\epsilon_4 = \epsilon_3-\epsilon_2$.  We have constructed
+$\epsilon_4 = \epsilon_3-\epsilon_2$.  {\bf We have constructed
 an angular distribution related to this TP as well.
@@
 right for different values of the parameters, the distributions
-remain peaked near $\Delta\phi(n_t,n_{\tbar})=0$, but become
-slightly distorted in such a way that there is a non-zero
-asymmetry [see Eq.~(\ref{eq26})].  Interestingly, while there
-is not much visible change in the $\epsilon_4$ angular distribution
-for different
-parameter values, the associated asymmetry values are
+become distorted in such a way that there is a non-zero
+asymmetry [see Eq.~(\ref{eq26})].  Moreover, the associated asymmetry values are
 larger than the asymmetries for the other TPs [see 
-  Tables \ref{table1} and \ref{table2}].  Since this angular
-distribution does not exhibit much visible change for
-different values of $\kp$ and $\kpt$, we do not include the corresponding
-plots here.
+Tables \ref{table1} and \ref{table2}].}
 
@@
 mean value for the combination $\epsilon_4$ introduced in
-Sec.~\ref{sec3.1} gives slightly smaller values than those listed in
-Table~\ref{table5} for $\langle \epsilon_2
-\rangle$ and $\langle \epsilon_3 \rangle$,
+Sec.~\ref{sec3.1} {\bf is slightly less sensitive than $\langle \epsilon_1\rangle$,
+ $\langle \epsilon_2\rangle$ and $\langle \epsilon_3\rangle$},
        {\bf (KK: is my explicit reference to $\epsilon_2$ and $\epsilon_3$ correct?  I think so\ldots.)}
-yielding $-4.32$, $1.11$ and $7.23$ for the cases
-$(\kp=1,\kpt=-1,0,1)$, respectively. As with the asymmetry, the
+{\bf with values $-4.32$, $1.11$ and $7.23$ for the cases
+$(\kp=1,\kpt=-1,0,1)$, respectively}. As with the asymmetry, the
 purely $\mathrm{CP}$-even and purely $\mathrm{CP}$-odd cases cannot be
@@
 \ref{table6} for $\epsilon_5$.
-We have also studied the associated angular distributions.
-We do not include plots of these distributions, however,
-because they
-do not exhibit much visible variation for the different
-scenarios under consideration.  (The situation is similar
+{\bf We have also studied the associated angular distributions. Specifically, 
+we have analized the $\Delta\phi(\ell^+,\ell^-)$ distribution in the $t\tbar H$ rest frame,
+taking $H$ to define the $z$-axis. The distributions obtained for different values of
+$\kp$ and $\kpt$ are not well described by Eq.~(\ref{eq27}) (the situation is similar
 to that encountered for the angular distribution
 associated with $\epsilon_4$ -- see the discussion
-at the end of Sec.~\ref{sec3.2}.)
-{\bf (KK: have I worded this correctly?
-  Does the distribution look similar even in the
-  purely CP-odd case, for example?)}
-
+at the end of Sec.~\ref{sec3.2}.).  For different values of the parameters,
+the distributions become slightly distorted giving rise to a non-zero asymmetry 
+[see Eq. (29)].}
 \begin{table}[H]

### 2016-03-15 Paper_ttbarH_Draft.tex
Version submitted to arxiv

@@
 ``$\mathrm{CP}$-mixed'' scenarios 
-with an effective separation of $\sim 20\sigma$. In
+with an effective separation of $\sim 19\sigma$. In
 the case of observables that do not require the reconstruction of the $t$
 and $\tbar$ momenta, the power of discrimination is up to $\sim
-16\sigma$ for the same number of events. We also show that the
+13\sigma$ for the same number of events. We also show that the
 most promising observables can still disentangle the
@@
 couplings. The proposed observables are based on a particular set of
-triple product (TP) structures that we extract from the
+triple product (TP) correlations that we extract from the
 expression for the differential cross section for $\ppprocess$,
@@
 \end{center}
+\vspace*{-1cm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \cite{ale1,*ale2,*ale3,*ale4}. \par
-
 %%%%%%%%%%%%%%%%% FIGURA 2 %%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\vspace*{-0.85cm}
 To derive the above expressions, we begin by considering the
@@
 %
-\bea
+\beq
 \label{eq7}
-\bar{\psi}_t &=& -g^2\, \mathbb{P}_t(t)\,\mathbb{P}_W(t-b)\,
-   \langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\
+\bar{\psi}_t = -g^2\, \mathbb{P}_t(t)\,\mathbb{P}_W(t-b)\,
+   \langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)
+\eeq
+\beq
 \label{eq8}
-\psi_{\tbar} &=& g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
-   \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
-\eea
+\psi_{\tbar} = g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
+   \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,\\[1mm]
+\eeq
+%\bea
+%\label{eq7}
+%\bar{\psi}_t &=& -g^2\, \mathbb{P}_t(t)\,\mathbb{P}_W(t-b)\,
+%   \langle b-|\nu_{\ell}+\rangle \langle {\ell}^+\!+|(\tslash+m_t)\\[0.4cm]
+%\label{eq8}
+%\psi_{\tbar} &=& g^2\, \mathbb{P}_t(\tbar)\,\mathbb{P}_W(\tbar-\bbar)\,
+%   \langle\nubar+|\bbar-\rangle (\tbslash-m_t)|{\ell}^-+\rangle,
+%   \vspace*{0.8cm}
+%\eea
 %
@@
 odd number of $\gamma^5$ matrices; these lead to triple-product
-(TP) structures
+(TP) correlations
 of the form $\epsilon_{\alpha\beta\gamma\delta}\,p^{\alpha}_ap^{\beta}_bp^{\gamma}_cp^{\delta}_d$,
@@
 respectively.
+\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
+\renewcommand{\arraystretch}{1.4}
+\begin{table}[H]
+  \caption{Asymmetries for three different scenarios,
+    obtained by using $10^5$ simulated events, for the
+    TPs $\epsilon_1=\TPa, \epsilon_2=\TPb$ and $\epsilon_3=\TPc$.
+    The three scenarios
+  correspond to the SM ($\kp=1$ and $\kpt= 0$) and the
+  two ``$\mathrm{CP}$-mixed'' cases (defined by
+  $\kp=1$ and $\kpt=\pm 1$).}
+\label{table1}
+\begin{center}
+\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
+%\begin{tabular}{|c|r||r|c||r|c||r|c|}
+\hhline{|========|}
+%\hhline{|--------|}
+$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_1)$~~&$\mathcal{A}(\epsilon_1)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_2)$~~&$\mathcal{A}(\epsilon_2)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_3)$~~&$\mathcal{A}(\epsilon_3)/\sigma_{\mathcal{A}}$  \\
+\hhline{|========|} 
+%\hhline{|--------|}
+$1$ & $-1$~~~ & $0.0315$~ & $10.0$ & $0.0332$~ & $10.5$~ & $-0.0307$~~~ & $-9.7$~~~\\[0.6mm]
+\hline
+$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $0.0009$~ & $0.3$~ & $-0.0011$~~~ & $-0.3$~~~\\[0.6mm]
+\hline
+$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $-0.0411$~~~& $-13.0$~~~ & $\,0.0378$~ & $12.0$ \\[0.6mm]
+\hhline{|========|}
+%\hhline{|--------|}
+\end{tabular}
+\end{center} 
+\end{table}
 
@@
 $q\qbar$ contribution.
-\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
-\renewcommand{\arraystretch}{1.4}
-\begin{table}[H]
-  \caption{Asymmetries for three different scenarios,
-    obtained by using $10^5$ simulated events, for the
-    TPs $\epsilon_1=\TPa, \epsilon_2=\TPb$ and $\epsilon_3=\TPc$.
-    The three scenarios
-  correspond to the SM ($\kp=1$ and $\kpt= 0$) and the
-  two ``$\mathrm{CP}$-mixed'' cases (defined by
-  $\kp=1$ and $\kpt=\pm 1$).}
-\label{table1}
-\begin{center}
-\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
-%\begin{tabular}{|c|r||r|c||r|c||r|c|}
-\hhline{|========|}
-%\hhline{|--------|}
-$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_1)$~~&$\mathcal{A}(\epsilon_1)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_2)$~~&$\mathcal{A}(\epsilon_2)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_3)$~~&$\mathcal{A}(\epsilon_3)/\sigma_{\mathcal{A}}$  \\
-\hhline{|========|} 
-%\hhline{|--------|}
-$1$ & $-1$~~~ & $0.0315$~ & $10.0$ & $0.0332$~ & $10.5$~ & $-0.0307$~~~ & $-9.7$~~~\\[0.6mm]
-\hline
-$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $0.0009$~ & $0.3$~ & $-0.0011$~~~ & $-0.3$~~~\\[0.6mm]
-\hline
-$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $-0.0411$~~~& $-13.0$~~~ & $\,0.0378$~ & $12.0$ \\[0.6mm]
-\hhline{|========|}
-%\hhline{|--------|}
-\end{tabular}
-\end{center} 
-\end{table}
 %%%%%%%%%%%%%%%%%%%%%%%%% FIGURA 3 %%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{center}
+\vspace*{-1cm}
 \par As can be seen from Figs.~\ref{fig5} and \ref{fig6}, the
@@
 are approximately between
-$0.9$ and $1$ ($-1$ and $-0.9$) for $\kp=\kpt=1$ ($\kp=-\kpt=1$), both
+$0.9$ and $1$ ($-1$ and $-0.9$) for $\kp=-\kpt=1$ ($\kp=\kpt=1$), both
 for $\epsilon_1$ and $\epsilon_2$.\footnote{The results for the
@@
 important to stress, however, that the fits for the $\Delta\phi_2$ distributions
-always yield smaller values for the $\chi^2/\mathrm{d.o.f}$.
-
+always yield smaller values for the $\chi^2/\mathrm{d.o.f}$.\par
+In Sec.~\ref{sec3.1} we defined a fourth triple product,
+$\epsilon_4 = \epsilon_3-\epsilon_2$. We have constructed
+an angular distribution related to this TP as well.
+Specifically, we have analyzed the
+$\Delta\phi(n_t,n_{\tbar})$ distribution in the $Q$ rest frame,
+taking
+$H$ to define the $z$-axis.  We have studied the distributions
+for various values of $\kp$ and $\kpt$ and have
+found that they are not well described by Eq.~(\ref{eq27}).
+Instead of resembling sinusoids that are shifted to the left or
+right for different values of the parameters, the distributions
+become distorted in such a way that there is a non-zero
+asymmetry [see Eq.~(\ref{eq26})].  Moreover, the associated asymmetry values are
+larger than the asymmetries for the other TPs [see 
+Tables \ref{table1} and \ref{table2}]. 
 \renewcommand{\arraystretch}{1.2}
@@
 \end{center}
-\par
-
-In Sec.~\ref{sec3.1} we defined a fourth triple product,
-$\epsilon_4 = \epsilon_3-\epsilon_2$.  {\bf We have constructed
-an angular distribution related to this TP as well.
-Specifically, we have analyzed the
-$\Delta\phi(n_t,n_{\tbar})$ distribution in the $Q$ rest frame,
-taking
-$H$ to define the $z$-axis.  We have studied the distributions
-for various values of $\kp$ and $\kpt$ and have
-found that they are not well described by Eq.~(\ref{eq27}).
-Instead of resembling sinusoids that are shifted to the left or
-right for different values of the parameters, the distributions
-become distorted in such a way that there is a non-zero
-asymmetry [see Eq.~(\ref{eq26})].  Moreover, the associated asymmetry values are
-larger than the asymmetries for the other TPs [see 
-Tables \ref{table1} and \ref{table2}].}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the two $\mathrm{CP}$-mixed cases
-are clearly disentangled, since the the observables are
+are clearly disentangled, since the observables are
 sensitive to the sign of $\kpt$. The observables $\langle \epsilon_2
@@
 mean value for the combination $\epsilon_4$ introduced in
-Sec.~\ref{sec3.1} {\bf is slightly less sensitive than $\langle \epsilon_1\rangle$,
- $\langle \epsilon_2\rangle$ and $\langle \epsilon_3\rangle$},
-       {\bf (KK: is my explicit reference to $\epsilon_2$ and $\epsilon_3$ correct?  I think so\ldots.)}
-{\bf with values $-4.32$, $1.11$ and $7.23$ for the cases
-$(\kp=1,\kpt=-1,0,1)$, respectively}. As with the asymmetry, the
+Sec.~\ref{sec3.1} is slightly less sensitive than $\langle \epsilon_1\rangle$,
+ $\langle \epsilon_2\rangle$ and $\langle \epsilon_3\rangle$, 
+ with values $-4.32$, $1.11$ and $7.23$ for the cases
+$(\kp=1,\kpt=-1,0,1)$, respectively. As with the asymmetry, the
 purely $\mathrm{CP}$-even and purely $\mathrm{CP}$-odd cases cannot be
@@
 the results presented in Sec.~\ref{sec3.1}, we can conclude that
-the sensitivity to the NP contribution is smaller for the mean values
+the sensitivity to the anomalous $tH$ coupling is smaller for the mean values
 of the TPs under consideration
@@
 %\hhline{|=====|}
-\hhline{|-----|}
+\hhline{|=====|}
 $\kappa_t$ & $\tilde{\kappa}_t$ & $\langle \epsilon_1 \rangle /\sigma_{\bar{\epsilon}_1}$ & $\langle \epsilon_2 \rangle /\sigma_{\bar{\epsilon}_2}$ & $\langle \epsilon_3 \rangle /\sigma_{\bar{\epsilon}_3}$ \\
@@
 \label{sec4}
-So far we have considered three TPs involving the momenta $t,\tbar$
+So far we have considered TPs involving the momenta $t,\tbar$
 and $Q$ and the spin vectors $n_t$ and $n_{\tbar}$ [defined in
@@
 %
-
-\renewcommand{\arraystretch}{1.4}
-\begin{table}[H]
-\caption{Asymmetries for the TPs $\epsilon_{5,6,7}$ for the SM case
-  and the two $\mathrm{CP}$-mixed cases.
-  The values correspond to $10^5$ simulated events.}
-\label{table7}
-\begin{center}
-\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
-%\begin{tabular}{|c|r||r|c||r|c||r|c|}
-\hhline{|========|}
-%\hhline{|--------|}
-$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_5)$~~&$\mathcal{A}(\epsilon_5)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_6)$~~&$\mathcal{A}(\epsilon_6)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_7)$~~&$\mathcal{A}(\epsilon_7)/\sigma_{\mathcal{A}}$  \\
-\hhline{|========|} 
-%\hhline{|--------|}
-$1$ & $-1$~~~ & $0.0315$~ & $10.0$~ & $-0.0134$~~~ & $-4.2$~~~ & $0.0111$~ & $3.5$~\\[0.6mm]
-\hline
-$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $-0.0011$~~~ & $-0.3$~~~ & $0.0009$~& $0.3$~\\[0.6mm]
-\hline
-$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $0.0143$~ & $4.5$~ & $-0.0137$~~~ & $\,-4.3$~~~  \\[0.6mm]
-\hhline{|========|}
-%\hhline{|--------|}
-\end{tabular}
-\end{center} 
-\end{table}
-
-\renewcommand{\arraystretch}{1.6}
-\begin{table}[H]
-\caption{Mean values obtained for $\epsilon_{5,6,7}$ for the
-  SM case and the two $\mathrm{CP}$-mixed cases.
-  The values correspond to $10^5$ simulated
-  events.}
-\label{table6}
-\begin{center}
-\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}||C{2cm}||C{2cm}|}
-%\hhline{|=====|}
-\hhline{|-----|}
-$\kappa_t$ & $\tilde{\kappa}_t$ & $\langle \epsilon_5 \rangle /\sigma_{\bar{\epsilon}_5}$ & $\langle \epsilon_6 \rangle /\sigma_{\bar{\epsilon}_6}$ & $\langle \epsilon_7 \rangle /\sigma_{\bar{\epsilon}_7}$ \\
-\hhline{|=====|} 
-%\hhline{|-----|}
-%\vspace*{.5mm}
-\renewcommand{\arraystretch}{1.0}
-$1$~ & $-1$~~~ & $3.98$~ & $-1.96$~~~ & $1.69$~ \\[0.6mm]
-\hline
-$1$ & $0$~ & $-0.43$~~~ & $1.25$~ & $0.74$~ \\[0.6mm]
-\hline
-$1$ & $1$~ & $-6.76$~~~ & $3.46$~ & $-3.29$~~~~\\[0.6mm]
-\hhline{|=====|}
-%\hhline{|-----|}
-\end{tabular}
-\end{center} 
-\end{table}
 \par
-%
 
@@
 appear to have a higher sensitivity to the pseudoscalar coupling than do
-$\epsilon_{5,6,7}$.  \par
-
+$\epsilon_{5,6,7}$. 
+\renewcommand{\arraystretch}{1.4}
+\begin{table}[H]
+\caption{Asymmetries for the TPs $\epsilon_{5,6,7}$ for the SM case
+  and the two $\mathrm{CP}$-mixed cases.
+  The values correspond to $10^5$ simulated events.}
+\label{table7}
+\begin{center}
+\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
+%\begin{tabular}{|c|r||r|c||r|c||r|c|}
+\hhline{|========|}
+%\hhline{|--------|}
+$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_5)$~~&$\mathcal{A}(\epsilon_5)/\sigma_{\mathcal{A}}$& $\mathcal{A}(\epsilon_6)$~~&$\mathcal{A}(\epsilon_6)/\sigma_{\mathcal{A}}$&$\mathcal{A}(\epsilon_7)$~~&$\mathcal{A}(\epsilon_7)/\sigma_{\mathcal{A}}$  \\
+\hhline{|========|} 
+%\hhline{|--------|}
+$1$ & $-1$~~~ & $0.0315$~ & $10.0$~ & $-0.0134$~~~ & $-4.2$~~~ & $0.0111$~ & $3.5$~\\[0.6mm]
+\hline
+$1$ & $0$ & $-0.0021$~~~ & $-0.7$~~~ & $-0.0011$~~~ & $-0.3$~~~ & $0.0009$~& $0.3$~\\[0.6mm]
+\hline
+$1$ & $1$ & $-0.0379$~~~ & $-12.0$~~~ & $0.0143$~ & $4.5$~ & $-0.0137$~~~ & $\,-4.3$~~~  \\[0.6mm]
+\hhline{|========|}
+%\hhline{|--------|}
+\end{tabular}
+\end{center} 
+\end{table}
+
+\renewcommand{\arraystretch}{1.6}
+\begin{table}[H]
+\caption{Mean values obtained for $\epsilon_{5,6,7}$ for the
+  SM case and the two $\mathrm{CP}$-mixed cases.
+  The values correspond to $10^5$ simulated
+  events.}
+\label{table6}
+\begin{center}
+\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}||C{2cm}||C{2cm}|}
+\hhline{|=====|}
+%\hhline{|-----|}
+$\kappa_t$ & $\tilde{\kappa}_t$ & $\langle \epsilon_5 \rangle /\sigma_{\bar{\epsilon}_5}$ & $\langle \epsilon_6 \rangle /\sigma_{\bar{\epsilon}_6}$ & $\langle \epsilon_7 \rangle /\sigma_{\bar{\epsilon}_7}$ \\
+\hhline{|=====|} 
+%\hhline{|-----|}
+%\vspace*{.5mm}
+\renewcommand{\arraystretch}{1.0}
+$1$~ & $-1$~~~ & $3.98$~ & $-1.96$~~~ & $1.69$~ \\[0.6mm]
+\hline
+$1$ & $0$~ & $-0.43$~~~ & $1.25$~ & $0.74$~ \\[0.6mm]
+\hline
+$1$ & $1$~ & $-6.76$~~~ & $3.46$~ & $-3.29$~~~~\\[0.6mm]
+\hhline{|=====|}
+%\hhline{|-----|}
+\end{tabular}
+\end{center} 
+\end{table}
+ \par
 It is important to mention that in the
@@
 \ref{table6} for $\epsilon_5$. 
-{\bf We have also studied the associated angular distributions. Specifically, 
-we have analized the $\Delta\phi(\ell^+,\ell^-)$ distribution in the $t\tbar H$ rest frame,
+We have also studied the associated angular distributions. Specifically, 
+we have analyzed the $\Delta\phi(\ell^+,\ell^-)$ distribution in the $t\tbar H$ rest frame,
 taking $H$ to define the $z$-axis. The distributions obtained for different values of
@@
 the distributions become slightly distorted giving rise to a non-zero asymmetry 
-[see Eq. (29)].}
+[see Eq. (29)].
 \begin{table}[H]
@@
 Comparing
-Tables~\ref{table9} and \ref{table10}, we see that the
+Tables~\ref{table9} and \ref{table10}, we see that the effective
 separation between the $\mathrm{CP}$-mixed scenarios is enhanced by
@@
 visible parts, while in the case of $\epsilon_9$ the bottom and
-antibottom momenta have been used.
-
-%
-\begin{table}[th]
+antibottom momenta have been used.\par
+For comparison purposes, we have also used our simulated events
+to test the lab frame
+\begin{table}[H]
 \caption{Asymmetry for the TP $\epsilon_{10}$ for the SM case and the
@@
 \end{table}
-%
-
-For comparison purposes, we have also used our simulated events
-to test the lab frame observable given
+\noindent
+observable given
 in Ref.~\cite{Guadagnoli}. We have found that this observable
@@
 be slightly less sensitive than $\mathcal{A}(\epsilon_{10})$,
-giving rise to a separation between the $\mathrm{CP}$-mixed scenarios
+giving rise to an effective separation between the $\mathrm{CP}$-mixed scenarios
 that is smaller by about $1.4\sigma$.
@@
 $5\times 10^3$ events the effective separation between the $\mathrm{CP}$-mixed
-scenarios under consideration is $\sim 6.5\sigma$. \par
+scenarios under consideration is $6.5\sigma$. \par
 
@@
 \mathrm{fb}^{-1}$ of data at $\sqrt{s}=8\,\mathrm{TeV}$.
-
-\begin{table}[th]
+%
+\begin{table}[H]
 \caption{Asymmetry for the TP $\epsilon_4$ obtained using $5\times
@@
 \end{table}
-
-\begin{table}[th]
-\caption{Asymmetry for the TP $\epsilon_{10}$ in the SM case and the
-  two $\mathrm{CP}$-mixed cases for
-  $5\times 10^4$ and $1\times 10^4$ events.}
-\label{table12}
-\begin{center}
-\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
-%\begin{tabular}{|c|r||r|c||r|c||r|c|}
-\hhline{|======|}
-%\hhline{|--------|}
-\multirow{2}{*}{$\kappa_t$} & \multirow{2}{*}{$\tilde{\kappa}_t$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=5\times 10^4$} & \multicolumn{2}{c|}{$N_{\mathrm{ev}}=1\times 10^4$} \\ \cline{3-6}
-& & $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ \\
-\hhline{|======|} 
-%\hhline{|--------|}
-$1$ & $-1$~~~ & $-0.0270$~~~ & $-6.0$~~~ & $-0.0184$~~~ & $-1.8$~~~  \\[0.6mm]
-\hline
-$1$ & $0$ & $0.0022$~ & $0.5$~ & $-0.0086$~~~ & $-0.9$~~~  \\[0.6mm]
-\hline
-$1$ & $1$ & $0.0313$~ & $7.0$~ & $0.0380$~ & $3.8\,$ \\
-\hhline{|======|}
-%\hhline{|--------|}
-\end{tabular}
-\end{center} 
-\end{table}
-%
-
-The
-results shown in Tables \ref{table11} and \ref{table12} reveal that
+The results shown in Tables \ref{table11} and \ref{table12} reveal that
 with $5\times 10^3$ and $1\times 10^4$ events, respectively, the
@@
 of luminosities is in principle achievable in the short term by the
-LHC. We note that in order to be fully conclusive about the required
-luminosity, it is important to include the effects of hadronization,
+LHC. We note that in order to be fully conclusive about  
+%
+\begin{table}[H]
+\caption{Asymmetry for the TP $\epsilon_{10}$ in the SM case and the
+  two $\mathrm{CP}$-mixed cases for
+  $5\times 10^4$ and $1\times 10^4$ events.}
+\label{table12}
+\begin{center}
+\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}||C{2cm}|C{2cm}|}
+%\begin{tabular}{|c|r||r|c||r|c||r|c|}
+\hhline{|======|}
+%\hhline{|--------|}
+\multirow{2}{*}{$\kappa_t$} & \multirow{2}{*}{$\tilde{\kappa}_t$} & \multicolumn{2}{c||}{$N_{\mathrm{ev}}=5\times 10^4$} & \multicolumn{2}{c|}{$N_{\mathrm{ev}}=1\times 10^4$} \\ \cline{3-6}
+& & $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ &  $\mathcal{A}(\epsilon_{10})$~~&$\mathcal{A}(\epsilon_{10})/\sigma_{\mathcal{A}}$ \\
+\hhline{|======|} 
+%\hhline{|--------|}
+$1$ & $-1$~~~ & $-0.0270$~~~ & $-6.0$~~~ & $-0.0184$~~~ & $-1.8$~~~  \\[0.6mm]
+\hline
+$1$ & $0$ & $0.0022$~ & $0.5$~ & $-0.0086$~~~ & $-0.9$~~~  \\[0.6mm]
+\hline
+$1$ & $1$ & $0.0313$~ & $7.0$~ & $0.0380$~ & $3.8\,$ \\
+\hhline{|======|}
+%\hhline{|--------|}
+\end{tabular}
+\end{center} 
+\end{table}
+%
+\noindent
+the required luminosity, it is important to include the effects of hadronization,
 detector resolution, reconstruction efficiencies and so
@@
 spin vectors ($\epsilon_8$), the sensitivity in the asymmetry is
-decreased by $\sim 3.1\sigma$ compared to the asymmetry associated
+decreased by $3.1\sigma$ compared to the asymmetry associated
 with $\epsilon_4$ for
